### 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
git init

---
title: "shrimp_goby_boatnoise"
author: "Jack Manera"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_download: true
    code_folding: hide
    depth: 4
    number_sections: no
    theme:  cosmo
    toc: yes
    toc_float: yes
    toc_depth: 4
  pdf_document:
    toc: yes
---

#1. Data wrangling
##1.1 Loading the required packages
```{r, message=FALSE, results='hide'}
#install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr)

remotes::install_github("stan-dev/loo")
# Setting colours for vidsalisations
colour1 <- "#97A275"
colour2 <- "#F2B23A"
colour3 <- "#F2711B"
colour4 <- "#8CBEB2"
colour5 <- "#E7C27D"
colour6 <- "#F2A775"
colour11 <- "#666E4F"
colour12 <- "#A38346"
colour13 <- "#9C4811"
```

##1.2 Unblinding the data
```{r}
#assigning the directory so that the code can be universally read on any computer as long as the entire project file is shared
directory <- './1-data/'

#reading in the coded raw BORIS output
BORIS_output <- read.csv("./1-data/BORIS_output_update.csv")

#reading in the decoder
Video_codes <- read.csv("./1-data/Video_codes.csv")

shrimp_species <- read.csv("./1-data/species.csv")

length(unique(BORIS_output$code))

#binding the decoder to the BORIS output and revealing the treatment and stage
BORIS_output$code <- str_sub(BORIS_output$video_id, 2,)
BORIS_output$code <- as.factor(BORIS_output$code)
shrimp_species$code <- as.factor(shrimp_species$code)
Video_codes$code <- as.factor(Video_codes$code)
decoded_dataframe <- inner_join(inner_join(BORIS_output, Video_codes, by = c("code")), shrimp_species, by = c("code"))
```

## 1.3 Cross-checking the imported datasets
```{r}
# Find common codes across all data sets
common_codes <- Reduce(intersect, list(BORIS_output$code, shrimp_species$code, Video_codes$code))

# Combine all codes from the three data sets
all_codes <- unique(c(BORIS_output$code, shrimp_species$code, Video_codes$code))

# Find codes not common across all data sets
codes_not_common <- setdiff(all_codes, common_codes)

# Define a function to check which data sets contain each code
check_code_origin <- function(code) {
  origins <- c()

  if(code %in% BORIS_output$code) {
    origins <- c(origins, "BORIS_output")
  }
  if(code %in% shrimp_species$code) {
    origins <- c(origins, "shrimp_species")
  }
  if(code %in% Video_codes$code) {
    origins <- c(origins, "Video_codes")
  }

  return(paste(origins, collapse=", "))
}

# Create a dataframe to store the results
results <- data.frame(code = character(0), origin = character(0), stringsAsFactors = FALSE)

# Loop through each code not common across all data sets
for(code in codes_not_common) {
  origin <- check_code_origin(code)
  results <- rbind(results, data.frame(code = as.character(code), origin = origin, stringsAsFactors = FALSE))
}

# Print the results
print(results)

# Missing observations are identified exclusively within the 'Video_codes' dataframe. This situation suggests that all videos capturing both shrimp and gobies are consistently represented across the datasets. However, there were instances where burrows were recorded and assigned video codes but showed no activity from gobies or shrimp during these recordings. These instances led to the assumption that such burrows were inactive, resulting in their exclusion from the further analysis of the study.
```

##1.4 Cleaning the dataframe
###1.4.1 Column renaming
```{r}
decoded_dataframe <- decoded_dataframe |> 
  rename(shrimp_species = species)

#renaming some of the variables and extracting individual variables from columns that have multiple variables contained in one string
decoded_dataframe <- decoded_dataframe |> 
  dplyr::rename(stage = video_section,
                duration = total_duration_s,
                behaviour = behavior) |>
  dplyr::mutate(date = str_sub(date_file, , 6),
                species = str_sub(subject, 5,),
                duration = as.numeric(duration),
                boat_id = str_sub(date_file, -1, -1),
                video_num = as.numeric(str_sub(video_id, 2)),
                burrow = ceiling(video_num/3),
                individual = str_sub(subject, 1, 1),
                helper = str_sub(date_file, -6,-6),
                stroke = ifelse(helper == "t", 'control', 
                                ifelse((boat_id == "A")|(boat_id == "B")|(boat_id == "C")|(boat_id == "D"), 
                                       '2', '4')))

#creating some unique identifiers to make grouping easier later on for reorganising of the dataframe
decoded_dataframe <- decoded_dataframe |> 
  unite("unique_id", 'burrow','individual', 'species', 'stage', remove = FALSE) |> 
  unite("burrow_species_stage", 'burrow', 'species', 'stage', remove = FALSE) |> 
  unite("burrow_species", 'burrow', 'species', remove = FALSE)
```

###1.4.2 Removing redundant BORIS entries
```{r}
#the next few lines of code are to do with the way BORIS outputs data, where there was redundant empty sections due to both species being independently scored in the software. So here we are filtering out the species specific data from the correlating BORIS species observation and then rebinding the data to remove all of the empty artifact entries.

#extracting just the goby data so that a species variable can be made
goby_dataframe <- decoded_dataframe |> 
  dplyr::filter(species == "Goby") |> 
  dplyr::filter(str_detect(video_id, 'g'))

#extracting just the shrimp data so that a species variable can be made
shrimp_dataframe <- decoded_dataframe |> 
  dplyr::filter(species == "Shrimp")  |>  
  dplyr::filter(str_detect(video_id, 'j'))

#binding the two species specific data frames back together so that there is now no empty 
workingdf1 <- bind_rows(goby_dataframe, shrimp_dataframe)

#filtering for the behviours of interest to this experiment
workingdf2 <- workingdf1 |> 
  group_by(unique_id) |> 
  filter(behaviour == 'INSIDE' | behaviour == 'EDGE' | behaviour == 'NEAR' | behaviour == 'AWAY' |behaviour == 'CONTACT' |behaviour == 'APART' ) |>
  mutate(averageduration = sum(duration))

#becuase of the way BORIS outputs data there are redundant individuals in the data, e.g., even if there are only two shrimp in a burrow then BORIS will still output observations for a third shrimp and all value will be 0's. this is what this section of code is removing
workingdf3 <- workingdf2 |> 
  group_by(burrow, species, individual) |> 
  filter(sum(averageduration) != 0)
```

###1.4.3 Assigning values to missing entries
```{r}
#now here we are making the assumption that when a goby or shrimp is present in other videos but missing from the video of focus it is either away and out of frame for the entire trial if it is a goby. Otherwise it is inside the burrow the entire time if it is a shrimp. These assumptions are based off of preliminary observation and the general tendencies of each species. Because of this assumption we are assigning the respective value to the behviour in cases where one of the species is known to be present in a burrow but not viewed for the length of the trial. 
fixeddf1 <- workingdf3 |> 
  filter(averageduration == 0) |> 
  mutate(duration = ifelse(species == "Goby" & behaviour == "AWAY", 300, duration),
         duration = ifelse(species == "Shrimp" & behaviour == "INSIDE", 300, duration)
         )

fixeddf2 <- workingdf3 |> 
  filter(averageduration != 0)

workingdf4 <- rbind(fixeddf2, fixeddf1) |> 
  group_by(burrow_species) |> 
  dplyr::mutate(number_conspecifics = max(as.integer(individual))) |> 
  ungroup()

#now using the number of conspecifics to calculate a duration value that represents the mean time spent doing that activity for that species (i.e. goby or shrimp) in that burrow as we are un able to preserve identity and thus instead must look at species averages for each behaviour. 
workingdf5 <- workingdf4 |> 
  group_by(burrow_species, behaviour, stage) |> 
  dplyr::mutate(mean_duration = mean(duration)) |> 
  ungroup() |> 
  filter(individual == 1)

#transforming the data frame into wide format and turning time spent in each zone into a proportion of the total time (i.e. a value between 0 and 1)
wide_data <- workingdf5 |>
  pivot_wider(
    id_cols = c(burrow_species, burrow_species_stage, burrow, stage, species, boat_id, stroke, site, number_conspecifics, shrimp_species),
    names_from = behaviour,
    values_from = mean_duration
  )

wide_data <- wide_data |> 
  mutate(INSIDE = as.numeric(INSIDE),
         EDGE = as.numeric(EDGE),
         NEAR = as.numeric(NEAR),
         AWAY = as.numeric(AWAY),
         CONTACT = as.numeric(CONTACT),
         APART = as.numeric(APART)) |> 
  mutate(total = INSIDE+NEAR+EDGE+AWAY,
         inside = (INSIDE + EDGE)/(INSIDE+EDGE+NEAR+AWAY), 
         away = (NEAR + AWAY)/(INSIDE+EDGE+NEAR+AWAY),
         number_conspecifics = as.factor(number_conspecifics),
         shrimp_contact = CONTACT/(CONTACT+APART)
         ) |> 
  dplyr::select(-INSIDE, -EDGE, -NEAR, -AWAY, -CONTACT, -APART)

#checking if every burrow contains observations for both 'Shrimp' and 'Goby'
burrow_values <- unique(wide_data$burrow) 
has_shrimp <- burrow_values %in% wide_data$burrow[wide_data$species == 'Shrimp'] 
has_goby <- burrow_values %in% wide_data$burrow[wide_data$species == 'Goby'] 
burrows_without_both_species <- burrow_values[!(has_shrimp & has_goby)]
cat("burrows without both 'Shrimp' and 'Goby' species:", paste(burrows_without_both_species, collapse = ', '))

#removing the rows with burrows without both 'Shrimp' and 'Goby' species from the dataframe
wide_data <- wide_data[!wide_data$burrow %in% burrows_without_both_species, ]

wide_data <- wide_data |> 
  mutate(burrow = as.factor(burrow))

#Checking to see the count of observations per burrow
burrow_counts <- table(wide_data$burrow)
print(burrow_counts)

#there are some burrows that are missing stages due to the animal not being observered at all during that observation so we will make some conditional assumptions and fill in the missing values.

#a function to fill the missing stages for each species within each burrow
fill_missing_stages <- function(df) {
  all_stages <- c('Pre', 'During', 'Post')

  missing_stages <- setdiff(all_stages, unique(df$stage))

  if(length(missing_stages) == 0) return(data.frame())

  common_values <- df[1, ]

  new_rows <- data.frame()

  for(stage in missing_stages) {
    new_row <- common_values
    new_row$stage <- stage

    # Set column values based on species
    if(new_row$species == "Goby") {
      new_row$away <- 1
      new_row$inside <- 0
      new_row$total <- 300
      new_row$shrimp_contact <- 0
    } else if(new_row$species == "Shrimp") {
      new_row$away <- 0
      new_row$inside <- 1
      new_row$total <- 300
      new_row$shrimp_contact <- NA
    }

    new_rows <- rbind(new_rows, new_row)
  }

  return(new_rows)
}

#applying the function
fixeddf3 <- wide_data |>
  group_by(burrow_species) |>
  do(fill_missing_stages(.)) |>
  ungroup()

wide_data_filled <- rbind(wide_data, fixeddf3)

#Checking to see the count of observations per burrow
filled_burrow_counts <- table(wide_data_filled$burrow)
print(filled_burrow_counts)
```

###1.4.4 Changing dataframe format 
```{r}
workingdf7 <- wide_data_filled |> 
  mutate(burrow_stage = paste(burrow, stage))

goby_df <- workingdf7 |> 
  filter(species == "Goby") |> 
  rename(goby_out = away, goby_total = total, goby_number = number_conspecifics) |> 
  select(-c("inside", "species", "burrow_species", "burrow_species_stage", "shrimp_contact"))

shrimp_df <- workingdf7 |> 
  filter(species == "Shrimp") |> 
  rename(shrimp_out = away, shrimp_total = total, shrimp_number = number_conspecifics) |> 
  select(c("shrimp_out", "shrimp_total", "shrimp_number", "burrow_stage", "shrimp_contact"))

final_df <- inner_join(goby_df, shrimp_df, by = "burrow_stage") |> 
  mutate(shrimp_contact = ifelse(is.na(shrimp_contact), ifelse(goby_out == 1, 0, 1 - goby_out), shrimp_contact))

write_csv(final_df, "final_df.csv")
```

#2. Statistical analysis using zero-one inflated beta regression
##2.1 Building a global model
```{r}
#building a global model for the proportion of time gobies spent out of the burrow
zoib_formula <- bf(
  # mu (mean) part
  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # phi (precision) part
  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # alpha (zero-one-inflation) part
  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # The one-inflated part, conditional on the 0s
  coi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),

  family = zero_one_inflated_beta()
)
```

##2.2 Specifying priors
###2.2.1 Checking default priors
```{r}
get_prior(
  zoib_formula,
  data = final_df
)
#we can see that all the beta coefficients are being given a flat prior which means it can take on a value from - infinity to + infinity. All the beta coefficients are on the logit scale so lets plot how changing the value of beta relates to different proportions
```

###2.2.2 Graphing logit~proportion
```{r}
tibble(x = seq(-8, 8, by = 0.1)) |> 
  mutate(y = plogis(x)) |> 
  ggplot(aes(x = x, y = y)) +
  geom_line(size = 1) +
  labs(x = "Logit scale", y = "Probability scale")

#we can see that after -5 or +5 the probability doesn't change much, instead of leaving our priors at the default of + and - infinity, we should say that they are most likely to occur between -5 and +5.
```

###2.2.3 Ploting priors
```{r}
# Generate data points
x <- seq(-20, 20, length.out = 1000)  # Adjusted range for better visualization

# Define parameters for the distributions
loc_logistic <- 0
scale_logistic <- 3

df_student_t <- 3
loc_student_t <- 0
scale_student_t <- 2.5

loc_normal <- 0
scale_normal <- 5

# Calculate PDFs
pdf_logistic <- dlogis(x, location = loc_logistic, scale = scale_logistic)
pdf_student_t <- dt(x, df = df_student_t)
pdf_normal <- dnorm(x, mean = loc_normal, sd = scale_normal)

# Plot the PDFs
df <- data.frame(x = x, Logistic = pdf_logistic, Student_t = pdf_student_t, Normal = pdf_normal)
ggplot(df, aes(x)) +
  geom_line(aes(y = Logistic, color = "Logistic(0, 3)")) + # Default priors of Logistic(0,1) have been broadened as these priors seemed too restrictive
  geom_line(aes(y = Student_t, color = "Student_t(3, 0, 2.5)")) +
  geom_line(aes(y = Normal, color = "Normal(0, 5)")) + #For the beta coefficient prior, we will set it to be normally distributed around 0 with an sd of 5, here is the plotted prior distribution 
  labs(title = "Probability Density Functions",
       x = "x",
       y = "Probability Density") +
  scale_color_manual(name = "Distribution", values = c("Logistic(0, 3)" = "blue", "Student_t(3, 0, 2.5)" = "green", "Normal(0, 5)" = "red")) +
  theme_minimal()
```

###2.2.4 Setting priors 
```{r}
#the priors for the intercept have been left as the default and the coefficient priors defined above
priors <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "coi"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "zoi"),
            set_prior("student_t(3, 0, 2.5)", class = "Intercept", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "zoi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "coi", lb = 0),
            set_prior("normal(0, 5)", class = "b"),
            set_prior("normal(0, 5)", class = "b", dpar = "phi"),
            set_prior("normal(0, 5)", class = "b", dpar = "zoi"),
            set_prior("normal(0, 5)", class = "b", dpar = "coi"))
```

###2.2.5 Prior predictive check 
```{r}
prior_formula <- bf(
  # mu (mean) part
  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # phi (precision) part
  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # alpha (zero-one-inflation) part
  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # The one-inflated part, conditional on the 0s
  coi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),

  family = zero_one_inflated_beta()
)

prior_model <- brm(
  prior_formula,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 1000, warmup = 100,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 12345,
  sample_prior = "only",
  file = "prior_check"
)

pp_check(prior_model, ndraws=20)
pp_check(prior_model, ndraws=100, type = 'stat', stat = 'mean')
```

##2.3 Modelling the proportion of time gobies spent outside of the burrow
```{r}
goby_out_formula_1 <- bf(
  # mu (mean) part
  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # phi (precision) part
  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # alpha (zero-one-inflation) part
  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # The one-inflated part, conditional on the 0s
  coi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),

  family = zero_one_inflated_beta()
)

goby_out_model <- brm(
  goby_out_formula_1,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 12345,
  file = "goby_out_model",

)

summary(goby_out_model)
```
###2.3.1 Model fit and diagnostics
####2.3.1.1 Model convergence
```{r}
#convergence diagnostics (R-hat)
extract_rhats <- function(model) {
  model_summary <- summary(model)
  #extract R-hat values for fixed effects
  fixed_rhats <- model_summary$fixed[, "Rhat", drop = FALSE]
  #check for random effects and extract R-hat values if present
  if (!is.null(model_summary$random)) {
    random_rhats <- do.call(rbind, lapply(model_summary$random, function(x) x[, "Rhat", drop = FALSE]))
    #combine fixed and random effects R-hat values
    rhats <- rbind(fixed_rhats, random_rhats)
  } else {
    rhats <- fixed_rhats
  }

  return(rhats)
}

extract_rhats(goby_out_model)
```

####2.3.1.2 Model fit
```{r}
#posterior predictive checks
pp_check(goby_out_model, ndraws = 50)

pp_check(goby_out_model, type='stat', stat='mean')

#fitted vs predicted values
summary(fitted(goby_out_model))
summary(predict(goby_out_model))
```

###2.3.2 Posterior marginal effects
####2.3.2.1 Pairwise contrasts of stroke and stage
```{r}
goby_out_contrast_effect <- goby_out_model |>
  emmeans(~ stroke*stage, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

# Extract the relevant contrast information
goby_out_results.table <- as.data.frame(goby_out_contrast_effect) |> 
  filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))

goby_out_results.table

goby_out_contrast_draws <- goby_out_model |>
  emmeans(~ stroke*stage, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise") |> 
  gather_emmeans_draws()
  goby_out_contrast_draws

goby_out_temporal_contrasts <- goby_out_contrast_draws |> 
  filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
  mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post"), "4", "2")))

goby_out_temporal_contrasts$stroke <- factor(goby_out_temporal_contrasts$stroke, levels = c("Control", "4", "2"))

fig.goby_out_temporal_contrasts<- ggplot(goby_out_temporal_contrasts, aes(x = .value, y = factor(contrast, levels = c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")), color = stroke, fill = stroke)) +
   geom_vline(xintercept = 0, color = "black", size = 0.5) +
  stat_halfeye(.width = c(0.89, 0.95))+
  scale_color_manual(values = c(colour11, colour12, colour13)) +
  scale_fill_manual(values = alpha(c(colour1, colour2, colour3), 0.8)) +
  labs(y = "Contrasts of the time periods relative to noise exposure",
       fill = "Noise treatment", color = "Noise treatment",
       fill_ramp = "Credible interval") +
  xlab(NULL) +
  coord_flip() +
  theme(legend.position = "right", 
        axis.text.x = element_text(angle = 50, hjust =1)) +
  scale_y_discrete(labels = c("Pre - During", "Pre - Post", "Pre - During", "Pre - Post", "Pre - During", "Pre - Post")) +
  scale_x_continuous(breaks = seq(-0.4, 0.5, 0.1), labels = c("-0.4","-0.3", "-0.2","-0.1" , "0", "0.1", "0.2", "0.3", "0.4", "0.5"), limits = c(-0.4, 0.4))

fig.goby_out_temporal_contrasts
```
###2.3.3 Plot of raw data and predicted estimates
####2.3.3.1 Extracting model estimates
```{r}
goby_out_model_estimates <- goby_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA)

goby_out_model_estimates <- as.data.frame(goby_out_model_estimates)

goby_out_model_estimates

write.csv(goby_out_model_estimates, "goby_out_model_estimates.csv")

goby_out_model_estimates_control <- goby_out_model_estimates |> 
  filter(stroke == "control") |> 
  rename(.value = emmean)

goby_out_model_estimates_four <- goby_out_model_estimates |> 
  filter(stroke == "4")|> 
  rename(.value = emmean)

goby_out_model_estimates_two <- goby_out_model_estimates |> 
  filter(stroke == "2")|> 
  rename(.value = emmean)
```

####2.3.3.2 Plotting control estimates and raw data
```{r}
goby_control_raw_data <- final_df |> 
  filter(stroke =="control") |> 
  rename(.value = goby_out)

goby_control_raw_data$stage <- factor(goby_control_raw_data$stage, levels = c("Post", "During", "Pre"))

#assigning a value for the baseline mean
goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control %>%
  filter(stage == "Pre") %>%
  pull(.value)

goby_out_fig_control <- ggplot(goby_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_hline(yintercept = goby_out_model_estimates_control_intercept, linetype = "dashed")+
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_control, size = 2, position = position_nudge(x = 0.5)) +
  labs(x="Period relative to treatment") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.title.y = element_text(size = 13, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("Control")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c")) +
  coord_flip()

goby_out_fig_control
```
####2.3.3.3 Plotting 4-stroke estimates and raw data
```{r}
goby_four_raw_data <- final_df |> 
  filter(stroke =="4") |> 
  rename(.value = goby_out)

goby_four_raw_data$stage <- factor(goby_four_raw_data$stage, levels = c("Post", "During", "Pre"))

#assigning a value for the baseline mean
goby_out_model_estimates_four_intercept <- goby_out_model_estimates_four %>%
  filter(stage == "Pre") %>%
  pull(.value)

goby_out_fig_four <- ggplot(goby_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_hline(yintercept = goby_out_model_estimates_four_intercept, linetype = "dashed")+
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_four, size = 2, position = position_nudge(x = 0.5)) +
  ylab("Proportion of time spent out of the burrow")+
  theme(legend.position = "none", 
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.x = element_text(size = 13, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("4-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b")) +
  coord_flip()

goby_out_fig_four
```

####2.3.3.4 Plotting 2-stroke estimates and raw data
```{r}
goby_two_raw_data <- final_df |> 
  filter(stroke =="2") |> 
  rename(.value = goby_out)

goby_two_raw_data$stage <- factor(goby_two_raw_data$stage, levels = c("Post", "During", "Pre"))

goby_out_model_estimates_two_intercept <- goby_out_model_estimates_two %>%
  filter(stage == "Pre") %>%
  pull(.value)

goby_out_fig_two <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_hline(yintercept = goby_out_model_estimates_two_intercept, linetype = "dashed")+
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_two, size = 2, position = position_nudge(x = 0.5)) +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("2-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a")) +
  coord_flip()

goby_out_fig_two
```
####2.3.3.5 Combining plots into one window
```{r}
# Combine the plots
goby_out_plot <- goby_out_fig_control + goby_out_fig_four + goby_out_fig_two + 
  plot_layout(ncol = 3)

# Display the combined plot
goby_out_plot

ggsave("goby_out_plot.png", plot = goby_out_plot, units = "px", width = 1500, height = 800, dpi = 320, scale = 2)
```

###2.3.4 Modelling the effect of covariates on the proportion of time gobies spent outside of the burrow
####2.3.4.1 Goby number
```{r}
goby_out_goby_number <- goby_out_model |>
  emmeans(~ goby_number, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")

goby_out_goby_number

goby_out_goby_number_draws <- goby_out_model |>
  emmeans(~ goby_number, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")|> 
  gather_emmeans_draws()

goby_out_goby_number_fig<- ggplot(goby_out_goby_number_draws, aes(x = .value, y = contrast)) +
   geom_vline(xintercept = 0, color = "black", size = 0.5) +
  stat_halfeye(.width = c(0.95))+
  labs(y = "Contrasts of the effect of the number of goby",
       fill = "Noise treatment", color = "Noise treatment",
       fill_ramp = "Credible interval") +
  xlab(NULL) +
  coord_flip()

goby_out_goby_number_fig
```

####2.3.4.2 Shrimp number
```{r}
goby_out_shrimp_number <- goby_out_model |>
  emmeans(~ shrimp_number, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")

goby_out_shrimp_number

goby_out_shrimp_number_estimates <- goby_out_model |>
  emmeans(~ shrimp_number, 
          epred = TRUE,
          re_formla = NULL)

goby_out_shrimp_number_estimates

goby_out_shrimp_number_draws <- goby_out_model |>
  emmeans(~ shrimp_number, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")|> 
  gather_emmeans_draws()

goby_out_shrimp_number_fig<- ggplot(goby_out_shrimp_number_draws, aes(x = .value, y = contrast)) +
   geom_vline(xintercept = 0, color = "black", size = 0.5) +
  stat_halfeye(.width = c(0.95))+
  labs(y = "Contrasts of the effect of the number of shrimp",
       fill = "Noise treatment", color = "Noise treatment",
       fill_ramp = "Credible interval") +
  xlab(NULL) +
  coord_flip()

goby_out_shrimp_number_fig
```

####2.3.4.3 Shrimp species
```{r}
goby_out_shrimp_species <- goby_out_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")

goby_out_shrimp_species

goby_out_shrimp_species_estimates <- goby_out_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL)

goby_out_shrimp_species_estimates

goby_out_shrimp_species_draws <- goby_out_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")|> 
  gather_emmeans_draws()

goby_out_shrimp_species_fig<- ggplot(goby_out_shrimp_species_draws, aes(x = .value, y = contrast)) +
   geom_vline(xintercept = 0, color = "black", size = 0.5) +
  stat_halfeye(.width = c(0.95))+
  labs(y = "Contrasts of the effect of the species of shrimp",
       fill = "Noise treatment", color = "Noise treatment",
       fill_ramp = "Credible interval") +
  xlab(NULL) +
  coord_flip()

goby_out_shrimp_species_fig
```

##2.4 Modelling the proportion of time shrimp spent outside of the burrow
```{r}
shrimp_out_formula <- bf(
  # mu (mean) part
  shrimp_out ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
  # phi (precision) part
  phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
  # alpha (zero-one-inflation) part
  zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
  # The one-inflated part, conditional on the 0s
  coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),

  family = zero_one_inflated_beta()
)

shrimp_out_model <- brm(
  shrimp_out_formula,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 12345,
  file = "shrimp_out_model"
)

summary(shrimp_out_model)
```

###2.4.1 Model fit and diagnostics
####2.4.1.1 Model convergence
```{r}
extract_rhats(shrimp_out_model)
```

####2.4.1.2 Model fit
```{r}
#posterior predictive checks
pp_check(shrimp_out_model)

pp_check(shrimp_out_model, type='stat', stat='mean')

#fitted vs predicted values
summary(fitted(shrimp_out_model))
summary(predict(shrimp_out_model))
```

###2.4.2 Posterior marginal effects
####2.4.2.1 Pairwise contrasts of stroke and stage
```{r}
shrimp_out_contrasts <- shrimp_out_model |>
  emmeans(~ stroke*stage, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

# Extract the relevant contrast information
shrimp_out_contrasts <- as.data.frame(shrimp_out_contrasts) |> 
  filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))

shrimp_out_contrasts

shrimp_out_contrast_draws <- shrimp_out_model  |>
  emmeans(~ stroke*stage, 
          epred = TRUE,
          re_formula = NA) |> 
  contrast(method = "revpairwise") |> 
  gather_emmeans_draws()

shrimp_out_temporal_contrasts <- shrimp_out_contrast_draws |> 
  filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
  mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post"), "4", "2")))

shrimp_out_temporal_contrasts$stroke <- factor(shrimp_out_temporal_contrasts$stroke, levels = c("Control", "4", "2"))

shrimp_out_temporal_contrasts_fig <- ggplot(shrimp_out_temporal_contrasts, aes(x = .value, y = factor(contrast, levels = c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post",  "2 Pre - 2 During", "2 Pre - 2 Post")), color = stroke, fill = stroke)) +
  geom_vline(xintercept = 0, color = "black", size = 0.5) +
  stat_halfeye(.width = c(0.89, 0.95)) +
  scale_color_manual(values = c(colour11, colour12, colour13)) +
  scale_fill_manual(values = alpha(c(colour1, colour2, colour3), 0.8)) +
  labs(x = "Difference in the proportion of time spent out of the burrow",
       y = "Contrasts of the time periods relative to noise exposure",
       fill = "Noise treatment", color = "Noise treatment",
       fill_ramp = "Credible interval") +
  coord_flip() +
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 50, hjust =1)) +
  scale_y_discrete(labels = c("Pre - During", "Pre - Post", "Pre - During", "Pre - Post", "Pre - During", "Pre - Post")) +
  scale_x_continuous(breaks = seq(-0.2, 0.3, 0.1), labels = c("-0.2","-0.1" , "0", "0.1", "0.2", "0.3"), limits = c(-0.3, 0.4))

shrimp_out_temporal_contrasts_fig
```
###2.4.3 Plot of raw data and predicted estimates
####2.4.3.1 Extracting model estimates
```{r}
shrimp_out_model_estimates <- shrimp_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA)

shrimp_out_model_estimates <- as.data.frame(shrimp_out_model_estimates)

shrimp_out_model_estimates

write.csv(shrimp_out_model_estimates, "shrimp_out_model_estimates.csv")

shrimp_out_model_estimates_control <- shrimp_out_model_estimates |> 
  filter(stroke == "control") |> 
  rename(.value = emmean)

shrimp_out_model_estimates_four <- shrimp_out_model_estimates |> 
  filter(stroke == "4")|> 
  rename(.value = emmean)

shrimp_out_model_estimates_two <- shrimp_out_model_estimates |> 
  filter(stroke == "2")|> 
  rename(.value = emmean)
```

####2.4.3.2 Plotting control estimates and raw data
```{r}
shrimp_control_raw_data <- final_df |> 
  filter(stroke =="control") |> 
  rename(.value = shrimp_out)

shrimp_control_raw_data$stage <- factor(shrimp_control_raw_data$stage, levels = c("Post", "During", "Pre"))

#assigning a value for the baseline mean
shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control %>%
  filter(stage == "Pre") %>%
  pull(.value)

shrimp_out_fig_control <- ggplot(shrimp_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_hline(yintercept = shrimp_out_model_estimates_control_intercept, linetype = "dashed")+
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_control, size = 2, position = position_nudge(x = 0.5)) +
  labs(x="Period relative to treatment")+
    theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.title.y = element_text(size = 13, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("Control")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c")) +
  coord_flip()

shrimp_out_fig_control
```

####2.4.3.3 Plotting 4-stroke estimates and raw data
```{r}
shrimp_four_raw_data <- final_df |> 
  filter(stroke =="4") |> 
  rename(.value = shrimp_out)

shrimp_four_raw_data$stage <- factor(shrimp_four_raw_data$stage, levels = c("Post", "During", "Pre"))

#assigning a value for the baseline mean
shrimp_out_model_estimates_four_intercept <- shrimp_out_model_estimates_four %>%
  filter(stage == "Pre") %>%
  pull(.value)

shrimp_out_fig_four <- ggplot(shrimp_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_hline(yintercept = shrimp_out_model_estimates_four_intercept, linetype = "dashed")+
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_four, size = 2, position = position_nudge(x = 0.5)) +
  ylab("Proportion of time spent out of the burrow")+
  theme(legend.position = "none", 
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.x = element_text(size = 13, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("4-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b")) +
  coord_flip()

shrimp_out_fig_four
```

####2.4.3.4 Plotting 2-stroke estimates and raw data
```{r}
shrimp_two_raw_data <- final_df |> 
  filter(stroke =="2") |> 
  rename(.value = shrimp_out)

#reordering the levels 
shrimp_two_raw_data$stage <- factor(shrimp_two_raw_data$stage, levels = c("Post", "During", "Pre"))

#assigning a value for the baseline mean
shrimp_out_model_estimates_two_intercept <- shrimp_out_model_estimates_two %>%
  filter(stage == "Pre") %>%
  pull(.value)

shrimp_out_fig_two <- ggplot(shrimp_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_hline(yintercept = shrimp_out_model_estimates_two_intercept, linetype = "dashed")+
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_two, size = 2, position = position_nudge(x = 0.5)) +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("2-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a")) +
  coord_flip()

shrimp_out_fig_two
```

####2.4.3.5 Combining plots into one window
```{r}
shrimp_out_plot <- shrimp_out_fig_control + shrimp_out_fig_four + shrimp_out_fig_two + 
  plot_layout(ncol = 3)

shrimp_out_plot

ggsave("shrimp_out_plot.png", plot = shrimp_out_plot, units = "px", width = 1500, height = 800, dpi = 320, scale = 2)

```

###2.4.4 Modelling the effect of covariates on the proportion of time gobies spent outside of the burrow
####2.4.4.1 Goby number
```{r}
shrimp_out_goby_number_contrasts <- shrimp_out_model |>
  emmeans(~ goby_number, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

shrimp_out_goby_number_contrasts
```

####2.4.4.2 Shrimp number
```{r}
shrimp_out_shrimp_number_contrasts <- shrimp_out_model |>
  emmeans(~ shrimp_number, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

shrimp_out_shrimp_number_contrasts

shrimp_out_shrimp_number_estimates <- shrimp_out_model |>
  emmeans(~ shrimp_number, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000)

shrimp_out_shrimp_number_estimates

shrimp_out_shrimp_number_contrasts <- shrimp_out_model |>
  emmeans(~ shrimp_number, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise") |> 
  gather_emmeans_draws()

ggplot(data = shrimp_out_shrimp_number_contrasts, aes(x = contrast, y = .value )) +
  stat_halfeye()
```
####2.4.4.3 Shrimp species
```{r}
shrimp_out_shrimp_species_contrasts <- shrimp_out_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

shrimp_out_shrimp_species_contrasts

shrimp_out_shrimp_species_contrasts <- shrimp_out_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise") |> 
  gather_emmeans_draws()

ggplot(data = shrimp_out_shrimp_species_contrasts, aes(x = contrast, y = .value )) +
  stat_halfeye()
```

##2.5 Modelling the proportion of time shrimp spent in contact with the goby
###2.5.1 Checking the response variable distribution
```{r}
shrimp_contact_df <- final_df |> 
  mutate(is_zero = shrimp_contact == 0)

shrimp_contact_plot <- shrimp_contact_df |> 
  mutate(shrimp_contact = ifelse(is_zero, -0.1, shrimp_contact)) |> 
  ggplot(aes(x = shrimp_contact)) +
  geom_histogram(aes(fill = is_zero), binwidth = 0.05, 
                 boundary = 0, color = "white") +
  geom_vline(xintercept = 0)
shrimp_contact_plot
# Distribution is a zero-one inflated beta distribution, because the value for shrimp_contact is bounded by 0-1 as it is a proportion of the total time and there is values of 0 and 1.
```

###2.5.2 Running the model
```{r}
shrimp_contact_model <- brm(
  bf(shrimp_contact ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow)
     ),
  data = final_df,
  prior = priors,
  family = zero_one_inflated_beta(),
  control = list(adapt_delta = 0.99, max_treedepth = 12),
  chains = 4, iter = 6000, warmup = 1000, seed = 12345, backend = "cmdstanr", cores = 4, threads = threading(2),
  file = "shrimp_contact_model"
)

summary(shrimp_contact_model)
```

###2.5.3 Model fit and diagnostics
####2.5.3.1 Model convergence
```{r}
extract_rhats(shrimp_contact_model)
```

####2.5.3.2 Model fit
```{r}
#posterior predictive checks
pp_check(shrimp_contact_model)

pp_check(shrimp_contact_model, type='stat', stat='mean')

#fitted vs predicted values
summary(fitted(shrimp_contact_model))
summary(predict(shrimp_contact_model))
```

###2.5.2 Posterior marginal effects
####2.5.2.1 Pairwise contrasts of stroke and stage
```{r}
shrimp_contact_contrasts <- shrimp_contact_model |>
  emmeans(~ stroke*stage, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

# Extract the relevant contrast information
shrimp_contact_contrasts <- as.data.frame(shrimp_contact_contrasts) |> 
  filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))

shrimp_contact_contrasts

shrimp_contact_contrasts_draws <- shrimp_contact_model  |>
  emmeans(~ stroke*stage, 
          epred = TRUE,
          re_formula = NA) |> 
  contrast(method = "revpairwise") |> 
  gather_emmeans_draws()

shrimp_contact_temporal_contrasts <- shrimp_contact_contrasts_draws |> 
  filter(contrast %in% c("control Pre - control During", "control Pre - control Post","control Post - control During" , "4 Pre - 4 During", "4 Pre - 4 Post", "4 Post - 4 During", "2 Pre - 2 During", "2 Pre - 2 Post", "2 Post - 2 During")) |> 
  mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post","control Post - control During"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post", "4 Post - 4 During"), "4", "2")))

shrimp_contact_temporal_contrasts$stroke <- factor(shrimp_contact_temporal_contrasts$stroke, levels = c("Control", "4", "2"))

shrimp_contact_temporal_fig<- ggplot(shrimp_contact_temporal_contrasts, aes(x = .value, y = factor(contrast, levels = c("control Pre - control During", "control Pre - control Post","control Post - control During" , "4 Pre - 4 During", "4 Pre - 4 Post", "4 Post - 4 During", "2 Pre - 2 During", "2 Pre - 2 Post", "2 Post - 2 During")), color = stroke, fill = stroke)) +
   geom_vline(xintercept = 0, color = "black", size = 0.5) +
  stat_halfeye(.width = c(0.89, 0.95)) +
  scale_color_manual(values = c(colour11, colour12, colour13)) +
  scale_fill_manual(values = alpha(c(colour1, colour2, colour3), 0.8)) +
  labs(x = "Difference in the proportion of time spent out of the burrow",
       y = "Contrasts of the time periods relative to noise exposure",
       fill = "Noise treatment", color = "Noise treatment",
       fill_ramp = "Credible interval") +
  coord_flip() +
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 50, hjust =1)) +
  scale_y_discrete(labels = c("Pre - During", "Pre - Post","Post - During" , "Pre - During", "Pre - Post", "Post - During", "Pre - During", "Pre - Post", "Post - During")) +
  scale_x_continuous(breaks = seq(-0.2, 0.3, 0.1), labels = c("-0.2","-0.1" , "0", "0.1", "0.2", "0.3"), limits = c(-0.2, 0.3))

shrimp_contact_temporal_fig
```

###2.5.3 Plot of raw data and predicted estimates
####2.5.3.1 Extracting model estimates
```{r}

shrimp_contact_model_estimates <- shrimp_contact_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA)

shrimp_contact_model_estimates <- as.data.frame(shrimp_contact_model_estimates)

shrimp_contact_model_estimates

write.csv(shrimp_contact_model_estimates, "shrimp_contact_model_estimates.csv")

shrimp_contact_model_estimates_control <- shrimp_contact_model_estimates |> 
  filter(stroke == "control") |> 
  rename(.value = emmean)

shrimp_contact_model_estimates_four <- shrimp_contact_model_estimates |> 
  filter(stroke == "4")|> 
  rename(.value = emmean)

shrimp_contact_model_estimates_two <- shrimp_contact_model_estimates |> 
  filter(stroke == "2")|> 
  rename(.value = emmean)

```

####2.5.3.2 Plotting control estimates and raw data
```{r}
shrimp_contact_control_raw_data <- final_df |> 
  filter(stroke =="control") |> 
  rename(.value = shrimp_contact)

shrimp_contact_control_raw_data$stage <- factor(shrimp_contact_control_raw_data$stage, levels = c("Post", "During", "Pre"))

shrimp_contact_fig_control <- ggplot(shrimp_contact_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_control, size = 2, position = position_nudge(x = 0.5)) +
    theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        plot.title = element_textbox_simple(size = 12, halign = 0.5, linewidth = 0.5, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"))+
  ggtitle("Control")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c")) +
  coord_flip()

shrimp_contact_fig_control
```

####2.5.3.3 Plotting 4-stroke estimates and raw data
```{r}
shrimp_contact_four_raw_data <- final_df |> 
  filter(stroke =="4") |> 
  rename(.value = shrimp_contact)

shrimp_contact_four_raw_data$stage <- factor(shrimp_contact_four_raw_data$stage, levels = c("Post", "During", "Pre"))

shrimp_contact_fig_four <- ggplot(shrimp_contact_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_four, size = 2, position = position_nudge(x = 0.5)) +
    theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.title = element_textbox_simple(size = 12, halign = 0.5, linewidth = 0.5, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"))+
  ggtitle("4-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b")) +
  coord_flip()

shrimp_contact_fig_four
```

####2.5.3.4 Plotting 2-stroke estimates and raw data
```{r}
shrimp_contact_two_raw_data <- final_df |> 
  filter(stroke =="2") |> 
  rename(.value = shrimp_contact)

shrimp_contact_two_raw_data$stage <- factor(shrimp_contact_two_raw_data$stage, levels = c("Post", "During", "Pre"))

shrimp_contact_fig_two <- ggplot(shrimp_contact_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_two, size = 2, position = position_nudge(x = 0.5)) +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.title = element_textbox_simple(size = 12, halign = 0.5, linewidth = 0.5, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"))+
  ggtitle("2-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a")) +
  coord_flip()

shrimp_contact_fig_two
```

####2.5.3.5 Combining plots into one window
```{r}
# Combine the plots
shrimp_contact_plot <- shrimp_contact_fig_control + shrimp_contact_fig_four + shrimp_contact_fig_two + 
  plot_layout(ncol = 3)

# Display the combined plot
shrimp_contact_plot
```
###2.5.4 Modelling the effect of covariates on the proportion of time spent in contact
####2.5.4.1 Goby number
```{r}
shrimp_contact_goby_number_contrasts <- shrimp_contact_model |>
  emmeans(~ goby_number, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

shrimp_contact_goby_number_contrasts
```

####2.5.4.2 Shrimp number
```{r}
shrimp_contact_shrimp_number_contrasts <- shrimp_contact_model |>
  emmeans(~ shrimp_number, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

shrimp_contact_shrimp_number_contrasts
```

####2.5.4.2 Shrimp species
```{r}
shrimp_contact_shrimp_species_contrasts <- shrimp_contact_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

shrimp_contact_shrimp_species_contrasts
```

####2.5.4.3 Overall model estimate for the proportion of time shrimp spent in contact with a goby
```{r}
shrimp_contact_model |>
  emmeans(~ 1, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000)
```

### 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
adding knitting setting to cache
test
changing authors

@@
 title: "shrimp_goby_boatnoise"
-author: "Jack Manera"
+author: "Jack L Manera & Jake M Martin"
 date: "`r format(Sys.time(), '%d %B %Y')`"
@@
 ---
+
+This is a test from the cooding god
+
+```{r setup, include = FALSE}
+#kniter setting
+knitr::opts_chunk$set(
+message = FALSE,
+warning = FALSE, # no warnings
+cache = TRUE,# Cacheing to save time when kniting
+tidy = TRUE
+)
+```
 

### 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
removing redundant text
updating the directory structure

@@
 
-This is a test from the cooding god
-
 ```{r setup, include = FALSE}
@@
 #assigning the directory so that the code can be universally read on any computer as long as the entire project file is shared
-directory <- './1-data/'
+directory <- './2-data/'
 
 #reading in the coded raw BORIS output
-BORIS_output <- read.csv("./1-data/BORIS_output_update.csv")
+BORIS_output <- read.csv("./2-data/BORIS_output_update.csv")
 
 #reading in the decoder
-Video_codes <- read.csv("./1-data/Video_codes.csv")
-
-shrimp_species <- read.csv("./1-data/species.csv")
+Video_codes <- read.csv("./2-data/Video_codes.csv")
+
+shrimp_species <- read.csv("./2-data/species.csv")
 

### 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
remove text
annotating code
error fishing

@@
 
+#reading in shrimp species information
 shrimp_species <- read.csv("./2-data/species.csv")
-
-length(unique(BORIS_output$code))
-
+#error fishing
 #binding the decoder to the BORIS output and revealing the treatment and stage

### 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
error fishing

--- 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
@@
 
+#reading in shrimp species information
 shrimp_species <- read.csv("./2-data/species.csv")
-
-length(unique(BORIS_output$code))
-
+#error fishing take 2
 #binding the decoder to the BORIS output and revealing the treatment and stage

### 2024-10-22 ms_boatnoise_shrimp_goby.Rmd
removing comment
Changed a lot of the figures and cleaned up the directory storage so that certain folders can be ignored

--- 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr)
+pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr, gghalves, ggpp, rstan)
 
@@
 
+#reading in shrimp species information
 shrimp_species <- read.csv("./2-data/species.csv")
-
-length(unique(BORIS_output$code))
 
@@
   group_by(unique_id) |> 
-  filter(behaviour == 'INSIDE' | behaviour == 'EDGE' | behaviour == 'NEAR' | behaviour == 'AWAY' |behaviour == 'CONTACT' |behaviour == 'APART' ) |>
+  dplyr::filter(behaviour == 'INSIDE' | behaviour == 'EDGE' | behaviour == 'NEAR' | behaviour == 'AWAY' |behaviour == 'CONTACT' |behaviour == 'APART' ) |>
   mutate(averageduration = sum(duration))
@@
   group_by(burrow, species, individual) |> 
-  filter(sum(averageduration) != 0)
+  dplyr::filter(sum(averageduration) != 0)
 ```
@@
 fixeddf1 <- workingdf3 |> 
-  filter(averageduration == 0) |> 
+  dplyr::filter(averageduration == 0) |> 
   mutate(duration = ifelse(species == "Goby" & behaviour == "AWAY", 300, duration),
@@
 fixeddf2 <- workingdf3 |> 
-  filter(averageduration != 0)
+  dplyr::filter(averageduration != 0)
 
@@
   ungroup() |> 
-  filter(individual == 1)
+  dplyr::filter(individual == 1)
 
@@
 goby_df <- workingdf7 |> 
-  filter(species == "Goby") |> 
+  dplyr::filter(species == "Goby") |> 
   rename(goby_out = away, goby_total = total, goby_number = number_conspecifics) |> 
@@
 shrimp_df <- workingdf7 |> 
-  filter(species == "Shrimp") |> 
+  dplyr::filter(species == "Shrimp") |> 
   rename(shrimp_out = away, shrimp_total = total, shrimp_number = number_conspecifics) |> 
@@
 
-write_csv(final_df, "final_df.csv")
+write_csv(final_df, "./2-data/final_df.csv")
 ```
@@
 goby_out_results.table <- as.data.frame(goby_out_contrast_effect) |> 
-  filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
+  dplyr::filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
 
@@
 goby_out_temporal_contrasts <- goby_out_contrast_draws |> 
-  filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
+  dplyr::filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
   mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post"), "4", "2")))
@@
 ```
-###2.3.3 Plot of raw data and predicted estimates
-####2.3.3.1 Extracting model estimates
+###2.3.3 Extracting and plotting model estimates
+####2.3.3.1 Extracting estimates
 ```{r}
@@
 
-write.csv(goby_out_model_estimates, "goby_out_model_estimates.csv")
-
+write.csv(goby_out_model_estimates, "./2-data/goby_out_model_estimates.csv")
+
+#Storing the model estimate means for each group to plot later on
 goby_out_model_estimates_control <- goby_out_model_estimates |> 
-  filter(stroke == "control") |> 
+  dplyr::filter(stroke == "control") |> 
   rename(.value = emmean)
@@
 goby_out_model_estimates_four <- goby_out_model_estimates |> 
-  filter(stroke == "4")|> 
+  dplyr::filter(stroke == "4")|> 
   rename(.value = emmean)
@@
 goby_out_model_estimates_two <- goby_out_model_estimates |> 
-  filter(stroke == "2")|> 
+  dplyr::filter(stroke == "2")|> 
   rename(.value = emmean)
 ```
-
-####2.3.3.2 Plotting control estimates and raw data
-```{r}
+####2.3.3.2 Plotting model estimates and raw data
+```{r}
+goby_out_model_draws <- goby_out_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+goby_out_model_draws <- goby_out_model_draws |> 
+  rename(emmean = .value)
+
+goby_out_raw_data <- final_df |> 
+  rename(emmean = goby_out)
+
+goby_out_raw_data$stage <- factor(goby_out_raw_data$stage, levels = c("Pre", "During", "Post"))
+goby_out_raw_data$stroke <- factor(goby_out_raw_data$stroke, levels = c("control", "4", "2"))
+
+goby_out_model_estimates$stage <- factor(goby_out_model_estimates$stage, levels = c("Pre", "During", "Post"))
+goby_out_model_estimates$stroke <- factor(goby_out_model_estimates$stroke, levels = c("control", "4", "2"))
+
+goby_out_model_draws$stage <- factor(goby_out_model_draws$stage, levels = c("Pre", "During", "Post"))
+goby_out_model_draws$stroke <- factor(goby_out_model_draws$stroke, levels = c("control", "4", "2"))
+
+goby_out_means <- goby_out_raw_data |> 
+  group_by(stage, stroke) |> 
+  summarise(emmean = mean(emmean))
+
+goby_out_fig_together <- ggplot(data = goby_out_raw_data, aes(x = stage, y = emmean, color = stroke, fill = stroke)) +
+  geom_point(data = goby_out_means, alpha = 1, position = position_dodgenudge(width = 0.8, x = -0.09), size = 9, shape = "_") +
+  geom_half_point(alpha = 0.3, position = position_dodgenudge(width = 0.8, x = -0.03), side = "l", range_scale = 0.5) +
+  geom_half_violin(data = goby_out_model_draws, aes(x = stage, y = emmean, color = stroke, fill = stroke), alpha = 0.6, position = position_dodge(width = 0.8), side = "r", size = 0) +
+  geom_point(data = goby_out_model_estimates, aes(x = stage, y = emmean, color = stroke), position = position_dodge(width = 0.8), size = 3) +
+  geom_errorbar(data = goby_out_model_estimates, aes(x = stage, y = emmean, ymin = lower.HPD, ymax = upper.HPD, color = stroke), position = position_dodge(width = 0.8), width = 0, size = 1.25) +
+  scale_fill_manual(values = c("control" = "#76A34A", "4" = "#F29E00", "2" = "#E25A00"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
+  scale_color_manual(values = c("control" = "#2A330E", "4" = "#805213", "2" = "#542709"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
+  scale_x_discrete(labels = c("Pre", "During", "Post")) +
+  labs(title = "The effects of boat noise on goby burrow use",
+       y = "Proportion of time in out of the burrow",
+       x = "Experimental phase relative to noise exposure") +
+  theme_classic() +
+  theme(
+    axis.text.x = element_text(size = 10, margin = margin(t = 5)),  
+    axis.text.y = element_text(size = 10, margin = margin(r = 5)),  
+    axis.title.x = element_text(size = 13, margin = margin(t = 10)),
+    axis.title.y = element_text(size = 13, margin = margin(r = 10)),
+    legend.text = element_text(size = 10),
+    legend.title = element_text(size = 10),
+    legend.position = "right",
+    legend.justification = "top",
+    plot.title = element_text(hjust = 0.5, size = 16),  
+    plot.margin = margin(10, 10, 10, 10)
+  )
+
+goby_out_fig_together
+ggsave("./3-figs/goby_out_fig_together.png", plot = goby_out_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
+```
+
+####2.3.3.3 Plotting control estimates and raw data
+```{r}
+goby_out_model_draws <- goby_out_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+goby_out_raw_data <- final_df |>
+  rename(.value = goby_out)
+
+goby_out_model_draws$stage <- factor(goby_out_model_draws$stage, levels = c("Pre", "During", "Post"))
+goby_out_model_draws$stroke <- factor(goby_out_model_draws$stroke, levels = c("control", "4", "2"))
+
+goby_out_control_model_draws <- goby_out_model_draws |> 
+  dplyr::filter(stroke == "control")
+
 goby_control_raw_data <- final_df |> 
-  filter(stroke =="control") |> 
+  dplyr::filter(stroke =="control") |> 
   rename(.value = goby_out)
 
-goby_control_raw_data$stage <- factor(goby_control_raw_data$stage, levels = c("Post", "During", "Pre"))
+goby_control_means <- goby_control_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+goby_control_raw_data$stage <- factor(goby_control_raw_data$stage, levels = c("Pre", "During", "Post"))
 
@@
 goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control %>%
-  filter(stage == "Pre") %>%
+  dplyr::filter(stage == "Pre") %>%
   pull(.value)
@@
 goby_out_fig_control <- ggplot(goby_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_violin(alpha = 0.7, size = 0) +
-  geom_hline(yintercept = goby_out_model_estimates_control_intercept, linetype = "dashed")+
-  geom_jitter(width = 0.1) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
-  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_control, size = 2, position = position_nudge(x = 0.5)) +
-  labs(x="Period relative to treatment") +
+  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = goby_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  labs(x="Period relative to treatment",
+       y="Proportion of time out of burrow") +
   theme(legend.position = "none", 
         axis.title.x = element_blank(), 
-        axis.title.y = element_text(size = 13, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
-        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_text(size = 13),
+        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
         panel.background = element_rect(fill = "white", colour = "black"),
-        panel.grid.major.x = element_line(colour = "#ededed"),
         plot.background = element_rect(fill = NA, colour = NA))+
@@
   scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c")) +
-  coord_flip()
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))
 
@@
 ```
-####2.3.3.3 Plotting 4-stroke estimates and raw data
-```{r}
+####2.3.3.4 Plotting 4-stroke estimates and raw data
+```{r}
+goby_out_control_model_draws <- goby_out_model_draws |> 
+  dplyr::filter(stroke == "4")
+
 goby_four_raw_data <- final_df |> 
-  filter(stroke =="4") |> 
+  dplyr::filter(stroke =="4") |> 
   rename(.value = goby_out)
 
-goby_four_raw_data$stage <- factor(goby_four_raw_data$stage, levels = c("Post", "During", "Pre"))
-
-#assigning a value for the baseline mean
-goby_out_model_estimates_four_intercept <- goby_out_model_estimates_four %>%
-  filter(stage == "Pre") %>%
-  pull(.value)
+goby_four_raw_data$stage <- factor(goby_four_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+goby_four_means <- goby_four_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
 
 goby_out_fig_four <- ggplot(goby_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_violin(alpha = 0.7, size = 0) +
-  geom_hline(yintercept = goby_out_model_estimates_four_intercept, linetype = "dashed")+
-  geom_jitter(width = 0.1) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
-  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_four, size = 2, position = position_nudge(x = 0.5)) +
-  ylab("Proportion of time spent out of the burrow")+
+  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = goby_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  xlab("Experimental phase relative to noise exposure")+
   theme(legend.position = "none", 
+        axis.title.y = element_blank(),  
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("4-stroke")+
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))
+
+goby_out_fig_four
+```
+
+####2.3.3.5 Plotting 2-stroke estimates and raw data
+```{r}
+goby_out_control_model_draws <- goby_out_model_draws |> 
+  dplyr::filter(stroke == "2")
+
+goby_two_raw_data <- final_df |> 
+  dplyr::filter(stroke =="2") |> 
+  rename(.value = goby_out)
+
+goby_two_raw_data$stage <- factor(goby_two_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+goby_two_means <- goby_two_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+goby_out_fig_two <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = goby_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  theme(legend.position = "none", 
+        axis.title.x = element_blank(),  
+        axis.text.x = element_text(size = 13),
         axis.title.y = element_blank(), 
@@
         axis.ticks.y = element_blank(), 
-        axis.title.x = element_text(size = 13, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
-        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
         panel.background = element_rect(fill = "white", colour = "black"),
-        panel.grid.major.x = element_line(colour = "#ededed"),
         plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("4-stroke")+
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b")) +
-  coord_flip()
-
-goby_out_fig_four
-```
-
-####2.3.3.4 Plotting 2-stroke estimates and raw data
-```{r}
-goby_two_raw_data <- final_df |> 
-  filter(stroke =="2") |> 
-  rename(.value = goby_out)
-
-goby_two_raw_data$stage <- factor(goby_two_raw_data$stage, levels = c("Post", "During", "Pre"))
-
-goby_out_model_estimates_two_intercept <- goby_out_model_estimates_two %>%
-  filter(stage == "Pre") %>%
-  pull(.value)
-
-goby_out_fig_two <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_violin(alpha = 0.7, size = 0) +
-  geom_hline(yintercept = goby_out_model_estimates_two_intercept, linetype = "dashed")+
-  geom_jitter(width = 0.1) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
-  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_two, size = 2, position = position_nudge(x = 0.5)) +
-  theme(legend.position = "none", 
-        axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        panel.grid.major.x = element_line(colour = "#ededed"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("2-stroke")+
+  ggtitle("2-stroke") +
   scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a")) +
-  coord_flip()
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))
 
@@
 ```
-####2.3.3.5 Combining plots into one window
-```{r}
-# Combine the plots
-goby_out_plot <- goby_out_fig_control + goby_out_fig_four + goby_out_fig_two + 
+####2.3.3.6 Combining plots into one figure
+```{r}
+goby_out_plot3 <- goby_out_fig_control + goby_out_fig_four + goby_out_fig_two + 
   plot_layout(ncol = 3)
 
-# Display the combined plot
-goby_out_plot
-
-ggsave("goby_out_plot.png", plot = goby_out_plot, units = "px", width = 1500, height = 800, dpi = 320, scale = 2)
-```
-
-###2.3.4 Modelling the effect of covariates on the proportion of time gobies spent outside of the burrow
+goby_out_plot3
+ggsave("./3-figs/goby_out_plot3.png", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+```
+
+###2.3.4 Effects of covariates on the proportion of time gobies spent outside of the burrow
 ####2.3.4.1 Goby number
@@
 shrimp_out_contrasts <- as.data.frame(shrimp_out_contrasts) |> 
-  filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
+  dplyr::filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
 
@@
 shrimp_out_temporal_contrasts <- shrimp_out_contrast_draws |> 
-  filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
+  dplyr::filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
   mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post"), "4", "2")))
@@
 ```
-###2.4.3 Plot of raw data and predicted estimates
-####2.4.3.1 Extracting model estimates
+
+###2.4.3 Extracting and plotting model estimates
+####2.4.3.1 Extracting estimates
 ```{r}
@@
 
-write.csv(shrimp_out_model_estimates, "shrimp_out_model_estimates.csv")
-
+write.csv(shrimp_out_model_estimates, "./2-data/shrimp_out_model_estimates.csv")
+
+#Storing the model estimate means for each group to plot later on
 shrimp_out_model_estimates_control <- shrimp_out_model_estimates |> 
-  filter(stroke == "control") |> 
+  dplyr::filter(stroke == "control") |> 
   rename(.value = emmean)
@@
 shrimp_out_model_estimates_four <- shrimp_out_model_estimates |> 
-  filter(stroke == "4")|> 
+  dplyr::filter(stroke == "4")|> 
   rename(.value = emmean)
@@
 shrimp_out_model_estimates_two <- shrimp_out_model_estimates |> 
-  filter(stroke == "2")|> 
+  dplyr::filter(stroke == "2")|> 
   rename(.value = emmean)
 ```
-
-####2.4.3.2 Plotting control estimates and raw data
-```{r}
+####2.4.3.2 Plotting model estimates and raw data
+```{r}
+shrimp_out_model_draws <- shrimp_out_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+shrimp_out_model_draws <- shrimp_out_model_draws |> 
+  rename(emmean = .value)
+
+shrimp_out_raw_data <- final_df |> 
+  rename(emmean = shrimp_out)
+
+shrimp_out_raw_data$stage <- factor(shrimp_out_raw_data$stage, levels = c("Pre", "During", "Post"))
+shrimp_out_raw_data$stroke <- factor(shrimp_out_raw_data$stroke, levels = c("control", "4", "2"))
+
+shrimp_out_model_estimates$stage <- factor(shrimp_out_model_estimates$stage, levels = c("Pre", "During", "Post"))
+shrimp_out_model_estimates$stroke <- factor(shrimp_out_model_estimates$stroke, levels = c("control", "4", "2"))
+
+shrimp_out_model_draws$stage <- factor(shrimp_out_model_draws$stage, levels = c("Pre", "During", "Post"))
+shrimp_out_model_draws$stroke <- factor(shrimp_out_model_draws$stroke, levels = c("control", "4", "2"))
+
+shrimp_out_means <- shrimp_out_raw_data |> 
+  group_by(stage, stroke) |> 
+  summarise(emmean = mean(emmean))
+
+shrimp_out_fig_together <- ggplot(data = shrimp_out_raw_data, aes(x = stage, y = emmean, color = stroke, fill = stroke)) +
+  geom_point(data = shrimp_out_means, alpha = 1, position = position_dodgenudge(width = 0.8, x = -0.09), size = 9, shape = "_") +
+  geom_half_point(alpha = 0.3, position = position_dodgenudge(width = 0.8, x = -0.03), side = "l", range_scale = 0.5) +
+  geom_half_violin(data = shrimp_out_model_draws, aes(x = stage, y = emmean, color = stroke, fill = stroke), alpha = 0.6, position = position_dodge(width = 0.8), side = "r", size = 0) +
+  geom_point(data = shrimp_out_model_estimates, aes(x = stage, y = emmean, color = stroke), position = position_dodge(width = 0.8), size = 3) +
+  geom_errorbar(data = shrimp_out_model_estimates, aes(x = stage, y = emmean, ymin = lower.HPD, ymax = upper.HPD, color = stroke), position = position_dodge(width = 0.8), width = 0, size = 1.25) +
+  scale_fill_manual(values = c("control" = "#76A34A", "4" = "#F29E00", "2" = "#E25A00"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
+  scale_color_manual(values = c("control" = "#2A330E", "4" = "#805213", "2" = "#542709"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
+  scale_x_discrete(labels = c("Pre", "During", "Post")) +
+  labs(title = "The effects of boat noise on shrimp burrow use",
+       y = "Proportion of time in out of the burrow",
+       x = "Experimental phase relative to noise exposure") +
+  theme_classic() +
+  theme(
+    axis.text.x = element_text(size = 10, margin = margin(t = 5)),  
+    axis.text.y = element_text(size = 10, margin = margin(r = 5)),  
+    axis.title.x = element_text(size = 13, margin = margin(t = 10)),
+    axis.title.y = element_text(size = 13, margin = margin(r = 10)),
+    legend.text = element_text(size = 10),
+    legend.title = element_text(size = 10),
+    legend.position = "right",
+    legend.justification = "top",
+    plot.title = element_text(hjust = 0.5, size = 16),  
+    plot.margin = margin(10, 10, 10, 10)
+  )
+
+shrimp_out_fig_together
+ggsave("./3-figs/shrimp_out_fig_together.png", plot = shrimp_out_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
+```
+
+####2.4.3.3 Plotting control estimates and raw data
+```{r}
+shrimp_out_model_draws <- shrimp_out_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+shrimp_out_raw_data <- final_df |>
+  rename(.value = shrimp_out)
+
+shrimp_out_model_draws$stage <- factor(shrimp_out_model_draws$stage, levels = c("Pre", "During", "Post"))
+shrimp_out_model_draws$stroke <- factor(shrimp_out_model_draws$stroke, levels = c("control", "4", "2"))
+
+shrimp_out_control_model_draws <- shrimp_out_model_draws |> 
+  dplyr::filter(stroke == "control")
+
 shrimp_control_raw_data <- final_df |> 
-  filter(stroke =="control") |> 
+  dplyr::filter(stroke =="control") |> 
   rename(.value = shrimp_out)
 
-shrimp_control_raw_data$stage <- factor(shrimp_control_raw_data$stage, levels = c("Post", "During", "Pre"))
+shrimp_control_means <- shrimp_control_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_control_raw_data$stage <- factor(shrimp_control_raw_data$stage, levels = c("Pre", "During", "Post"))
 
@@
 shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control %>%
-  filter(stage == "Pre") %>%
+  dplyr::filter(stage == "Pre") %>%
   pull(.value)
@@
 shrimp_out_fig_control <- ggplot(shrimp_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_violin(alpha = 0.7, size = 0) +
-  geom_hline(yintercept = shrimp_out_model_estimates_control_intercept, linetype = "dashed")+
-  geom_jitter(width = 0.1) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_control, size = 2, position = position_nudge(x = 0.5)) +
-  labs(x="Period relative to treatment")+
+  geom_half_violin(data = shrimp_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = shrimp_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  labs(x="Period relative to treatment",
+       y="Proportion of time out of burrow") +
   theme(legend.position = "none", 
         axis.title.x = element_blank(), 
-        axis.title.y = element_text(size = 13, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
-        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_text(size = 13),
+        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
         panel.background = element_rect(fill = "white", colour = "black"),
-        panel.grid.major.x = element_line(colour = "#ededed"),
         plot.background = element_rect(fill = NA, colour = NA))+
@@
 ```
-
-####2.4.3.3 Plotting 4-stroke estimates and raw data
-```{r}
+####2.4.3.4 Plotting 4-stroke estimates and raw data
+```{r}
+shrimp_out_control_model_draws <- shrimp_out_model_draws |> 
+  dplyr::filter(stroke == "4")
+
 shrimp_four_raw_data <- final_df |> 
-  filter(stroke =="4") |> 
+  dplyr::filter(stroke =="4") |> 
   rename(.value = shrimp_out)
 
-shrimp_four_raw_data$stage <- factor(shrimp_four_raw_data$stage, levels = c("Post", "During", "Pre"))
-
-#assigning a value for the baseline mean
-shrimp_out_model_estimates_four_intercept <- shrimp_out_model_estimates_four %>%
-  filter(stage == "Pre") %>%
-  pull(.value)
+shrimp_four_raw_data$stage <- factor(shrimp_four_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+shrimp_four_means <- shrimp_four_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
 
 shrimp_out_fig_four <- ggplot(shrimp_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_violin(alpha = 0.7, size = 0) +
-  geom_hline(yintercept = shrimp_out_model_estimates_four_intercept, linetype = "dashed")+
-  geom_jitter(width = 0.1) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_four, size = 2, position = position_nudge(x = 0.5)) +
-  ylab("Proportion of time spent out of the burrow")+
+  geom_half_violin(data = shrimp_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = shrimp_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  xlab("Experimental phase relative to noise exposure")+
   theme(legend.position = "none", 
+        axis.title.y = element_blank(),  
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("4-stroke")+
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))
+
+shrimp_out_fig_four
+```
+
+####2.4.3.5 Plotting 2-stroke estimates and raw data
+```{r}
+shrimp_out_control_model_draws <- shrimp_out_model_draws |> 
+  dplyr::filter(stroke == "2")
+
+shrimp_two_raw_data <- final_df |> 
+  dplyr::filter(stroke =="2") |> 
+  rename(.value = shrimp_out)
+
+shrimp_two_raw_data$stage <- factor(shrimp_two_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+shrimp_two_means <- shrimp_two_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_out_fig_two <- ggplot(shrimp_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_half_violin(data = shrimp_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = shrimp_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  theme(legend.position = "none", 
+        axis.title.x = element_blank(),  
+        axis.text.x = element_text(size = 13),
         axis.title.y = element_blank(), 
@@
         axis.ticks.y = element_blank(), 
-        axis.title.x = element_text(size = 13, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
-        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
         panel.background = element_rect(fill = "white", colour = "black"),
-        panel.grid.major.x = element_line(colour = "#ededed"),
         plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("4-stroke")+
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b")) +
-  coord_flip()
-
-shrimp_out_fig_four
-```
-
-####2.4.3.4 Plotting 2-stroke estimates and raw data
-```{r}
-shrimp_two_raw_data <- final_df |> 
-  filter(stroke =="2") |> 
-  rename(.value = shrimp_out)
-
-#reordering the levels 
-shrimp_two_raw_data$stage <- factor(shrimp_two_raw_data$stage, levels = c("Post", "During", "Pre"))
-
-#assigning a value for the baseline mean
-shrimp_out_model_estimates_two_intercept <- shrimp_out_model_estimates_two %>%
-  filter(stage == "Pre") %>%
-  pull(.value)
-
-shrimp_out_fig_two <- ggplot(shrimp_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_violin(alpha = 0.7, size = 0) +
-  geom_hline(yintercept = shrimp_out_model_estimates_two_intercept, linetype = "dashed")+
-  geom_jitter(width = 0.1) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_two, size = 2, position = position_nudge(x = 0.5)) +
-  theme(legend.position = "none", 
-        axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        panel.grid.major.x = element_line(colour = "#ededed"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("2-stroke")+
+  ggtitle("2-stroke") +
   scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a")) +
-  coord_flip()
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))
 
@@
 ```
-
-####2.4.3.5 Combining plots into one window
-```{r}
-shrimp_out_plot <- shrimp_out_fig_control + shrimp_out_fig_four + shrimp_out_fig_two + 
+####2.4.3.6 Combining plots into one figure
+```{r}
+shrimp_out_plot3 <- shrimp_out_fig_control + shrimp_out_fig_four + shrimp_out_fig_two + 
   plot_layout(ncol = 3)
 
-shrimp_out_plot
-
-ggsave("shrimp_out_plot.png", plot = shrimp_out_plot, units = "px", width = 1500, height = 800, dpi = 320, scale = 2)
-
-```
-
-###2.4.4 Modelling the effect of covariates on the proportion of time gobies spent outside of the burrow
+shrimp_out_plot3
+ggsave("./3-figs/shrimp_out_plot3.png", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+```
+
+###2.4.4 Effects of covariates on the proportion of time shrimp spent outside of the burrow
 ####2.4.4.1 Goby number
@@
 shrimp_contact_contrasts <- as.data.frame(shrimp_contact_contrasts) |> 
-  filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
+  dplyr::filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
 
@@
 shrimp_contact_temporal_contrasts <- shrimp_contact_contrasts_draws |> 
-  filter(contrast %in% c("control Pre - control During", "control Pre - control Post","control Post - control During" , "4 Pre - 4 During", "4 Pre - 4 Post", "4 Post - 4 During", "2 Pre - 2 During", "2 Pre - 2 Post", "2 Post - 2 During")) |>
+  dplyr::filter(contrast %in% c("control Pre - control During", "control Pre - control Post","control Post - control During" , "4 Pre - 4 During", "4 Pre - 4 Post", "4 Post - 4 During", "2 Pre - 2 During", "2 Pre - 2 Post", "2 Post - 2 During")) |>
   mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post","control Post - control During"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post", "4 Post - 4 During"), "4", "2")))
@@
 
-###2.5.3 Plot of raw data and predicted estimates
-####2.5.3.1 Extracting model estimates
-```{r}
-
+###2.5.3 Extracting and plotting model estimates
+####2.5.3.1 Extracting estimates
+```{r}
 shrimp_contact_model_estimates <- shrimp_contact_model |> 
@@
 
-write.csv(shrimp_contact_model_estimates, "shrimp_contact_model_estimates.csv")
-
+write.csv(shrimp_contact_model_estimates, "./2-data/shrimp_contact_model_estimates.csv")
+
+#Storing the model estimate means for each group to plot later on
 shrimp_contact_model_estimates_control <- shrimp_contact_model_estimates |> 
-  filter(stroke == "control") |> 
+  dplyr::filter(stroke == "control") |> 
   rename(.value = emmean)
@@
 shrimp_contact_model_estimates_four <- shrimp_contact_model_estimates |> 
-  filter(stroke == "4")|> 
+  dplyr::filter(stroke == "4")|> 
   rename(.value = emmean)
@@
 shrimp_contact_model_estimates_two <- shrimp_contact_model_estimates |> 
-  filter(stroke == "2")|> 
+  dplyr::filter(stroke == "2")|> 
   rename(.value = emmean)
-
-```
-
-####2.5.3.2 Plotting control estimates and raw data
-```{r}
-shrimp_contact_control_raw_data <- final_df |> 
-  filter(stroke =="control") |> 
+```
+####2.5.3.2 Plotting model estimates and raw data
+```{r}
+shrimp_contact_model_draws <- shrimp_contact_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+shrimp_contact_model_draws <- shrimp_contact_model_draws |> 
+  rename(emmean = .value)
+
+shrimp_contact_raw_data <- final_df |> 
+  rename(emmean = shrimp_contact)
+
+shrimp_contact_raw_data$stage <- factor(shrimp_contact_raw_data$stage, levels = c("Pre", "During", "Post"))
+shrimp_contact_raw_data$stroke <- factor(shrimp_contact_raw_data$stroke, levels = c("control", "4", "2"))
+
+shrimp_contact_model_estimates$stage <- factor(shrimp_contact_model_estimates$stage, levels = c("Pre", "During", "Post"))
+shrimp_contact_model_estimates$stroke <- factor(shrimp_contact_model_estimates$stroke, levels = c("control", "4", "2"))
+
+shrimp_contact_model_draws$stage <- factor(shrimp_contact_model_draws$stage, levels = c("Pre", "During", "Post"))
+shrimp_contact_model_draws$stroke <- factor(shrimp_contact_model_draws$stroke, levels = c("control", "4", "2"))
+
+shrimp_contact_means <- shrimp_contact_raw_data |> 
+  group_by(stage, stroke) |> 
+  summarise(emmean = mean(emmean))
+
+shrimp_contact_fig_together <- ggplot(data = shrimp_contact_raw_data, aes(x = stage, y = emmean, color = stroke, fill = stroke)) +
+  geom_point(data = shrimp_contact_means, alpha = 1, position = position_dodgenudge(width = 0.8, x = -0.09), size = 9, shape = "_") +
+  geom_half_point(alpha = 0.3, position = position_dodgenudge(width = 0.8, x = -0.03), side = "l", range_scale = 0.5) +
+  geom_half_violin(data = shrimp_contact_model_draws, aes(x = stage, y = emmean, color = stroke, fill = stroke), alpha = 0.6, position = position_dodge(width = 0.8), side = "r", size = 0) +
+  geom_point(data = shrimp_contact_model_estimates, aes(x = stage, y = emmean, color = stroke), position = position_dodge(width = 0.8), size = 3) +
+  geom_errorbar(data = shrimp_contact_model_estimates, aes(x = stage, y = emmean, ymin = lower.HPD, ymax = upper.HPD, color = stroke), position = position_dodge(width = 0.8), width = 0, size = 1.25) +
+  scale_fill_manual(values = c("control" = "#76A34A", "4" = "#F29E00", "2" = "#E25A00"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
+  scale_color_manual(values = c("control" = "#2A330E", "4" = "#805213", "2" = "#542709"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
+  scale_x_discrete(labels = c("Pre", "During", "Post")) +
+  labs(title = "The effects of boat noise on goby-shrimp contact",
+       y = "Proportion of time the in contact",
+       x = "Experimental phase relative to noise exposure") +
+  theme_classic() +
+  theme(
+    axis.text.x = element_text(size = 10, margin = margin(t = 5)),  
+    axis.text.y = element_text(size = 10, margin = margin(r = 5)),  
+    axis.title.x = element_text(size = 13, margin = margin(t = 10)),
+    axis.title.y = element_text(size = 13, margin = margin(r = 10)),
+    legend.text = element_text(size = 10),
+    legend.title = element_text(size = 10),
+    legend.position = "right",
+    legend.justification = "top",
+    plot.title = element_text(hjust = 0.5, size = 16),  
+    plot.margin = margin(10, 10, 10, 10)
+  )
+
+shrimp_contact_fig_together
+ggsave("./3-figs/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
+```
+
+####2.5.3.3 Plotting control estimates and raw data
+```{r}
+shrimp_contact_model_draws <- shrimp_contact_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+shrimp_contact_raw_data <- final_df |>
   rename(.value = shrimp_contact)
 
-shrimp_contact_control_raw_data$stage <- factor(shrimp_contact_control_raw_data$stage, levels = c("Post", "During", "Pre"))
-
-shrimp_contact_fig_control <- ggplot(shrimp_contact_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_violin(alpha = 0.7, size = 0) +
-  geom_jitter(width = 0.1) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_control, size = 2, position = position_nudge(x = 0.5)) +
+shrimp_contact_model_draws$stage <- factor(shrimp_contact_model_draws$stage, levels = c("Pre", "During", "Post"))
+shrimp_contact_model_draws$stroke <- factor(shrimp_contact_model_draws$stroke, levels = c("control", "4", "2"))
+
+shrimp_contact_control_model_draws <- shrimp_contact_model_draws |> 
+  dplyr::filter(stroke == "control")
+
+goby_control_raw_data <- final_df |> 
+  dplyr::filter(stroke =="control") |> 
+  rename(.value = shrimp_contact)
+
+goby_control_means <- goby_control_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+goby_control_raw_data$stage <- factor(goby_control_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+#assigning a value for the baseline mean
+shrimp_contact_model_estimates_control_intercept <- shrimp_contact_model_estimates_control %>%
+  dplyr::filter(stage == "Pre") %>%
+  pull(.value)
+
+shrimp_contact_fig_control <- ggplot(goby_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_half_violin(data = shrimp_contact_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = goby_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  labs(x="Period relative to treatment",
+       y="Proportion of time in contact") +
   theme(legend.position = "none", 
         axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        plot.title = element_textbox_simple(size = 12, halign = 0.5, linewidth = 0.5, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_text(size = 13),
+        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
         panel.background = element_rect(fill = "white", colour = "black"),
-        panel.grid.major.x = element_line(colour = "#ededed"))+
+        plot.background = element_rect(fill = NA, colour = NA))+
   ggtitle("Control")+
   scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c")) +
-  coord_flip()
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))
 
@@
 ```
-
-####2.5.3.3 Plotting 4-stroke estimates and raw data
-```{r}
-shrimp_contact_four_raw_data <- final_df |> 
-  filter(stroke =="4") |> 
+####2.5.3.4 Plotting 4-stroke estimates and raw data
+```{r}
+shrimp_contact_control_model_draws <- shrimp_contact_model_draws |> 
+  dplyr::filter(stroke == "4")
+
+goby_four_raw_data <- final_df |> 
+  dplyr::filter(stroke =="4") |> 
   rename(.value = shrimp_contact)
 
-shrimp_contact_four_raw_data$stage <- factor(shrimp_contact_four_raw_data$stage, levels = c("Post", "During", "Pre"))
-
-shrimp_contact_fig_four <- ggplot(shrimp_contact_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_violin(alpha = 0.7, size = 0) +
-  geom_jitter(width = 0.1) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_four, size = 2, position = position_nudge(x = 0.5)) +
+goby_four_raw_data$stage <- factor(goby_four_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+goby_four_means <- goby_four_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_contact_fig_four <- ggplot(goby_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_half_violin(data = shrimp_contact_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = goby_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  xlab("Experimental phase relative to noise exposure")+
+  theme(legend.position = "none", 
+        axis.title.y = element_blank(),  
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("4-stroke")+
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))
+
+shrimp_contact_fig_four
+```
+
+####2.5.3.5 Plotting 2-stroke estimates and raw data
+```{r}
+shrimp_contact_control_model_draws <- shrimp_contact_model_draws |> 
+  dplyr::filter(stroke == "2")
+
+goby_two_raw_data <- final_df |> 
+  dplyr::filter(stroke =="2") |> 
+  rename(.value = shrimp_contact)
+
+goby_two_raw_data$stage <- factor(goby_two_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+goby_two_means <- goby_two_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_contact_fig_two <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_half_violin(data = shrimp_contact_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = goby_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
   theme(legend.position = "none", 
         axis.title.x = element_blank(),  
+        axis.text.x = element_text(size = 13),
         axis.title.y = element_blank(), 
@@
         axis.ticks.y = element_blank(), 
-        plot.title = element_textbox_simple(size = 12, halign = 0.5, linewidth = 0.5, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
         panel.background = element_rect(fill = "white", colour = "black"),
-        panel.grid.major.x = element_line(colour = "#ededed"))+
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("2-stroke") +
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))
+
+shrimp_contact_fig_two
+```
+####2.5.3.6 Combining plots into one figure
+```{r}
+shrimp_contact_plot3 <- shrimp_contact_fig_control + shrimp_contact_fig_four + shrimp_contact_fig_two + 
+  plot_layout(ncol = 3)
+
+shrimp_contact_plot3
+ggsave("./3-figs/shrimp_contact_plot3.png", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+```
+
+###2.5.4 Modelling the effect of covariates on the proportion of time spent in contact
+####2.5.4.1 Goby number
+```{r}
+shrimp_contact_goby_number_contrasts <- shrimp_contact_model |>
+  emmeans(~ goby_number, 
+          epred = TRUE,
+          re_formla = NULL,
+          rg.limit =14000) |> 
+  contrast(method = "revpairwise")
+
+shrimp_contact_goby_number_contrasts
+```
+
+####2.5.4.2 Shrimp number
+```{r}
+shrimp_contact_shrimp_number_contrasts <- shrimp_contact_model |>
+  emmeans(~ shrimp_number, 
+          epred = TRUE,
+          re_formla = NULL,
+          rg.limit =14000) |> 
+  contrast(method = "revpairwise")
+
+shrimp_contact_shrimp_number_contrasts
+```
+
+####2.5.4.2 Shrimp species
+```{r}
+shrimp_contact_shrimp_species_contrasts <- shrimp_contact_model |>
+  emmeans(~ shrimp_species, 
+          epred = TRUE,
+          re_formla = NULL,
+          rg.limit =14000) |> 
+  contrast(method = "revpairwise")
+
+shrimp_contact_shrimp_species_contrasts
+```
+
+#Alternate graphs
+## Goby out
+```{r}
+goby_out_model_draws <- goby_out_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+goby_out_raw_data <- final_df |>
+  rename(.value = goby_out)
+
+goby_out_model_draws$stage <- factor(goby_out_model_draws$stage, levels = c("Pre", "During", "Post"))
+goby_out_model_draws$stroke <- factor(goby_out_model_draws$stroke, levels = c("control", "4", "2"))
+
+goby_out_control_model_draws <- goby_out_model_draws |> 
+  dplyr::filter(stroke == "control")
+
+goby_control_raw_data <- final_df |> 
+  dplyr::filter(stroke =="control") |> 
+  rename(.value = goby_out)
+
+goby_control_means <- goby_control_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+goby_control_raw_data$stage <- factor(goby_control_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+#assigning a value for the baseline mean
+goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control %>%
+  dplyr::filter(stage == "Pre") %>%
+  pull(.value)
+
+goby_out_fig_control2 <- ggplot(goby_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = goby_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  labs(x="Period relative to treatment",
+       y="Proportion of time out of burrow") +
+  theme(legend.position = "none", 
+        axis.title.x = element_blank(), 
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_text(size = 13),
+        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("Control")+
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))
+
+goby_out_fig_control
+
+goby_out_control_model_draws <- goby_out_model_draws |> 
+  dplyr::filter(stroke == "4")
+
+goby_four_raw_data <- final_df |> 
+  dplyr::filter(stroke =="4") |> 
+  rename(.value = goby_out)
+
+goby_four_raw_data$stage <- factor(goby_four_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+goby_four_means <- goby_four_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+goby_out_fig_four2 <- ggplot(goby_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = goby_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  xlab("Experimental phase relative to noise exposure")+
+  theme(legend.position = "none", 
+        axis.title.y = element_blank(),  
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
   ggtitle("4-stroke")+
   scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b")) +
-  coord_flip()
-
-shrimp_contact_fig_four
-```
-
-####2.5.3.4 Plotting 2-stroke estimates and raw data
-```{r}
-shrimp_contact_two_raw_data <- final_df |> 
-  filter(stroke =="2") |> 
-  rename(.value = shrimp_contact)
-
-shrimp_contact_two_raw_data$stage <- factor(shrimp_contact_two_raw_data$stage, levels = c("Post", "During", "Pre"))
-
-shrimp_contact_fig_two <- ggplot(shrimp_contact_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_violin(alpha = 0.7, size = 0) +
-  geom_jitter(width = 0.1) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_two, size = 2, position = position_nudge(x = 0.5)) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))
+
+goby_out_fig_four
+
+goby_out_control_model_draws <- goby_out_model_draws |> 
+  dplyr::filter(stroke == "2")
+
+goby_two_raw_data <- final_df |> 
+  dplyr::filter(stroke =="2") |> 
+  rename(.value = goby_out)
+
+goby_two_raw_data$stage <- factor(goby_two_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+goby_two_means <- goby_two_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+goby_out_fig_two2 <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = goby_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
   theme(legend.position = "none", 
         axis.title.x = element_blank(),  
+        axis.text.x = element_text(size = 13),
         axis.title.y = element_blank(), 
@@
         axis.ticks.y = element_blank(), 
-        plot.title = element_textbox_simple(size = 12, halign = 0.5, linewidth = 0.5, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
         panel.background = element_rect(fill = "white", colour = "black"),
-        panel.grid.major.x = element_line(colour = "#ededed"))+
-  ggtitle("2-stroke")+
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("2-stroke") +
   scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a")) +
-  coord_flip()
-
-shrimp_contact_fig_two
-```
-
-####2.5.3.5 Combining plots into one window
-```{r}
-# Combine the plots
-shrimp_contact_plot <- shrimp_contact_fig_control + shrimp_contact_fig_four + shrimp_contact_fig_two + 
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))
+
+goby_out_fig_two
+
+goby_out_plot2 <- goby_out_fig_control2 + goby_out_fig_four2 + goby_out_fig_two2 + 
   plot_layout(ncol = 3)
 
-# Display the combined plot
-shrimp_contact_plot
-```
-###2.5.4 Modelling the effect of covariates on the proportion of time spent in contact
-####2.5.4.1 Goby number
-```{r}
-shrimp_contact_goby_number_contrasts <- shrimp_contact_model |>
-  emmeans(~ goby_number, 
-          epred = TRUE,
-          re_formla = NULL,
-          rg.limit =14000) |> 
-  contrast(method = "revpairwise")
-
-shrimp_contact_goby_number_contrasts
-```
-
-####2.5.4.2 Shrimp number
-```{r}
-shrimp_contact_shrimp_number_contrasts <- shrimp_contact_model |>
-  emmeans(~ shrimp_number, 
-          epred = TRUE,
-          re_formla = NULL,
-          rg.limit =14000) |> 
-  contrast(method = "revpairwise")
-
-shrimp_contact_shrimp_number_contrasts
-```
-
-####2.5.4.2 Shrimp species
-```{r}
-shrimp_contact_shrimp_species_contrasts <- shrimp_contact_model |>
-  emmeans(~ shrimp_species, 
-          epred = TRUE,
-          re_formla = NULL,
-          rg.limit =14000) |> 
-  contrast(method = "revpairwise")
-
-shrimp_contact_shrimp_species_contrasts
-```
-
-####2.5.4.3 Overall model estimate for the proportion of time shrimp spent in contact with a goby
-```{r}
-shrimp_contact_model |>
-  emmeans(~ 1, 
-          epred = TRUE,
-          re_formla = NULL,
-          rg.limit =14000)
-```
+goby_out_plot2
+ggsave("./3-figs/goby_out_plot2.png", plot = goby_out_plot2, units = "px", width = 2200, height = 1400, dpi = 300)
+```
+
+##Shrmip out
+```{r}
+shrimp_out_model_draws <- shrimp_out_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+shrimp_out_raw_data <- final_df |>
+  rename(.value = shrimp_out)
+
+shrimp_out_model_draws$stage <- factor(shrimp_out_model_draws$stage, levels = c("Pre", "During", "Post"))
+shrimp_out_model_draws$stroke <- factor(shrimp_out_model_draws$stroke, levels = c("control", "4", "2"))
+
+shrimp_out_control_model_draws <- shrimp_out_model_draws |> 
+  dplyr::filter(stroke == "control")
+
+shrimp_control_raw_data <- final_df |> 
+  dplyr::filter(stroke =="control") |> 
+  rename(.value = shrimp_out)
+
+shrimp_control_means <- shrimp_control_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_control_raw_data$stage <- factor(shrimp_control_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+#assigning a value for the baseline mean
+shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control %>%
+  dplyr::filter(stage == "Pre") %>%
+  pull(.value)
+
+shrimp_out_fig_control2 <- ggplot(shrimp_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = shrimp_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  labs(x="Period relative to treatment",
+       y="Proportion of time out of burrow") +
+  theme(legend.position = "none", 
+        axis.title.x = element_blank(), 
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_text(size = 13),
+        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("Control")+
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))
+
+shrimp_out_fig_control
+
+shrimp_out_control_model_draws <- shrimp_out_model_draws |> 
+  dplyr::filter(stroke == "4")
+
+shrimp_four_raw_data <- final_df |> 
+  dplyr::filter(stroke =="4") |> 
+  rename(.value = shrimp_out)
+
+shrimp_four_raw_data$stage <- factor(shrimp_four_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+shrimp_four_means <- shrimp_four_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_out_fig_four2 <- ggplot(shrimp_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = shrimp_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  xlab("Experimental phase relative to noise exposure")+
+  theme(legend.position = "none", 
+        axis.title.y = element_blank(),  
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("4-stroke")+
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))
+
+shrimp_out_fig_four
+
+shrimp_out_control_model_draws <- shrimp_out_model_draws |> 
+  dplyr::filter(stroke == "2")
+
+shrimp_two_raw_data <- final_df |> 
+  dplyr::filter(stroke =="2") |> 
+  rename(.value = shrimp_out)
+
+shrimp_two_raw_data$stage <- factor(shrimp_two_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+shrimp_two_means <- shrimp_two_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_out_fig_two2 <- ggplot(shrimp_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = shrimp_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  theme(legend.position = "none", 
+        axis.title.x = element_blank(),  
+        axis.text.x = element_text(size = 13),
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("2-stroke") +
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))
+
+shrimp_out_fig_two
+
+shrimp_out_plot2 <- shrimp_out_fig_control2 + shrimp_out_fig_four2 + shrimp_out_fig_two2 + 
+  plot_layout(ncol = 3)
+
+shrimp_out_plot2
+ggsave("./3-figs/shrimp_out_plot2.png", plot = shrimp_out_plot2, units = "px", width = 2200, height = 1400, dpi = 300)
+```
+
+##Shrmip contact
+```{r}
+shrimp_contact_model_draws <- shrimp_contact_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+shrimp_contact_raw_data <- final_df |>
+  rename(.value = shrimp_contact)
+
+shrimp_contact_model_draws$stage <- factor(shrimp_contact_model_draws$stage, levels = c("Pre", "During", "Post"))
+shrimp_contact_model_draws$stroke <- factor(shrimp_contact_model_draws$stroke, levels = c("control", "4", "2"))
+
+shrimp_contact_control_model_draws <- shrimp_contact_model_draws |> 
+  dplyr::filter(stroke == "control")
+
+shrimp_control_raw_data <- final_df |> 
+  dplyr::filter(stroke =="control") |> 
+  rename(.value = shrimp_contact)
+
+shrimp_control_means <- shrimp_control_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_control_raw_data$stage <- factor(shrimp_control_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+#assigning a value for the baseline mean
+shrimp_contact_model_estimates_control_intercept <- shrimp_contact_model_estimates_control %>%
+  dplyr::filter(stage == "Pre") %>%
+  pull(.value)
+
+shrimp_contact_fig_control2 <- ggplot(shrimp_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = shrimp_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  labs(x="Period relative to treatment",
+       y="Proportion of time contact of burrow") +
+  theme(legend.position = "none", 
+        axis.title.x = element_blank(), 
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_text(size = 13),
+        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("Control")+
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))
+
+shrimp_contact_control_model_draws <- shrimp_contact_model_draws |> 
+  dplyr::filter(stroke == "4")
+
+shrimp_four_raw_data <- final_df |> 
+  dplyr::filter(stroke =="4") |> 
+  rename(.value = shrimp_contact)
+
+shrimp_four_raw_data$stage <- factor(shrimp_four_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+shrimp_four_means <- shrimp_four_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_contact_fig_four2 <- ggplot(shrimp_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = shrimp_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  xlab("Experimental phase relative to noise exposure")+
+  theme(legend.position = "none", 
+        axis.title.y = element_blank(),  
+        axis.text.x = element_text(size = 13),  
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("4-stroke")+
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))
+
+shrimp_contact_control_model_draws <- shrimp_contact_model_draws |> 
+  dplyr::filter(stroke == "2")
+
+shrimp_two_raw_data <- final_df |> 
+  dplyr::filter(stroke =="2") |> 
+  rename(.value = shrimp_contact)
+
+shrimp_two_raw_data$stage <- factor(shrimp_two_raw_data$stage, levels = c("Pre", "During", "Post"))
+
+shrimp_two_means <- shrimp_two_raw_data |> 
+  group_by(stage) |> 
+  summarise(.value = mean(.value))
+
+shrimp_contact_fig_two2 <- ggplot(shrimp_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
+  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
+  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
+  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
+  geom_point(data = shrimp_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
+  theme(legend.position = "none", 
+        axis.title.x = element_blank(),  
+        axis.text.x = element_text(size = 13),
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
+        panel.background = element_rect(fill = "white", colour = "black"),
+        plot.background = element_rect(fill = NA, colour = NA))+
+  ggtitle("2-stroke") +
+  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
+  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))
+
+shrimp_contact_plot2 <- shrimp_contact_fig_control2 + shrimp_contact_fig_four2 + shrimp_contact_fig_two2 + 
+  plot_layout(ncol = 3)
+
+shrimp_contact_plot2
+ggsave("./3-figs/shrimp_contact_plot2.png", plot = shrimp_contact_plot2, units = "px", width = 2200, height = 1400, dpi = 300)
+```

### 2024-11-15 ms_boatnoise_shrimp_goby.Rmd
added table outputs for ms

@@
 loc_normal <- 0
-scale_normal <- 5
+scale_normal <- 3
 
@@
   geom_line(aes(y = Student_t, color = "Student_t(3, 0, 2.5)")) +
-  geom_line(aes(y = Normal, color = "Normal(0, 5)")) + #For the beta coefficient prior, we will set it to be normally distributed around 0 with an sd of 5, here is the plotted prior distribution 
+  geom_line(aes(y = Normal, color = "Normal(0, 3)")) + #For the beta coefficient prior, we will set it to be normally distributed around 0 with an sd of 5, here is the plotted prior distribution 
   labs(title = "Probability Density Functions",
@@
        y = "Probability Density") +
-  scale_color_manual(name = "Distribution", values = c("Logistic(0, 3)" = "blue", "Student_t(3, 0, 2.5)" = "green", "Normal(0, 5)" = "red")) +
+  scale_color_manual(name = "Distribution", values = c("Logistic(0, 3)" = "blue", "Student_t(3, 0, 2.5)" = "green", "Normal(0, 3)" = "red")) +
   theme_minimal()
@@
             set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "coi", lb = 0),
-            set_prior("normal(0, 5)", class = "b"),
-            set_prior("normal(0, 5)", class = "b", dpar = "phi"),
-            set_prior("normal(0, 5)", class = "b", dpar = "zoi"),
-            set_prior("normal(0, 5)", class = "b", dpar = "coi"))
+            set_prior("normal(0, 3)", class = "b"),
+            set_prior("normal(0, 3)", class = "b", dpar = "phi"),
+            set_prior("normal(0, 3)", class = "b", dpar = "zoi"),
+            set_prior("normal(0, 3)", class = "b", dpar = "coi"))
 ```
@@
   backend = "cmdstanr",
-  seed = 12345,
+  seed = 1,
   sample_prior = "only",
@@
   backend = "cmdstanr",
-  seed = 12345,
-  file = "goby_out_model",
-
+  seed = 1,
+  file = "goby_out_model"
 )
@@
         axis.text.y = element_text(size = 13),
+        panel.grid = element_blank(),
         axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
@@
         axis.ticks.y = element_blank(), 
+        panel.grid = element_blank(),
         axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
@@
         axis.ticks.y = element_blank(), 
+        panel.grid = element_blank(),
         plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
@@
 goby_out_plot3
-ggsave("./3-figs/goby_out_plot3.png", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./3-figs/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 ```{r}
+goby_out_model |>
+  emmeans(~ goby_number, 
+          epred = TRUE,
+          re_formla = NULL)
+
 goby_out_goby_number <- goby_out_model |>
@@
   backend = "cmdstanr",
-  seed = 12345,
+  seed = 1,
   file = "shrimp_out_model"
@@
 ```{r}
+ranef(shrimp_out_model)
+
 shrimp_out_contrasts <- shrimp_out_model |>
@@
 shrimp_out_plot3
-ggsave("./3-figs/shrimp_out_plot3.png", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./3-figs/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 
-shrimp_out_shrimp_number_contrasts <- shrimp_out_model |>
+shrimp_out_shrimp_number_contrast_draws <- shrimp_out_model |>
   emmeans(~ shrimp_number, 
@@
 
-ggplot(data = shrimp_out_shrimp_number_contrasts, aes(x = contrast, y = .value )) +
+ggplot(data = shrimp_out_shrimp_number_contrast_draws, aes(x = contrast, y = .value )) +
   stat_halfeye()
@@
 
-shrimp_out_shrimp_species_contrasts <- shrimp_out_model |>
+shrimp_out_shrimp_species_contrasts_draws <- shrimp_out_model |>
   emmeans(~ shrimp_species, 
@@
 
-ggplot(data = shrimp_out_shrimp_species_contrasts, aes(x = contrast, y = .value )) +
+ggplot(data = shrimp_out_shrimp_species_contrasts_draws, aes(x = contrast, y = .value )) +
   stat_halfeye()
@@
   control = list(adapt_delta = 0.99, max_treedepth = 12),
-  chains = 4, iter = 6000, warmup = 1000, seed = 12345, backend = "cmdstanr", cores = 4, threads = threading(2),
+  chains = 4, iter = 6000, warmup = 1000, seed = 1, backend = "cmdstanr", cores = 4, threads = threading(2),
   file = "shrimp_contact_model"
@@
   emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA)
+
+shrimp_contact_model |> 
+  emmeans(~ 1,
           epred = TRUE,
@@
 shrimp_contact_plot3
-ggsave("./3-figs/shrimp_contact_plot3.png", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./3-figs/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 
-#Alternate graphs
-## Goby out
-```{r}
-goby_out_model_draws <- goby_out_model |> 
-  emmeans(~ stroke*stage,
-          epred = TRUE,
-          rg.limit = 14000,
-          re_formula = NA) |> 
-  gather_emmeans_draws()
-
-goby_out_raw_data <- final_df |>
-  rename(.value = goby_out)
-
-goby_out_model_draws$stage <- factor(goby_out_model_draws$stage, levels = c("Pre", "During", "Post"))
-goby_out_model_draws$stroke <- factor(goby_out_model_draws$stroke, levels = c("control", "4", "2"))
-
-goby_out_control_model_draws <- goby_out_model_draws |> 
-  dplyr::filter(stroke == "control")
-
-goby_control_raw_data <- final_df |> 
-  dplyr::filter(stroke =="control") |> 
-  rename(.value = goby_out)
-
-goby_control_means <- goby_control_raw_data |> 
-  group_by(stage) |> 
-  summarise(.value = mean(.value))
-
-goby_control_raw_data$stage <- factor(goby_control_raw_data$stage, levels = c("Pre", "During", "Post"))
-
-#assigning a value for the baseline mean
-goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control %>%
-  dplyr::filter(stage == "Pre") %>%
-  pull(.value)
-
-goby_out_fig_control2 <- ggplot(goby_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
-  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
-  geom_point(data = goby_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
-  labs(x="Period relative to treatment",
-       y="Proportion of time out of burrow") +
-  theme(legend.position = "none", 
-        axis.title.x = element_blank(), 
-        axis.text.x = element_text(size = 13),  
-        axis.text.y = element_text(size = 13),
-        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
-        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("Control")+
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))
-
-goby_out_fig_control
-
-goby_out_control_model_draws <- goby_out_model_draws |> 
-  dplyr::filter(stroke == "4")
-
-goby_four_raw_data <- final_df |> 
-  dplyr::filter(stroke =="4") |> 
-  rename(.value = goby_out)
-
-goby_four_raw_data$stage <- factor(goby_four_raw_data$stage, levels = c("Pre", "During", "Post"))
-
-goby_four_means <- goby_four_raw_data |> 
-  group_by(stage) |> 
-  summarise(.value = mean(.value))
-
-goby_out_fig_four2 <- ggplot(goby_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
-  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
-  geom_point(data = goby_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
-  xlab("Experimental phase relative to noise exposure")+
-  theme(legend.position = "none", 
-        axis.title.y = element_blank(),  
-        axis.text.x = element_text(size = 13),  
-        axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
-        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("4-stroke")+
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))
-
-goby_out_fig_four
-
-goby_out_control_model_draws <- goby_out_model_draws |> 
-  dplyr::filter(stroke == "2")
-
-goby_two_raw_data <- final_df |> 
-  dplyr::filter(stroke =="2") |> 
-  rename(.value = goby_out)
-
-goby_two_raw_data$stage <- factor(goby_two_raw_data$stage, levels = c("Pre", "During", "Post"))
-
-goby_two_means <- goby_two_raw_data |> 
-  group_by(stage) |> 
-  summarise(.value = mean(.value))
-
-goby_out_fig_two2 <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
-  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
-  geom_point(data = goby_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
-  theme(legend.position = "none", 
-        axis.title.x = element_blank(),  
-        axis.text.x = element_text(size = 13),
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("2-stroke") +
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))
-
-goby_out_fig_two
-
-goby_out_plot2 <- goby_out_fig_control2 + goby_out_fig_four2 + goby_out_fig_two2 + 
-  plot_layout(ncol = 3)
-
-goby_out_plot2
-ggsave("./3-figs/goby_out_plot2.png", plot = goby_out_plot2, units = "px", width = 2200, height = 1400, dpi = 300)
-```
-
-##Shrmip out
-```{r}
-shrimp_out_model_draws <- shrimp_out_model |> 
-  emmeans(~ stroke*stage,
-          epred = TRUE,
-          rg.limit = 14000,
-          re_formula = NA) |> 
-  gather_emmeans_draws()
-
-shrimp_out_raw_data <- final_df |>
-  rename(.value = shrimp_out)
-
-shrimp_out_model_draws$stage <- factor(shrimp_out_model_draws$stage, levels = c("Pre", "During", "Post"))
-shrimp_out_model_draws$stroke <- factor(shrimp_out_model_draws$stroke, levels = c("control", "4", "2"))
-
-shrimp_out_control_model_draws <- shrimp_out_model_draws |> 
-  dplyr::filter(stroke == "control")
-
-shrimp_control_raw_data <- final_df |> 
-  dplyr::filter(stroke =="control") |> 
-  rename(.value = shrimp_out)
-
-shrimp_control_means <- shrimp_control_raw_data |> 
-  group_by(stage) |> 
-  summarise(.value = mean(.value))
-
-shrimp_control_raw_data$stage <- factor(shrimp_control_raw_data$stage, levels = c("Pre", "During", "Post"))
-
-#assigning a value for the baseline mean
-shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control %>%
-  dplyr::filter(stage == "Pre") %>%
-  pull(.value)
-
-shrimp_out_fig_control2 <- ggplot(shrimp_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
-  geom_point(data = shrimp_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
-  labs(x="Period relative to treatment",
-       y="Proportion of time out of burrow") +
-  theme(legend.position = "none", 
-        axis.title.x = element_blank(), 
-        axis.text.x = element_text(size = 13),  
-        axis.text.y = element_text(size = 13),
-        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
-        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("Control")+
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))
-
-shrimp_out_fig_control
-
-shrimp_out_control_model_draws <- shrimp_out_model_draws |> 
-  dplyr::filter(stroke == "4")
-
-shrimp_four_raw_data <- final_df |> 
-  dplyr::filter(stroke =="4") |> 
-  rename(.value = shrimp_out)
-
-shrimp_four_raw_data$stage <- factor(shrimp_four_raw_data$stage, levels = c("Pre", "During", "Post"))
-
-shrimp_four_means <- shrimp_four_raw_data |> 
-  group_by(stage) |> 
-  summarise(.value = mean(.value))
-
-shrimp_out_fig_four2 <- ggplot(shrimp_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
-  geom_point(data = shrimp_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
-  xlab("Experimental phase relative to noise exposure")+
-  theme(legend.position = "none", 
-        axis.title.y = element_blank(),  
-        axis.text.x = element_text(size = 13),  
-        axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
-        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("4-stroke")+
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))
-
-shrimp_out_fig_four
-
-shrimp_out_control_model_draws <- shrimp_out_model_draws |> 
-  dplyr::filter(stroke == "2")
-
-shrimp_two_raw_data <- final_df |> 
-  dplyr::filter(stroke =="2") |> 
-  rename(.value = shrimp_out)
-
-shrimp_two_raw_data$stage <- factor(shrimp_two_raw_data$stage, levels = c("Pre", "During", "Post"))
-
-shrimp_two_means <- shrimp_two_raw_data |> 
-  group_by(stage) |> 
-  summarise(.value = mean(.value))
-
-shrimp_out_fig_two2 <- ggplot(shrimp_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
-  geom_point(data = shrimp_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
-  theme(legend.position = "none", 
-        axis.title.x = element_blank(),  
-        axis.text.x = element_text(size = 13),
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("2-stroke") +
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))
-
-shrimp_out_fig_two
-
-shrimp_out_plot2 <- shrimp_out_fig_control2 + shrimp_out_fig_four2 + shrimp_out_fig_two2 + 
-  plot_layout(ncol = 3)
-
-shrimp_out_plot2
-ggsave("./3-figs/shrimp_out_plot2.png", plot = shrimp_out_plot2, units = "px", width = 2200, height = 1400, dpi = 300)
-```
-
-##Shrmip contact
-```{r}
-shrimp_contact_model_draws <- shrimp_contact_model |> 
-  emmeans(~ stroke*stage,
-          epred = TRUE,
-          rg.limit = 14000,
-          re_formula = NA) |> 
-  gather_emmeans_draws()
-
-shrimp_contact_raw_data <- final_df |>
-  rename(.value = shrimp_contact)
-
-shrimp_contact_model_draws$stage <- factor(shrimp_contact_model_draws$stage, levels = c("Pre", "During", "Post"))
-shrimp_contact_model_draws$stroke <- factor(shrimp_contact_model_draws$stroke, levels = c("control", "4", "2"))
-
-shrimp_contact_control_model_draws <- shrimp_contact_model_draws |> 
-  dplyr::filter(stroke == "control")
-
-shrimp_control_raw_data <- final_df |> 
-  dplyr::filter(stroke =="control") |> 
-  rename(.value = shrimp_contact)
-
-shrimp_control_means <- shrimp_control_raw_data |> 
-  group_by(stage) |> 
-  summarise(.value = mean(.value))
-
-shrimp_control_raw_data$stage <- factor(shrimp_control_raw_data$stage, levels = c("Pre", "During", "Post"))
-
-#assigning a value for the baseline mean
-shrimp_contact_model_estimates_control_intercept <- shrimp_contact_model_estimates_control %>%
-  dplyr::filter(stage == "Pre") %>%
-  pull(.value)
-
-shrimp_contact_fig_control2 <- ggplot(shrimp_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
-  geom_point(data = shrimp_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
-  labs(x="Period relative to treatment",
-       y="Proportion of time contact of burrow") +
-  theme(legend.position = "none", 
-        axis.title.x = element_blank(), 
-        axis.text.x = element_text(size = 13),  
-        axis.text.y = element_text(size = 13),
-        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
-        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("Control")+
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))
-
-shrimp_contact_control_model_draws <- shrimp_contact_model_draws |> 
-  dplyr::filter(stroke == "4")
-
-shrimp_four_raw_data <- final_df |> 
-  dplyr::filter(stroke =="4") |> 
-  rename(.value = shrimp_contact)
-
-shrimp_four_raw_data$stage <- factor(shrimp_four_raw_data$stage, levels = c("Pre", "During", "Post"))
-
-shrimp_four_means <- shrimp_four_raw_data |> 
-  group_by(stage) |> 
-  summarise(.value = mean(.value))
-
-shrimp_contact_fig_four2 <- ggplot(shrimp_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
-  geom_point(data = shrimp_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
-  xlab("Experimental phase relative to noise exposure")+
-  theme(legend.position = "none", 
-        axis.title.y = element_blank(),  
-        axis.text.x = element_text(size = 13),  
-        axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
-        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("4-stroke")+
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))
-
-shrimp_contact_control_model_draws <- shrimp_contact_model_draws |> 
-  dplyr::filter(stroke == "2")
-
-shrimp_two_raw_data <- final_df |> 
-  dplyr::filter(stroke =="2") |> 
-  rename(.value = shrimp_contact)
-
-shrimp_two_raw_data$stage <- factor(shrimp_two_raw_data$stage, levels = c("Pre", "During", "Post"))
-
-shrimp_two_means <- shrimp_two_raw_data |> 
-  group_by(stage) |> 
-  summarise(.value = mean(.value))
-
-shrimp_contact_fig_two2 <- ggplot(shrimp_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
-  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
-  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_contact_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
-  geom_point(pch = 23, stroke = 1.2, data = shrimp_contact_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
-  geom_point(data = shrimp_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
-  theme(legend.position = "none", 
-        axis.title.x = element_blank(),  
-        axis.text.x = element_text(size = 13),
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
-        panel.background = element_rect(fill = "white", colour = "black"),
-        plot.background = element_rect(fill = NA, colour = NA))+
-  ggtitle("2-stroke") +
-  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
-  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))
-
-shrimp_contact_plot2 <- shrimp_contact_fig_control2 + shrimp_contact_fig_four2 + shrimp_contact_fig_two2 + 
-  plot_layout(ncol = 3)
-
-shrimp_contact_plot2
-ggsave("./3-figs/shrimp_contact_plot2.png", plot = shrimp_contact_plot2, units = "px", width = 2200, height = 1400, dpi = 300)
-```
+#3 Manuscript output files
+##3.1 Supp tables
+###3.1.1 Model estimates
+```{r}
+goby_out_model_estimates <- goby_out_model_estimates |> 
+  mutate(`Behavioural measure` = "Proportion of time gobies spent outside of the burrow")
+
+shrimp_out_model_estimates <- shrimp_out_model_estimates |> 
+  mutate(`Behavioural measure` = "Proportion of time shrimp spent outside of the burrow")
+
+shrimp_contact_model_estimates <- shrimp_contact_model_estimates |> 
+  mutate(`Behavioural measure` = "Proportion of time shrimp spent in contact with a goby")
+
+model_estimates <- bind_rows(goby_out_model_estimates, 
+                             shrimp_out_model_estimates, 
+                             shrimp_contact_model_estimates)
+
+model_estimates <- model_estimates |>
+  mutate(stroke = ifelse(stroke == "4", "4-stroke", ifelse(stroke == "2", "2-stroke", "control")),
+         stroke = factor(stroke, levels = c("control", "4-stroke", "2-stroke")),
+         stage = factor(stage, levels = c("Pre", "During", "Post")),
+         `Behavioural measure` = factor(`Behavioural measure`, levels = c("Proportion of time gobies spent outside of the burrow", "Proportion of time shrimp spent outside of the burrow", "Proportion of time shrimp spent in contact with a goby"))) |>
+  arrange(`Behavioural measure`, stage, stroke) |> 
+  rename(`Estimated marginal mean` = emmean,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Phase = stage,
+         `Noise exposure` = stroke) |> 
+  select(c(`Behavioural measure`, Phase, `Noise exposure`, `Estimated marginal mean`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+write_csv(model_estimates, "./2-data/model_estimates.csv")
+```
+
+###3.1.2 Pairwise contrasts
+```{r}
+#goby out
+goby_out_contrasts <- goby_out_results.table |> 
+  mutate(`Predictor variable` = "Treatment and phase interaction",
+         contrast = str_replace_all(contrast, "\\b2\\b", "2-Stroke"),
+         contrast = str_replace_all(contrast, "\\b4\\b", "4-Stroke"),
+         contrast = str_replace_all(contrast, "\\bcontrol\\b", "Control")
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+goby_out_goby_number1 <- goby_out_goby_number |>
+  as.data.frame() |> 
+  mutate(`Predictor variable` = "Number of gobies",
+         contrast = str_replace_all(contrast, "\\bgoby_number2\\b", "2 gobies"),
+         contrast = str_replace_all(contrast, "\\bgoby_number1\\b", "1 goby")
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+goby_out_shrimp_number1 <- goby_out_shrimp_number |> 
+  as.data.frame() |> 
+  mutate(`Predictor variable` = "Number of shrimp",
+         contrast = str_replace_all(contrast, "\\bshrimp_number2\\b", "2 shrimp"),
+         contrast = str_replace_all(contrast, "\\bshrimp_number1\\b", "1 shrimp"),
+         contrast = str_replace_all(contrast, "\\bshrimp_number3\\b", "3 shrimp")
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+goby_out_shrimp_species1 <- goby_out_shrimp_species |> 
+  as.data.frame() |> 
+  mutate(`Predictor variable` = "Shrimp species"
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+goby_out_contrasts_table <- rbind(goby_out_contrasts, goby_out_goby_number1, goby_out_shrimp_number1, goby_out_shrimp_species1) |>
+  mutate(
+    `Estimated marginal difference` = round(`Estimated marginal difference`, 3),
+    `Lower 95% CrI` = round(`Lower 95% CrI`, 3),
+    `Upper 95% CrI` = round(`Upper 95% CrI`, 3)
+  )
+
+write_csv(goby_out_contrasts_table, "./2-data/goby_out_contrasts_table.csv")
+
+#shrimp out
+shrimp_out_contrasts1 <- shrimp_out_contrasts |> 
+  mutate(`Predictor variable` = "Treatment and phase interaction",
+         contrast = str_replace_all(contrast, "\\b2\\b", "2-Stroke"),
+         contrast = str_replace_all(contrast, "\\b4\\b", "4-Stroke"),
+         contrast = str_replace_all(contrast, "\\bcontrol\\b", "Control")
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+shrimp_out_goby_number_contrasts1 <- shrimp_out_goby_number_contrasts |>
+  as.data.frame() |> 
+  mutate(`Predictor variable` = "Number of gobies",
+         contrast = str_replace_all(contrast, "\\bgoby_number2\\b", "2 gobies"),
+         contrast = str_replace_all(contrast, "\\bgoby_number1\\b", "1 goby")
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+shrimp_out_shrimp_number_contrasts1 <- shrimp_out_shrimp_number_contrasts |> 
+  as.data.frame() |> 
+  mutate(`Predictor variable` = "Number of shrimp",
+         contrast = str_replace_all(contrast, "\\bshrimp_number2\\b", "2 shrimp"),
+         contrast = str_replace_all(contrast, "\\bshrimp_number1\\b", "1 shrimp"),
+         contrast = str_replace_all(contrast, "\\bshrimp_number3\\b", "3 shrimp")
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+shrimp_out_shrimp_species_contrasts1 <- shrimp_out_shrimp_species_contrasts |> 
+  as.data.frame() |> 
+  mutate(`Predictor variable` = "Shrimp species"
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+shrimp_out_contrasts_table <- rbind(shrimp_out_contrasts1, shrimp_out_goby_number_contrasts1, shrimp_out_shrimp_number_contrasts1, shrimp_out_shrimp_species_contrasts1) |>
+  mutate(
+    `Estimated marginal difference` = round(`Estimated marginal difference`, 3),
+    `Lower 95% CrI` = round(`Lower 95% CrI`, 3),
+    `Upper 95% CrI` = round(`Upper 95% CrI`, 3)
+  )
+
+write_csv(shrimp_out_contrasts_table, "./2-data/shrimp_out_contrasts_table.csv")
+
+#shrimp contact
+shrimp_contact_contrasts1 <- shrimp_contact_contrasts |> 
+  mutate(`Predictor variable` = "Treatment and phase interaction",
+         contrast = str_replace_all(contrast, "\\b2\\b", "2-Stroke"),
+         contrast = str_replace_all(contrast, "\\b4\\b", "4-Stroke"),
+         contrast = str_replace_all(contrast, "\\bcontrol\\b", "Control")
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+shrimp_contact_goby_number_contrasts1 <- shrimp_contact_goby_number_contrasts |>
+  as.data.frame() |> 
+  mutate(`Predictor variable` = "Number of gobies",
+         contrast = str_replace_all(contrast, "\\bgoby_number2\\b", "2 gobies"),
+         contrast = str_replace_all(contrast, "\\bgoby_number1\\b", "1 goby")
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+shrimp_contact_shrimp_number_contrasts1 <- shrimp_contact_shrimp_number_contrasts |> 
+  as.data.frame() |> 
+  mutate(`Predictor variable` = "Number of shrimp",
+         contrast = str_replace_all(contrast, "\\bshrimp_number2\\b", "2 shrimp"),
+         contrast = str_replace_all(contrast, "\\bshrimp_number1\\b", "1 shrimp"),
+         contrast = str_replace_all(contrast, "\\bshrimp_number3\\b", "3 shrimp")
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+shrimp_contact_shrimp_species_contrasts1 <- shrimp_contact_shrimp_species_contrasts |> 
+  as.data.frame() |> 
+  mutate(`Predictor variable` = "Shrimp species"
+         ) |> 
+  rename(`Estimated marginal difference` = estimate,
+         `Lower 95% CrI` = lower.HPD,
+         `Upper 95% CrI` = upper.HPD,
+         Contrast = contrast) |> 
+  select(c(`Predictor variable`, Contrast, `Estimated marginal difference`, `Lower 95% CrI`, `Upper 95% CrI`))
+
+shrimp_contact_contrasts_table <- rbind(shrimp_contact_contrasts1, shrimp_contact_goby_number_contrasts1, shrimp_contact_shrimp_number_contrasts1, shrimp_contact_shrimp_species_contrasts1) |>
+  mutate(
+    `Estimated marginal difference` = round(`Estimated marginal difference`, 3),
+    `Lower 95% CrI` = round(`Lower 95% CrI`, 3),
+    `Upper 95% CrI` = round(`Upper 95% CrI`, 3)
+  )
+
+write_csv(shrimp_contact_contrasts_table, "./2-data/shrimp_contact_contrasts_table.csv")
+```

### 2025-02-18 ms_boatnoise_shrimp_goby.Rmd
adding code

@@
 
-remotes::install_github("stan-dev/loo")
+#remotes::install_github("stan-dev/loo")
 # Setting colours for vidsalisations
@@
 #reading in the coded raw BORIS output
-BORIS_output <- read.csv("./2-data/BORIS_output_update.csv")
+BORIS_output <- read.csv("./2-data/BORIS_output.csv")
 
@@
                 individual = str_sub(subject, 1, 1),
-                helper = str_sub(date_file, -6,-6),
-                stroke = ifelse(helper == "t", 'control', 
-                                ifelse((boat_id == "A")|(boat_id == "B")|(boat_id == "C")|(boat_id == "D"), 
-                                       '2', '4')))
+                stroke = factor(stroke),
+                boat_name = factor(boat_name)
+                )
 
@@
 final_df <- inner_join(goby_df, shrimp_df, by = "burrow_stage") |> 
-  mutate(shrimp_contact = ifelse(is.na(shrimp_contact), ifelse(goby_out == 1, 0, 1 - goby_out), shrimp_contact))
+  mutate(shrimp_contact = ifelse(is.na(shrimp_contact), ifelse(goby_out == 1, 0, 1 - goby_out), shrimp_contact)) |> 
+  filter(site != "SITE O")
 
@@
   # mu (mean) part
-  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  goby_out ~ stroke * stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
   # phi (precision) part
-  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  phi ~ stroke * stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
   # alpha (zero-one-inflation) part
-  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  zoi ~ stroke * stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
   # The one-inflated part, conditional on the 0s
-  coi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  coi ~ stroke * stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
 
@@
 
-goby_out_model_estimates
-
-write.csv(goby_out_model_estimates, "./2-data/goby_out_model_estimates.csv")
-
 #Storing the model estimate means for each group to plot later on
@@
 ```
+
 ####2.3.3.2 Plotting model estimates and raw data
@@
 goby_out_fig_together
-ggsave("./3-figs/goby_out_fig_together.png", plot = goby_out_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 
-goby_out_shrimp_species
+goby_out_shrimp_species <- as.data.frame(goby_out_shrimp_species)
 
@@
 
-goby_out_shrimp_species_estimates
+goby_out_shrimp_species_estimates <- as.data.frame(goby_out_shrimp_species_estimates)
 
@@
 ```{r}
-ranef(shrimp_out_model)
-
 shrimp_out_contrasts <- shrimp_out_model |>
@@
 shrimp_out_model_estimates
-
-write.csv(shrimp_out_model_estimates, "./2-data/shrimp_out_model_estimates.csv")
 
@@
 shrimp_out_fig_together
-ggsave("./3-figs/shrimp_out_fig_together.png", plot = shrimp_out_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 
-shrimp_out_shrimp_number_contrasts
+shrimp_out_shrimp_number_contrasts <- as.data.frame(shrimp_out_shrimp_number_contrasts)
 
@@
   contrast(method = "revpairwise")
+
+overall_mean <- shrimp_contact_model |>
+  emmeans(~ 1,             # 1 means "no factors," i.e. the grand mean
+          epred = TRUE,    # estimate on the response scale
+          re_formla = NULL,
+          rg.limit = 14000)
+
+# View the summary with posterior mean and credible intervals
+overall_mean
 
@@
 shrimp_contact_model_estimates
-
-write.csv(shrimp_contact_model_estimates, "./2-data/shrimp_contact_model_estimates.csv")
 
@@
 ```
+
+```{r}
+table_S1 <- final_df %>%
+  select(c("burrow", "stroke", "site")) |> 
+  unique() |> 
+  group_by(site, stroke) %>%
+  summarise(n = n(), .groups = "drop") %>%
+  pivot_wider(names_from = stroke, values_from = n, values_fill = 0) %>%
+  mutate(Total = `control` + `4` + `2`) %>%
+  arrange(site) %>%
+  rename(`4-stroke` = `4`, 
+         `2-stroke` = `2`, 
+         Control = control)
+```

### 2025-02-19 ms_boatnoise_shrimp_goby.Rmd
Jakes code updates and addtional annotation

@@
     depth: 4
-    number_sections: no
+    number_sections: yes
     theme:  cosmo
@@
     toc: yes
+knit: |
+  (function(input, ...) {
+    rmarkdown::render(
+      input,
+      output_file = paste0(
+       'index.html'
+      ),
+      envir = globalenv()
+    )
+  })
 ---
 
-```{r setup, include = FALSE}
-#kniter setting
+<!------------------------------->
+# 📕 READ ME   
+<!------------------------------->
+
+**SUMMARY**
+
+**AIM**
+
+**AUTHORS**
+
+**AFFILIATIONS**
+
+**CONTRIBUTOR ROLES**
+
+<!------------------------------->
+# 📧 Contact
+<!------------------------------->
+
+**Jake M. Martin**
+
+📧 **Email:** [jake.martin@deakin.edu.au](mailto:jake.martin@deakin.edu.au)
+
+📧 **Alt Email:** [jake.martin.research@gmail.com](mailto:jake.martin.research@gmail.com)
+
+🌐 **Web:** [jakemartin.org](https://jakemartin.org/)
+
+🐙 **GitHub**: [JakeMartinResearch](https://github.com/JakeMartinResearch)
+
+<!------------------------------->
+# ⚙️ Knit settings 
+<!------------------------------->
+
+Here we define our Knit settings, to make the output more user friendly, and to cache output for faster knitting.
+
+```{r setup}
+#kniter seetting
 knitr::opts_chunk$set(
@@
 
-#1. Data wrangling
-##1.1 Loading the required packages
+<!------------------------------->
+# 📦 Required packages
+<!------------------------------->
+
+These are the R packages required for this script. You will need to install a package called pacman to run the p_load function.
+
+🚧 Do we need `stan-dev/loo` 🚧
+
 ```{r, message=FALSE, results='hide'}
 #install.packages("pacman")
-pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr, gghalves, ggpp, rstan)
+#require("pacman") 
+pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr, gghalves, ggpp, rstan, gt)
 
 #remotes::install_github("stan-dev/loo")
-# Setting colours for vidsalisations
+```
+
+<!------------------------------->
+# 🤠 Data wrangling
+<!------------------------------->
+
+Setting colour palette for visualisations
+
+```{r}
+# Setting colours for visualisations
 colour1 <- "#97A275"
@@
 
-##1.2 Unblinding the data
+## Data
+
+Here we load in the three date files
+
+- **💿 BORIS_output.csv**: This is the summary output from the BORIS, the key logging software used for behavioural observations.
+This includes the occurrence count and total duration of each of the measured behaviour endpoints, for each shrimp and each goby across all trials.
+They are identified with the code column.
+- **💿 Video_codes.csv**: This has meta data for each video, include treatment information and associated codes.
+- **💿 species.csv**: This is the species name for the shrimp in each of the videos
+
 ```{r}
@@
 shrimp_species <- read.csv("./2-data/species.csv")
-
+```
+
+## Unblinding data
+
+Now we unbind the treatment code form behavioural observations (all behaviours were scored blind to treatment). This is done using video code column.
+
+```{r}
 #binding the decoder to the BORIS output and revealing the treatment and stage
@@
 
-## 1.3 Cross-checking the imported datasets
+## Cross-checking the imported datasets
+
+There were instances where burrows were recorded and assigned video codes but showed no activity from gobies or shrimp during these recordings.
+These instances led to the assumption that such burrows were inactive, resulting in their exclusion from the further analysis of the study.
+
 ```{r}
@@
 print(results)
-
-# Missing observations are identified exclusively within the 'Video_codes' dataframe.
-This situation suggests that all videos capturing both shrimp and gobies are consistently represented across the datasets.
-However, there were instances where burrows were recorded and assigned video codes but showed no activity from gobies or shrimp during these recordings.
-These instances led to the assumption that such burrows were inactive, resulting in their exclusion from the further analysis of the study.
-```
-
-##1.4 Cleaning the dataframe
-###1.4.1 Column renaming
+```
+
+##  Cleaning the dataframe
+
+### Column renaming
+
+Renaming some of the variables and extracting individual variables from columns that have multiple variables contained in one string
+
 ```{r}
@@
 
-#renaming some of the variables and extracting individual variables from columns that have multiple variables contained in one string
 decoded_dataframe <- decoded_dataframe |> 
@@
                 )
-
-#creating some unique identifiers to make grouping easier later on for reorganising of the dataframe
+```
+
+Creating some unique identifiers to make grouping easier later on for reorganising of the data frame.
+
+```{r}
 decoded_dataframe <- decoded_dataframe |> 
@@
 
-###1.4.2 Removing redundant BORIS entries
-```{r}
-#the next few lines of code are to do with the way BORIS outputs data, where there was redundant empty sections due to both species being independently scored in the software.
+### Removing redundant BORIS entries
+
+Here we clean the BROIS output data, where there was redundant empty sections due to both species being independently scored in the software.
 So here we are filtering out the species specific data from the correlating BORIS species observation and then rebinding the data to remove all of the empty artifact entries.
 
+```{r}
 #extracting just the goby data so that a species variable can be made
@@
 
-###1.4.3 Assigning values to missing entries
-```{r}
-#now here we are making the assumption that when a goby or shrimp is present in other videos but missing from the video of focus it is either away and out of frame for the entire trial if it is a goby.
-Otherwise it is inside the burrow the entire time if it is a shrimp.
-These assumptions are based off of preliminary observation and the general tendencies of each species.
+### Assigning values to missing entries
+
+Here we are dealing with miss focal species during specific segments of the trial.
+
+We make the assumption that when a **goby is present in other videos** (i.e.
+we know it exists) but **missing from a given trial segment** it is **'away'** and out of frame for the entire trial.
+In the case of shrimps, we assume it **inside the burrow the entire time**.
+These assumptions are based off our teams observation of these species, and the previously reported biological tendencies of each species.
 Because of this assumption we are assigning the respective value to the behviour in cases where one of the species is known to be present in a burrow but not viewed for the length of the trial.
+
+🚧 Jack, maybe you could break this up and add a little more detial, I got a little lost in the code 🚧
+
+```{r}
 fixeddf1 <- workingdf3 |> 
@@
 print(burrow_counts)
-
-#there are some burrows that are missing stages due to the animal not being observered at all during that observation so we will make some conditional assumptions and fill in the missing values.
-
+```
+
+There are some burrows that are missing stages due to the animal not being observered at all during that observation so we will make some conditional assumptions and fill in the missing values.
+
+```{r}
 #a function to fill the missing stages for each species within each burrow
@@
 
-###1.4.4 Changing dataframe format 
+### Changing dataframe format
+
+Restructure the data frame for easier analysis
+
 ```{r}
@@
 
-#2. Statistical analysis using zero-one inflated beta regression
-##2.1 Building a global model
-```{r}
-#building a global model for the proportion of time gobies spent out of the burrow
+<!------------------------------->
+# 🧮 Analysis 
+<!------------------------------->
+
+## 🐟 Gobies time outside of burrow
+
+### Model struture
+
+First we will build a global model for the proportion of time gobies spent out of the burrow
+
+```{r}
 zoib_formula <- bf(
@@
 
-##2.2 Specifying priors
-###2.2.1 Checking default priors
+### Specifying priors
+
+#### Checking default priors
+
+First we check default priors
+
+All the beta coefficients are being given a flat prior which means it can take on a value from - infinity to + infinity.
+All the beta coefficients are on the logit scale so lets plot how changing the value of beta relates to different proportions
+
 ```{r}
@@
   data = final_df
-)
-#we can see that all the beta coefficients are being given a flat prior which means it can take on a value from - infinity to + infinity.
-All the beta coefficients are on the logit scale so lets plot how changing the value of beta relates to different proportions
-```
-
-###2.2.2 Graphing logit~proportion
+) %>% 
+  gt()
+```
+
+#### Graphing logit~proportion
+
+After -5 or +5 the probability doesn't change much, instead of leaving our priors at the default of + and - infinity, we should say that they are most likely to occur between -5 and +5.
+
 ```{r}
@@
   geom_line(size = 1) +
-  labs(x = "Logit scale", y = "Probability scale")
-
-#we can see that after -5 or +5 the probability doesn't change much, instead of leaving our priors at the default of + and - infinity, we should say that they are most likely to occur between -5 and +5.
-```
-
-###2.2.3 Ploting priors
+  labs(x = "Logit scale", y = "Probability scale") +
+  theme_minimal()
+```
+
+#### Ploting priors
+
+This visualises our priors, to aid in specification.
+
 ```{r}
@@
 
-###2.2.4 Setting priors 
-```{r}
-#the priors for the intercept have been left as the default and the coefficient priors defined above
+#### Setting priors
+
+These are our specified priors, for the intercept have been left as the default and the coefficient priors defined above.
+
+```{r}
 priors <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
@@
 
-###2.2.5 Prior predictive check 
+#### Prior predictive check
+
+Here we will build a prior only model, to check the specification was reasonable
+
 ```{r}
@@
 
+color_scheme_set("red")
 pp_check(prior_model, ndraws=20)
@@
 
-##2.3 Modelling the proportion of time gobies spent outside of the burrow
+### Running model
+
+Now we run and save the model.
+
+⏭️ **Skip this step** if you have downloaded the saved model 'goby_out_model.rds'. You will load the model in the next step.
+
+🚧 Jack, you might consider wiring the brms models to a folder called '4-mods' 🚧
+
 ```{r}
@@
 )
-
-goby_out_model <- brm(
-  goby_out_formula_1,
-  data = final_df,
-  family = zero_one_inflated_beta(),
-  prior = priors,
-  control = list(adapt_delta = 0.99,
-                 max_treedepth = 12),
-  chains = 4, iter = 4000, warmup = 1000,
-  cores = 4, threads = threading(2),
-  backend = "cmdstanr",
-  seed = 1,
-  file = "goby_out_model"
-)
-
+```
+
+Run model
+
+```{r}
+# goby_out_model <- brm(
+#   goby_out_formula_1,
+#   data = final_df,
+#   family = zero_one_inflated_beta(),
+#   prior = priors,
+#   control = list(adapt_delta = 0.99,
+#                  max_treedepth = 12),
+#   chains = 4, iter = 4000, warmup = 1000,
+#   cores = 4, threads = threading(2),
+#   backend = "cmdstanr",
+#   seed = 1,
+#   file = "goby_out_model"
+# )
+```
+
+Here we reload the model.
+
+```{r}
+goby_out_model <-  readRDS(file = "goby_out_model.rds")
+```
+
+Looking at the basic model summary
+
+```{r}
 summary(goby_out_model)
 ```
-###2.3.1 Model fit and diagnostics
-####2.3.1.1 Model convergence
+
+### Model fit and diagnostics
+
+#### Model convergence
+
+Here we check the model convergence using R-hat
+
 ```{r}
@@
 
-####2.3.1.2 Model fit
+#### Model fit
+
+Now we will asses model fit.
+
 ```{r}
@@
 pp_check(goby_out_model, type='stat', stat='mean')
-
-#fitted vs predicted values
+```
+
+Creating a summary of the observed data
+
+```{r}
 summary(fitted(goby_out_model))
+```
+
+To compare with a summary of the predicted data, they seem to align very nicely.
+
+```{r}
 summary(predict(goby_out_model))
@@
 
-###2.3.2 Posterior marginal effects
-####2.3.2.1 Pairwise contrasts of stroke and stage
+🚧 Interesting that a 16% of the observations are not being predicted very well by the model, do we think this is an issue 🚧
+
+Using leave one out (loo) measure of fit, the model appears to preform ok, 16% Pareto k estimates falls outside the good range (0.7, 1]
+
+```{r}
+loo(goby_out_model)
+```
+
+### Posterior marginal effects
+
+#### Pairwise contrasts of stroke and stage
+
 ```{r}
@@
 
-goby_out_results.table
-
+goby_out_results.table %>% 
+  gt()
+```
+
+Pull predicted contrast for a plot
+
+```{r}
 goby_out_contrast_draws <- goby_out_model |>
@@
   gather_emmeans_draws()
-  goby_out_contrast_draws
 
@@
 goby_out_temporal_contrasts$stroke <- factor(goby_out_temporal_contrasts$stroke, levels = c("Control", "4", "2"))
-
-fig.goby_out_temporal_contrasts<- ggplot(goby_out_temporal_contrasts, aes(x = .value, y = factor(contrast, levels = c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")), color = stroke, fill = stroke)) +
+```
+
+Making a figure
+
+```{r}
+fig.goby_out_temporal_contrasts <- ggplot(goby_out_temporal_contrasts, aes(x = .value, y = factor(contrast, levels = c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")), color = stroke, fill = stroke)) +
    geom_vline(xintercept = 0, color = "black", size = 0.5) +
@@
 ```
-###2.3.3 Extracting and plotting model estimates
-####2.3.3.1 Extracting estimates
+### Extracting and plotting model estimates
+
+#### Extracting estimates
 ```{r}
@@
 
-####2.3.3.2 Plotting model estimates and raw data
+####  Plotting model estimates and raw data
+
 ```{r}
@@
 
-####2.3.3.3 Plotting control estimates and raw data
+#### Plotting control estimates and raw data
+
 ```{r}
@@
 ```
-####2.3.3.4 Plotting 4-stroke estimates and raw data
+#### Plotting 4-stroke estimates and raw data
+
 ```{r}
@@
 
-####2.3.3.5 Plotting 2-stroke estimates and raw data
+#### Plotting 2-stroke estimates and raw data
+
 ```{r}
@@
 ```
-####2.3.3.6 Combining plots into one figure
-```{r}
+
+#### Combining plots into one figure
+
+```{r, results='hide'}
 goby_out_plot3 <- goby_out_fig_control + goby_out_fig_four + goby_out_fig_two + 
   plot_layout(ncol = 3)
-
+```
+
+```{r}
 goby_out_plot3
@@
 
-###2.3.4 Effects of covariates on the proportion of time gobies spent outside of the burrow
-####2.3.4.1 Goby number
+### Effects of covariates on the proportion of time gobies spent outside of the burrow
+
+#### Goby number
+
+Estimates based on the number of gobies
+
 ```{r}
@@
 goby_out_goby_number
-
+```
+
+Plotting contrast
+
+```{r}
 goby_out_goby_number_draws <- goby_out_model |>
@@
   xlab(NULL) +
+  theme_classic() +
   coord_flip()
@@
 
-####2.3.4.2 Shrimp number
+#### Shrimp number
+
+Estimates based on the number of shrimp
+
 ```{r}
@@
 goby_out_shrimp_number_estimates
-
+```
+
+Plotting contrast
+
+```{r}
 goby_out_shrimp_number_draws <- goby_out_model |>
@@
 
-####2.3.4.3 Shrimp species
+#### Shrimp species
+
 ```{r}
@@
 
-##2.4 Modelling the proportion of time shrimp spent outside of the burrow
+## 🦐 Shrimp time outside of burrow
+
+Model structure
+
 ```{r}
@@
 )
-
-shrimp_out_model <- brm(
-  shrimp_out_formula,
-  data = final_df,
-  family = zero_one_inflated_beta(),
-  prior = priors,
-  control = list(adapt_delta = 0.99,
-                 max_treedepth = 12),
-  chains = 4, iter = 4000, warmup = 1000,
-  cores = 4, threads = threading(2),
-  backend = "cmdstanr",
-  seed = 1,
-  file = "shrimp_out_model"
-)
-
+```
+
+Now we run and save the model.
+
+⏭️ **Skip this step** if you have downloaded the saved model 'shrimp_out_model.rds'. You will load the model in the next step
+
+```{r}
+# shrimp_out_model <- brm(
+#   shrimp_out_formula,
+#   data = final_df,
+#   family = zero_one_inflated_beta(),
+#   prior = priors,
+#   control = list(adapt_delta = 0.99,
+#                  max_treedepth = 12),
+#   chains = 4, iter = 4000, warmup = 1000,
+#   cores = 4, threads = threading(2),
+#   backend = "cmdstanr",
+#   seed = 1,
+#   file = "shrimp_out_model"
+# )
+```
+
+Here we reload the model.
+
+```{r}
+shrimp_out_model <-  readRDS(file = "shrimp_out_model.rds")
+```
+
+```{r}
 summary(shrimp_out_model)
@@
 
-###2.4.1 Model fit and diagnostics
-####2.4.1.1 Model convergence
+### Model fit and diagnostics
+
+#### Model convergence
+
 ```{r}
@@
 
-####2.4.1.2 Model fit
+#### Model fit
+
 ```{r}
@@
 pp_check(shrimp_out_model, type='stat', stat='mean')
-
-#fitted vs predicted values
+```
+
+Creating a summary of the observed data
+
+```{r}
 summary(fitted(shrimp_out_model))
+```
+
+To compare with a summary of the predicted data, they seem to align very nicely.
+
+```{r}
 summary(predict(shrimp_out_model))
@@
 
-###2.4.2 Posterior marginal effects
-####2.4.2.1 Pairwise contrasts of stroke and stage
+### Posterior marginal effects
+
+#### Pairwise contrasts of stroke and stage
+
 ```{r}
@@
 shrimp_out_contrasts
-
+```
+
+```{r}
 shrimp_out_contrast_draws <- shrimp_out_model  |>
@@
 
-###2.4.3 Extracting and plotting model estimates
-####2.4.3.1 Extracting estimates
+### Extracting and plotting model estimates
+
+#### Extracting estimates
+
 ```{r}
@@
 ```
-####2.4.3.2 Plotting model estimates and raw data
+
+#### Plotting model estimates and raw data
+
 ```{r}
@@
 
-####2.4.3.3 Plotting control estimates and raw data
+#### Plotting control estimates and raw data
+
 ```{r}
@@
 ```
-####2.4.3.4 Plotting 4-stroke estimates and raw data
+
+#### Plotting 4-stroke estimates and raw data
+
 ```{r}
@@
 
-####2.4.3.5 Plotting 2-stroke estimates and raw data
+#### Plotting 2-stroke estimates and raw data
+
 ```{r}
@@
 ```
-####2.4.3.6 Combining plots into one figure
+#### Combining plots into one figure
+
 ```{r}
@@
 
-###2.4.4 Effects of covariates on the proportion of time shrimp spent outside of the burrow
-####2.4.4.1 Goby number
+### Effects of covariates on the proportion of time shrimp spent outside of the burrow
+
+#### Goby number
+
 ```{r}
@@
 
-####2.4.4.2 Shrimp number
+####  Shrimp number
+
 ```{r}
@@
 shrimp_out_shrimp_number_estimates
-
+```
+
+```{r}
 shrimp_out_shrimp_number_contrast_draws <- shrimp_out_model |>
@@
 ```
-####2.4.4.3 Shrimp species
+#### Shrimp species
+
 ```{r}
@@
 
-##2.5 Modelling the proportion of time shrimp spent in contact with the goby
-###2.5.1 Checking the response variable distribution
+## 🐟-🦐 Modelling the proportion of time shrimp spent in contact with the goby
+
+### Checking the response variable distribution
+
 ```{r}
@@
 
-###2.5.2 Running the model
+### Running the model
+
 ```{r}
@@
 
-###2.5.3 Model fit and diagnostics
-####2.5.3.1 Model convergence
+### Model fit and diagnostics
+
+#### Model convergence
+
 ```{r}
@@
 
-####2.5.3.2 Model fit
+#### Model fit
+
 ```{r}
@@
 pp_check(shrimp_contact_model, type='stat', stat='mean')
-
-#fitted vs predicted values
+```
+
+```{r}
 summary(fitted(shrimp_contact_model))
+```
+
+```{r}
 summary(predict(shrimp_contact_model))
@@
 
-###2.5.2 Posterior marginal effects
-####2.5.2.1 Pairwise contrasts of stroke and stage
+### Posterior marginal effects
+
+#### Pairwise contrasts of stroke and stage
+
 ```{r}
@@
 shrimp_contact_contrasts
-
+```
+
+```{r}
 shrimp_contact_contrasts_draws <- shrimp_contact_model  |>
@@
   scale_fill_manual(values = alpha(c(colour1, colour2, colour3), 0.8)) +
-  labs(x = "Difference in the proportion of time spent out of the burrow",
+  labs(x = "Difference in the proportion of time spent in contact",
        y = "Contrasts of the time periods relative to noise exposure",
@@
 
-###2.5.3 Extracting and plotting model estimates
-####2.5.3.1 Extracting estimates
+### Extracting and plotting model estimates
+
+#### Extracting estimates
 ```{r}
@@
 ```
-####2.5.3.2 Plotting model estimates and raw data
+#### Plotting model estimates and raw data
+
 ```{r}
@@
 
-####2.5.3.3 Plotting control estimates and raw data
+#### Plotting control estimates and raw data
+
 ```{r}
@@
 ```
-####2.5.3.4 Plotting 4-stroke estimates and raw data
+
+#### Plotting 4-stroke estimates and raw data
+
 ```{r}
@@
 
-####2.5.3.5 Plotting 2-stroke estimates and raw data
+#### Plotting 2-stroke estimates and raw data
+
 ```{r}
@@
 ```
-####2.5.3.6 Combining plots into one figure
+
+#### Combining plots into one figure
+
 ```{r}
@@
   plot_layout(ncol = 3)
-
+```
+
+```{r}
 shrimp_contact_plot3
@@
 
-###2.5.4 Modelling the effect of covariates on the proportion of time spent in contact
-####2.5.4.1 Goby number
+### Modelling the effect of covariates on the proportion of time spent in contact
+
+#### Goby number
+
 ```{r}
@@
 
-####2.5.4.2 Shrimp number
+#### Shrimp number
+
 ```{r}
@@
 
-####2.5.4.2 Shrimp species
+#### Shrimp species
+
 ```{r}
@@
 
-#3 Manuscript output files
-##3.1 Supp tables
-###3.1.1 Model estimates
+# Manuscript output files
+
+## Supp tables
+
+### Model estimates
+
 ```{r}
@@
 
-###3.1.2 Pairwise contrasts
+### Pairwise contrasts
+
 ```{r}

### 2025-02-20 ms_boatnoise_shrimp_goby.Rmd
Included a line to install cmdstanR for interfacing between brms and stan

@@
 #install.packages("pacman")
+#install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos")))
 #require("pacman") 

### 2025-02-25 ms_boatnoise_shrimp_goby.Rmd
Script tidy, PDF figures, and update ignore

--- 2025-02-19 ms_boatnoise_shrimp_goby.Rmd
@@
 
+**🚧 UNPUBLISHED AND ONGOING 🚧 **   
+The data in this script is currently **unpublished**.
+There may be part of this script that are currently incomplete.
+This script has been made publicly available for easy of sharing with collaborators and colleagues who are interested in the progression of the project and for complete transparency.
+
+-------
+
 **SUMMARY**  
+Human activities are reshaping marine soundscapes, with boat noise a near-constant source of underwater noise and a primary contributor to rising oceanic noise pollution.
+Despite increasing concern, empirical data for most marine life, particularly in natural settings, remains sparse.
+Fish and crustaceans are underrepresented in noise pollution research, despite their auditory ranges make them especially susceptible to low-frequency typical of boat engines.
+Accordingly, this study employs a field-based experimental approach to investigate the impacts of boat noise on an iconic behavioural mutualism between gobies (Amblyeleotris steinitzi) and shrimp (Alpheus spp).
+Our findings demonstrate that both species exhibit increased burrow use in response to boat noise, suggesting a heightened perception of risk.
+Despite the perceived risk triggered by boat noise, the behaviour of the two species remained tightly correlated and communication—measured as antennae contact—remained unchanged.
+Notably, shrimp exhibited stronger responses to 2-stroke engines, whereas gobies responded more strongly to 4-stroke engines, indicating species-specific sensitivities to different noise spectra.
+These results highlight the complex and taxon-specific effects of noise pollution on marine species and emphasize the need for targeted research to inform conservation strategies aimed at mitigating anthropogenic acoustic disturbances in marine ecosystems .
+
+-------
 
 **AIM**  
+This study employs a field-based experimental approach to investigate the impacts of boat noise on an iconic behavioural mutualism between gobies (Amblyeleotris steinitzi) and shrimp (Alpheus spp).
+We test the hypothesis that boat noise exposure (2-stroke and 4-stroke engines) would alter the mutualism of these two species by independently altering perceived risk, leading to shifts in behaviour, and potentially disrupting their communication.
+
+-------
 
 **AUTHORS**  
+Jack L. Manera^1†^   
+Jake M. Martin^1,2,3†^    
+Maria M. Palacios^4^ 
+Rachel T Mason^3^    
+Mark I. McCormick^5^    
+Bob BM. Wong^1^
+
+-------
 
 **AFFILIATIONS**    
+^1^School of Biological Sciences, Monash University, Clayton, Victoria 3800, Australia   
+^2^School of Life and Environmental Sciences, Deakin University, Waurn Ponds, Victoria 3216, Australia   
+^3^Department of Wildlife, Fish, and Environmental Studies, Swedish University of Agricultural Sciences, Umeå, Sweden   
+^4^Centre for Nature Positive Solutions, School of Science, RMIT University, Melbourne, Victoria 3100, Australia   
+^5^Coastal Marine Field Station, School of Science, University of Waikato, Tauranga, New Zealand   
+^†^These authors contributed equally as lead investigators
+
+-------
 
 **CONTRIBUTOR ROLES**  
+*🚧 to be added 🚧*
+
+<!------------------------------->
+# 📑 Sharing/accessing and citing
+<!------------------------------->
+
+**Licenses/restrictions placed on the data:** CC-BY 4.0
+
+**Link to the associated publication:**     
+🚧 *To be added* 🚧
+
+**Recommended citation for this data:**      
+🚧 *To be added based on OSF DOI* 🚧
 
@@
 <!------------------------------->
+
+**Jack L. Manera**
+
+📧 **Email:** [jack.manera@monash.edu](mailto:jack.manera@monash.edu)
+
+🌐 **Web:** *🚧 to be added 🚧*
+
+🐙 **GitHub**: [JLManera](https://github.com/JLManera)
+
+-------
 
@@
 #install.packages("pacman")
-#require("pacman") 
+#install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos")))
+
 pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr, gghalves, ggpp, rstan, gt)
@@
 
+## Directories
+
+Assigning the directory so that the code can be universally read on any computer as long as the entire project file is shared. This is a relative path.
+
+```{r}
+directory <- './2-data/'
+```
+
 ## Data
@@
 They are identified with the code column.
+
+```{r}
+BORIS_output <- read.csv("./2-data/BORIS_output.csv")
+```
+
 - **💿 Video_codes.csv**: This has meta data for each video, include treatment information and associated codes.
+
+```{r}
+Video_codes <- read.csv("./2-data/Video_codes.csv")
+```
+
 - **💿 species.csv**: This is the species name for the shrimp in each of the videos
@@
 ```{r}
-#assigning the directory so that the code can be universally read on any computer as long as the entire project file is shared
-directory <- './2-data/'
-
-#reading in the coded raw BORIS output
-BORIS_output <- read.csv("./2-data/BORIS_output.csv")
-
-#reading in the decoder
-Video_codes <- read.csv("./2-data/Video_codes.csv")
-
-#reading in shrimp species information
 shrimp_species <- read.csv("./2-data/species.csv")
@@
 
-🚧 Jack, maybe you could break this up and add a little more detial, I got a little lost in the code 🚧
+🚧 Jack, maybe you could break this up and add a little more detail, I got a little lost in the code 🚧
 
@@
 
-Restructure the data frame for easier analysis
+Restructure the data frame for easier analysis. We also write this file as **💿 final_df.csv** in the the 📁 `./2-data` folder. This is what we will use for analysis.
 
@@
 
-### Running model
-
-Now we run and save the model.
-
-⏭️ **Skip this step** if you have downloaded the saved model 'goby_out_model.rds'. You will load the model in the next step.
-
-🚧 Jack, you might consider wiring the brms models to a folder called '4-mods' 🚧
+### Final model structure
+
+This is the structure of the final model
 
@@
 
-Run model
+### Running model
+
+Now we run and save the model.
+
+⏭️ **Skip this step** if you have downloaded the saved model 'goby_out_model.rds'. You will load the model in the next step.
+
+🚧 Jack, you might consider wiring the brms models to a folder called '4-mods' 🚧
 
@@
 
-Here we reload the model.
+Here we reload the saved model.
 
@@
 ggsave("./3-figs/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./3-figs/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
 ```
@@
 ```
+
 #### Combining plots into one figure
@@
 ggsave("./3-figs/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./3-figs/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
 ```
@@
 ggsave("./3-figs/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./3-figs/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
 ```

### 2025-03-04 ms_boatnoise_shrimp_goby.Rmd
Updated the abstract

@@
 **SUMMARY**  
-Human activities are reshaping marine soundscapes, with boat noise a near-constant source of underwater noise and a primary contributor to rising oceanic noise pollution.
-Despite increasing concern, empirical data for most marine life, particularly in natural settings, remains sparse.
-Fish and crustaceans are underrepresented in noise pollution research, despite their auditory ranges make them especially susceptible to low-frequency typical of boat engines.
-Accordingly, this study employs a field-based experimental approach to investigate the impacts of boat noise on an iconic behavioural mutualism between gobies (Amblyeleotris steinitzi) and shrimp (Alpheus spp).
-Our findings demonstrate that both species exhibit increased burrow use in response to boat noise, suggesting a heightened perception of risk.
-Despite the perceived risk triggered by boat noise, the behaviour of the two species remained tightly correlated and communication—measured as antennae contact—remained unchanged.
-Notably, shrimp exhibited stronger responses to 2-stroke engines, whereas gobies responded more strongly to 4-stroke engines, indicating species-specific sensitivities to different noise spectra.
-These results highlight the complex and taxon-specific effects of noise pollution on marine species and emphasize the need for targeted research to inform conservation strategies aimed at mitigating anthropogenic acoustic disturbances in marine ecosystems .
+Human activities are reshaping marine soundscapes globally, with persistent low-frequency noise from boat traffic recognised as a primary driver of marine noise pollution.
+Despite growing concern, empirical data for most marine life, in natural settings, remains sparse, particularly for fish and crustaceans whose auditory ranges overlap with the frequencies of boat noise.
+Accordingly, we conducted a field experiment to evaluate how boat noise from different engine types (2-stroke and 4-stroke) affects the mutualistic partnership between Steinitz’s goby (Amblyeleotris steinitzi) and snapping shrimp (Alpheus spp.).
+Across 123 mutualistic partnerships, we recorded behavioural responses before, during, and after noise exposure.
+Both species increased burrow use during noise exposure, indicating heightened risk perception, yet their tactile communication—critical for the functioning of the mutualism—remained unaltered.
+Notably, gobies responded more strongly to 4-stroke boat noise, reducing time outside their burrows by 22%, while shrimp were more sensitive to 2-stroke noise, reducing burrow use by 34%, reflecting species-specific sensitivities to different noise spectra.
+Behavioural changes were transient, rapidly reverting to baseline levels after the noise exposure stopped.
+These findings highlight divergent vulnerabilities tied to different engine acoustics and emphasise the need for targeted research to inform strategies for mitigating marine noise pollution.
 

### 2025-03-04 ms_boatnoise_shrimp_goby.Rmd
Updating the directory naming and relevant code

@@
 ```{r}
-directory <- './2-data/'
+directory <- './1-data/'
 ```
@@
 ```{r}
-BORIS_output <- read.csv("./2-data/BORIS_output.csv")
+BORIS_output <- read.csv("./1-data/BORIS_output.csv")
 ```
@@
 ```{r}
-Video_codes <- read.csv("./2-data/Video_codes.csv")
+Video_codes <- read.csv("./1-data/Video_codes.csv")
 ```
@@
 ```{r}
-shrimp_species <- read.csv("./2-data/species.csv")
+shrimp_species <- read.csv("./1-data/species.csv")
 ```
@@
 
-Restructure the data frame for easier analysis. We also write this file as **💿 final_df.csv** in the the 📁 `./2-data` folder. This is what we will use for analysis.
+Restructure the data frame for easier analysis. We also write this file as **💿 final_df.csv** in the the 📁 `./1-data` folder. This is what we will use for analysis.
 
@@
 
-write_csv(final_df, "./2-data/final_df.csv")
+write_csv(final_df, "./1-data/final_df.csv")
 ```
@@
 goby_out_plot3
-ggsave("./3-figs/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
-ggsave("./3-figs/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
+ggsave("./2-figs/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./2-figs/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
 ```
@@
 shrimp_out_plot3
-ggsave("./3-figs/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
-ggsave("./3-figs/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
+ggsave("./2-figs/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./2-figs/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
 ```
@@
 shrimp_contact_fig_together
-ggsave("./3-figs/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./2-figs/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 shrimp_contact_plot3
-ggsave("./3-figs/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
-ggsave("./3-figs/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
+ggsave("./2-figs/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./2-figs/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
 ```
@@
 
-write_csv(model_estimates, "./2-data/model_estimates.csv")
+write_csv(model_estimates, "./1-data/model_estimates.csv")
 ```
@@
 
-write_csv(goby_out_contrasts_table, "./2-data/goby_out_contrasts_table.csv")
+write_csv(goby_out_contrasts_table, "./1-data/goby_out_contrasts_table.csv")
 
@@
 
-write_csv(shrimp_out_contrasts_table, "./2-data/shrimp_out_contrasts_table.csv")
+write_csv(shrimp_out_contrasts_table, "./1-data/shrimp_out_contrasts_table.csv")
 
@@
 
-write_csv(shrimp_contact_contrasts_table, "./2-data/shrimp_contact_contrasts_table.csv")
+write_csv(shrimp_contact_contrasts_table, "./1-data/shrimp_contact_contrasts_table.csv")
 ```

### 2025-03-04 ms_boatnoise_shrimp_goby.Rmd
Improving annotations

@@
 
-These are the R packages required for this script. You will need to install a package called pacman to run the p_load function.
-
-🚧 Do we need `stan-dev/loo` 🚧
+These are the R packages required for this script. You will need to install a package called pacman to run the p_load function and cmdstanr as a lightwight backend for running the brms models.
 
@@
 pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr, gghalves, ggpp, rstan, gt) 
-
-#remotes::install_github("stan-dev/loo")
 ```
@@
 
-### Assigning values to missing entries
-
-Here we are dealing with miss focal species during specific segments of the trial.
-
-We make the assumption that when a **goby is present in other videos** (i.e.
-we know it exists) but **missing from a given trial segment** it is **'away'** and out of frame for the entire trial.
-In the case of shrimps, we assume it **inside the burrow the entire time**.
-These assumptions are based off our teams observation of these species, and the previously reported biological tendencies of each species.
-Because of this assumption we are assigning the respective value to the behviour in cases where one of the species is known to be present in a burrow but not viewed for the length of the trial.
-
-🚧 Jack, maybe you could break this up and add a little more detail, I got a little lost in the code 🚧
+### Assigning Values to Zero Entries
+
+During some trial phases, only one individual of a species was observed at a time.
+However, we know from observations in other phases of the same trial that multiple individuals were actually present.
+For example, in burrow X, only a single shrimp may have been seen during the noise exposure phase, but two shrimp were observed at the same time in the pre-noise exposure phase.
+
+This issue leads to incomplete behavioral data because the second individual is assigned zeros across all behavioral states.
+However, since the individual does exist, it must be in one of the four behavioral states: INSIDE, EDGE, NEAR, or AWAY.
+This suggests that the individual either:
+(1) Remained out of frame ("AWAY") for the entire phase.
+(2) Stayed inside the burrow ("INSIDE") for the entire phase.
+(3) Alternated visibility with the first individual, meaning only one individual of that species was observed at any given time.
+
+To correct for this, we apply the following biologically informed assumptions:
+- If **a goby is observed in other videos but missing from a given phase**, it is **"away"** (out of frame for the entire phase).
+- If **a shrimp is missing**, it is **"inside"** the burrow for the entire phase.
+
+These assumptions are based on our team's direct observations and previously documented biological tendencies of each species.
+While they are well-supported for cases (1) and (2), case (3) presents a challenge, as individual identity could not be maintained.
+Since behaviors could not be reliably assigned to a specific individual, we instead compute species-level averages for each burrow in the following code.
+This approach ensures that even if individuals were alternating in visibility, assigning one individual as "away" or "inside" for an entire trial does not compromise the overall behavioral representation.
+By averaging at the species level, we capture the broader behavioral patterns of the group.
 
@@
   dplyr::filter(individual == 1) 
-
+```
+
+###Converting durations to proportions
+
+Here we converte absolute duration of each behaviour to proportional time budgets (0-1 scale).
+
+```{r}
 #transforming the data frame into wide format and turning time spent in each zone into a proportion of the total time (i.e. a value between 0 and 1)
@@
   dplyr::select(-INSIDE, -EDGE, -NEAR, -AWAY, -CONTACT, -APART)
-
+```
+
+###Validating complete burrow records
+
+We identified and removed burrows that lacked records for both species.
+Without evidence of both species, we could not confidently confirm their coexistence in the burrow.
+Therefore, to ensure a focus on mutualistic pairs, we excluded partial records where only one species was observed.
+
+```{r}
 #checking if every burrow contains observations for both 'Shrimp' and 'Goby'
@@
 
-There are some burrows that are missing stages due to the animal not being observered at all during that observation so we will make some conditional assumptions and fill in the missing values.
+### Assigning values to missing entries
+
+In some cases, a species was not observed during an entire video, although other videos confirmed its presence in the same burrow.
+These instances were not captured by the earlier code designed for "Assigning Values to Zero Entries." As a result, we need to assign values to these missing entries using the same approach and assumptions.
+Specifically, all gobies are considered AWAY for the entire trial segment, while all shrimp are considered inside the burrow for the entire segment.
 
@@
 
-#Checking to see the count of observations per burrow
+#Checking to see the count of observations per burrow to ensure the code has worked
 filled_burrow_counts <- table(wide_data_filled$burrow)

### 2025-03-04 ms_boatnoise_shrimp_goby.Rmd
Updating annotations and readability of the code. Also, I have changed the folder structure for better organisation.

@@
 
-prior_model <- brm(
-  prior_formula,
-  data = final_df,
-  family = zero_one_inflated_beta(),
-  prior = priors,
-  control = list(adapt_delta = 0.99,
-                 max_treedepth = 12),
-  chains = 4, iter = 1000, warmup = 100,
-  cores = 4, threads = threading(2),
-  backend = "cmdstanr",
-  seed = 1,
-  sample_prior = "only",
-  file = "prior_check"
-)
+#Now we run and save the model. **unhash** the code below if you haven't downloaded the saved model 'goby_out_model.rds' in the "3-models" folder.
+
+# prior_model <- brm(
+#   prior_formula,
+#   data = final_df,
+#   family = zero_one_inflated_beta(),
+#   prior = priors,
+#   control = list(adapt_delta = 0.99,
+#                  max_treedepth = 12),
+#   chains = 4, iter = 1000, warmup = 100,
+#   cores = 4, threads = threading(2),
+#   backend = "cmdstanr",
+#   seed = 1,
+#   sample_prior = "only",
+#   file = "./3-models/prior_check"
+# )
+
+prior_model <-  readRDS(file = "./3-models/goby_out_model.rds")
 
@@
 ⏭️ **Skip this step** if you have downloaded the saved model 'goby_out_model.rds'. You will load the model in the next step.
-
-🚧 Jack, you might consider wiring the brms models to a folder called '4-mods' 🚧
 
@@
 #   seed = 1,
-#   file = "goby_out_model"
+#   file = "./3-models/goby_out_model"
 # )
@@
 ```{r}
-goby_out_model <-  readRDS(file = "goby_out_model.rds")
+goby_out_model <-  readRDS(file = "./3-models/goby_out_model.rds")
 ```
@@
 goby_out_plot3
-ggsave("./2-figs/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
-ggsave("./2-figs/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
-```
-
-### Effects of covariates on the proportion of time gobies spent outside of the burrow
+ggsave("./2-figures/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./2-figures/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
+```
+
+### Estimating the effects of covariates on the proportion of time gobies spent outside of the burrow
 
@@
 #   seed = 1,
-#   file = "shrimp_out_model"
+#   file = "./3-models/shrimp_out_model"
 # )
@@
 ```{r}
-shrimp_out_model <-  readRDS(file = "shrimp_out_model.rds")
+shrimp_out_model <-  readRDS(file = "./3-models/shrimp_out_model.rds")
 ```
@@
 shrimp_out_plot3
-ggsave("./2-figs/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
-ggsave("./2-figs/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
-```
-
-### Effects of covariates on the proportion of time shrimp spent outside of the burrow
+ggsave("./2-figures/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./2-figures/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
+```
+
+### Estimating the effects of covariates on the proportion of time shrimp spent outside of the burrow
 
@@
 
-```{r}
-shrimp_contact_model <- brm(
-  bf(shrimp_contact ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
-     phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
-     zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
-     coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow)
-     ),
-  data = final_df,
-  prior = priors,
-  family = zero_one_inflated_beta(),
-  control = list(adapt_delta = 0.99, max_treedepth = 12),
-  chains = 4, iter = 6000, warmup = 1000, seed = 1, backend = "cmdstanr", cores = 4, threads = threading(2),
-  file = "shrimp_contact_model"
-)
-
+Now we run and save the model.
+
+⏭️ **Skip this step** if you have downloaded the saved model 'shrimp_contact_model.rds'. You will load the model in the next step.
+
+```{r}
+# shrimp_contact_model <- brm(
+#   bf(shrimp_contact ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
+#      phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
+#      zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
+#      coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow)
+#      ),
+#   data = final_df,
+#   prior = priors,
+#   family = zero_one_inflated_beta(),
+#   control = list(adapt_delta = 0.99, max_treedepth = 12),
+#   chains = 4, iter = 6000, warmup = 1000, seed = 1, backend = "cmdstanr", cores = 4, threads = threading(2),
+#   file = "./3-models/shrimp_contact_model"
+# )
+```
+
+Here we reload the model.
+
+```{r}
+shrimp_contact_model <-  readRDS(file = "./3-models/shrimp_contact_model.rds")
+```
+
+```{r}
 summary(shrimp_contact_model)
@@
 shrimp_contact_fig_together
-ggsave("./2-figs/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./2-figures/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 shrimp_contact_plot3
-ggsave("./2-figs/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
-ggsave("./2-figs/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
-```
-
-### Modelling the effect of covariates on the proportion of time spent in contact
+ggsave("./2-figures/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
+ggsave("./2-figures/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
+```
+
+### Estimating the effect of covariates on the proportion of time spent in contact
 

### 2025-03-05 ms_boatnoise_shrimp_goby.Rmd
addressing Jake Martin's comments with addition of temporary code for explination

@@
 ```{r}
-#posterior predictive checks
 pp_check(goby_out_model, ndraws = 50)
@@
 
+```{r}
+loo(shrimp_out_model)
+```
+
 ### Posterior marginal effects
@@
 ```
+
+#Delete me I am one of Jack's rabbit holes
+
+```{r}
+priors <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
+            set_prior("logistic(0, 3)", class = "Intercept", dpar = "coi"),
+            set_prior("logistic(0, 3)", class = "Intercept", dpar = "zoi"),
+            set_prior("student_t(3, 0, 2.5)", class = "Intercept", dpar = "phi", lb = 0),
+            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
+            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "phi", lb = 0),
+            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "zoi", lb = 0),
+            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "coi", lb = 0),
+            set_prior("normal(0, 3)", class = "b"),
+            set_prior("normal(0, 3)", class = "b", dpar = "phi"),
+            set_prior("normal(0, 3)", class = "b", dpar = "zoi"),
+            set_prior("normal(0, 3)", class = "b", dpar = "coi"))
+
+priors1 <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
+            set_prior("logistic(0, 3)", class = "Intercept", dpar = "zoi"),
+            set_prior("student_t(3, 0, 2.5)", class = "Intercept", dpar = "phi", lb = 0),
+            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
+            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "phi", lb = 0),
+            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "zoi", lb = 0),
+            set_prior("normal(0, 3)", class = "b"),
+            set_prior("normal(0, 3)", class = "b", dpar = "phi"),
+            set_prior("normal(0, 3)", class = "b", dpar = "zoi"))
+
+priors2 <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
+            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
+            set_prior("normal(0, 3)", class = "b"))
+
+priors3 <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
+            set_prior("logistic(0, 3)", class = "Intercept", dpar = "coi"),
+            set_prior("logistic(0, 3)", class = "Intercept", dpar = "zoi"),
+            set_prior("student_t(3, 0, 2.5)", class = "Intercept", dpar = "phi", lb = 0),
+            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
+            set_prior("normal(0, 3)", class = "b"),
+            set_prior("normal(0, 3)", class = "b", dpar = "phi"),
+            set_prior("normal(0, 3)", class = "b", dpar = "zoi"),
+            set_prior("normal(0, 3)", class = "b", dpar = "coi"))
+
+priors4 <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
+            set_prior("normal(0, 3)", class = "b"))
+```
+
+```{r}
+goby_out_formula_simple1 <- bf(
+  # mu (mean) part
+  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  # phi (precision) part
+  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  # alpha (zero-one-inflation) part
+  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  # The one-inflated part, conditional on the 0s
+  coi ~ 1,
+
+  family = zero_one_inflated_beta()
+)
+
+goby_out_model_simple1 <- brm(
+  goby_out_formula_simple1,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors1,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 4000, warmup = 1000,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1
+)
+```
+
+```{r}
+goby_out_formula_simple2 <- bf(
+  # mu (mean) part
+  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  # phi (precision) part
+  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
+  # alpha (zero-one-inflation) part
+  zoi ~ 1,
+  # The one-inflated part, conditional on the 0s
+  coi ~ 1,
+
+  family = zero_one_inflated_beta()
+)
+
+goby_out_model_simple2 <- brm(
+  goby_out_formula_simple2,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors2,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 4000, warmup = 1000,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1
+)
+```
+
+```{r}
+goby_out_formula_simple3 <- bf(
+  # mu (mean) part
+  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  # phi (precision) part
+  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
+  # alpha (zero-one-inflation) part
+  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
+  # The one-inflated part, conditional on the 0s
+  coi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
+
+  family = zero_one_inflated_beta()
+)
+
+goby_out_model_simple3 <- brm(
+  goby_out_formula_simple3,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors3,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 4000, warmup = 1000,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1
+)
+```
+
+```{r}
+goby_out_formula_simple4 <- bf(
+  # mu (mean) part
+  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
+  # phi (precision) part
+  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
+  # alpha (zero-one-inflation) part
+  zoi ~ 1,
+  # The one-inflated part, conditional on the 0s
+  coi ~ 1,
+
+  family = zero_one_inflated_beta()
+)
+
+goby_out_model_simple4 <- brm(
+  goby_out_formula_simple4,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors4,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 4000, warmup = 1000,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1
+)
+```
+
+```{r}
+pp_check(goby_out_model, ndraws = 50)
+pp_check(goby_out_model_simple1, ndraws = 50)
+pp_check(goby_out_model_simple2, ndraws = 50)
+pp_check(goby_out_model_simple3, ndraws = 50)
+pp_check(goby_out_model_simple4, ndraws = 50)
+pp_check(goby_out_model, type='stat', stat='mean')
+pp_check(goby_out_model_simple1, type='stat', stat='mean')
+pp_check(goby_out_model_simple2, type='stat', stat='mean')
+pp_check(goby_out_model_simple3, type='stat', stat='mean')
+pp_check(goby_out_model_simple4, type='stat', stat='mean')
+```
+
+```{r}
+loo(goby_out_model_simple1)
+```
+
+```{r}
+loo(goby_out_model_simple2)
+```
+
+```{r}
+loo(goby_out_model_simple3)
+```
+
+```{r}
+loo(goby_out_model_simple4)
+```

### 2025-03-05 ms_boatnoise_shrimp_goby.Rmd
addressing Jake Martin's comments with addition of temporary code for explination

@@
 
-🚧 Interesting that a 16% of the observations are not being predicted very well by the model, do we think this is an issue 🚧
-
-Using leave one out (loo) measure of fit, the model appears to preform ok, 16% Pareto k estimates falls outside the good range (0.7, 1]
-
-```{r}
-loo(goby_out_model)
-```
-
 ### Posterior marginal effects
@@
 ```{r}
-pp_check(goby_out_model, ndraws = 50)
-pp_check(goby_out_model_simple1, ndraws = 50)
-pp_check(goby_out_model_simple2, ndraws = 50)
-pp_check(goby_out_model_simple3, ndraws = 50)
-pp_check(goby_out_model_simple4, ndraws = 50)
-pp_check(goby_out_model, type='stat', stat='mean')
-pp_check(goby_out_model_simple1, type='stat', stat='mean')
-pp_check(goby_out_model_simple2, type='stat', stat='mean')
-pp_check(goby_out_model_simple3, type='stat', stat='mean')
-pp_check(goby_out_model_simple4, type='stat', stat='mean')
-```
-
-```{r}
+pp_check(goby_out_model, ndraws = 50) + ggtitle("Main Model - Density Plot")
+pp_check(goby_out_model_simple1, ndraws = 50) + ggtitle("Simple Model 1 - Density Plot")
+pp_check(goby_out_model_simple2, ndraws = 50) + ggtitle("Simple Model 2 - Density Plot")
+pp_check(goby_out_model_simple3, ndraws = 50) + ggtitle("Simple Model 3 - Density Plot")
+pp_check(goby_out_model_simple4, ndraws = 50) + ggtitle("Simple Model 4 - Density Plot")
+pp_check(goby_out_model, type = 'stat', stat = 'mean') + ggtitle("Main Model - Mean Check")
+pp_check(goby_out_model_simple1, type = 'stat', stat = 'mean') + ggtitle("Simple Model 1 - Mean Check")
+pp_check(goby_out_model_simple2, type = 'stat', stat = 'mean') + ggtitle("Simple Model 2 - Mean Check")
+pp_check(goby_out_model_simple3, type = 'stat', stat = 'mean') + ggtitle("Simple Model 3 - Mean Check")
+pp_check(goby_out_model_simple4, type = 'stat', stat = 'mean') + ggtitle("Simple Model 4 - Mean Check")
+```
+
+```{r}
+loo(goby_out_model)
 loo(goby_out_model_simple1)
-```
-
-```{r}
 loo(goby_out_model_simple2)
-```
-
-```{r}
 loo(goby_out_model_simple3)
-```
-
-```{r}
 loo(goby_out_model_simple4)
-```
+#I have nicely pasted outputs below in text
+```
+
+**Main model**
+Pareto k diagnostic values:
+                         Count Pct.    Min. ESS
+(-Inf, 0.7]   (good)     310   84.0%   530     
+   (0.7, 1]   (bad)       57   15.4%   <NA>    
+   (1, Inf)   (very bad)   2    0.5%   <NA>
+
+**Simple model1**
+Pareto k diagnostic values:
+                         Count Pct.    Min. ESS
+(-Inf, 0.7]   (good)     341   92.4%   266     
+   (0.7, 1]   (bad)       26    7.0%   <NA>    
+   (1, Inf)   (very bad)   2    0.5%   <NA>
+
+**Simple model2**
+Pareto k diagnostic values:
+                         Count Pct.    Min. ESS
+(-Inf, 0.7]   (good)     341   92.4%   266     
+   (0.7, 1]   (bad)       26    7.0%   <NA>    
+   (1, Inf)   (very bad)   2    0.5%   <NA>
+
+**Simple model3**
+Pareto k diagnostic values:
+                         Count Pct.    Min. ESS
+(-Inf, 0.7]   (good)     349   94.6%   307     
+   (0.7, 1]   (bad)       18    4.9%   <NA>    
+   (1, Inf)   (very bad)   2    0.5%   <NA>
+
+**Simple model4**
+Pareto k diagnostic values:
+                         Count Pct.    Min. ESS
+(-Inf, 0.7]   (good)     367   99.5%   875     
+   (0.7, 1]   (bad)        2    0.5%   <NA>    
+   (1, Inf)   (very bad)   0    0.0%   <NA>
+
+#results from rabbit hole
+
+#################################################################################
+Change **var_model** to suit the model you want to compare to the complete model
+#################################################################################
+```{r}
+var_model = goby_out_model_simple2
+
+var_model_contrasts <- var_model |>
+  emmeans(~ stroke*stage, 
+          epred = TRUE,
+          re_formla = NULL,
+          rg.limit =14000) |> 
+  contrast(method = "revpairwise")
+
+# Extract the relevant contrast information
+var_model_contrasts <- as.data.frame(var_model_contrasts) |> 
+  dplyr::filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
+
+var_model_contrasts %>% 
+  gt()
+
+var_model_estimates <- var_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA)
+
+var_model_estimates <- as.data.frame(var_model_estimates)
+
+var_model_draws <- var_model |> 
+  emmeans(~ stroke*stage,
+          epred = TRUE,
+          rg.limit = 14000,
+          re_formula = NA) |> 
+  gather_emmeans_draws()
+
+var_model_draws <- var_model_draws |> 
+  rename(emmean = .value)
+
+goby_out_raw_data <- final_df |> 
+  rename(emmean = goby_out)
+
+goby_out_raw_data$stage <- factor(goby_out_raw_data$stage, levels = c("Pre", "During", "Post"))
+goby_out_raw_data$stroke <- factor(goby_out_raw_data$stroke, levels = c("control", "4", "2"))
+
+var_model_estimates$stage <- factor(var_model_estimates$stage, levels = c("Pre", "During", "Post"))
+var_model_estimates$stroke <- factor(var_model_estimates$stroke, levels = c("control", "4", "2"))
+
+var_model_draws$stage <- factor(var_model_draws$stage, levels = c("Pre", "During", "Post"))
+var_model_draws$stroke <- factor(var_model_draws$stroke, levels = c("control", "4", "2"))
+
+goby_out_means <- goby_out_raw_data |> 
+  group_by(stage, stroke) |> 
+  summarise(emmean = mean(emmean))
+
+var_fig_together <- ggplot(data = goby_out_raw_data, aes(x = stage, y = emmean, color = stroke, fill = stroke)) +
+  geom_point(data = goby_out_means, alpha = 1, position = position_dodgenudge(width = 0.8, x = -0.09), size = 9, shape = "_") +
+  geom_half_point(alpha = 0.3, position = position_dodgenudge(width = 0.8, x = -0.03), side = "l", range_scale = 0.5) +
+  geom_half_violin(data = var_model_draws, aes(x = stage, y = emmean, color = stroke, fill = stroke), alpha = 0.6, position = position_dodge(width = 0.8), side = "r", size = 0) +
+  geom_point(data = var_model_estimates, aes(x = stage, y = emmean, color = stroke), position = position_dodge(width = 0.8), size = 3) +
+  geom_errorbar(data = var_model_estimates, aes(x = stage, y = emmean, ymin = lower.HPD, ymax = upper.HPD, color = stroke), position = position_dodge(width = 0.8), width = 0, size = 1.25) +
+  scale_fill_manual(values = c("control" = "#76A34A", "4" = "#F29E00", "2" = "#E25A00"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
+  scale_color_manual(values = c("control" = "#2A330E", "4" = "#805213", "2" = "#542709"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
+  scale_x_discrete(labels = c("Pre", "During", "Post")) +
+  labs(title = "The effects of boat noise on goby burrow use",
+       y = "Proportion of time in out of the burrow",
+       x = "Experimental phase relative to noise exposure") +
+  theme_classic() +
+  theme(
+    axis.text.x = element_text(size = 10, margin = margin(t = 5)),  
+    axis.text.y = element_text(size = 10, margin = margin(r = 5)),  
+    axis.title.x = element_text(size = 13, margin = margin(t = 10)),
+    axis.title.y = element_text(size = 13, margin = margin(r = 10)),
+    legend.text = element_text(size = 10),
+    legend.title = element_text(size = 10),
+    legend.position = "right",
+    legend.justification = "top",
+    plot.title = element_text(hjust = 0.5, size = 16),  
+    plot.margin = margin(10, 10, 10, 10)
+  )
+
+var_fig_together + ggtitle("Simple model")
+goby_out_fig_together + ggtitle("Original model")
+```

### 2025-08-21 ms_boatnoise_shrimp_goby.Rmd
Updated most documents in preperation for publication. Formatting changes and additional analyses added.

--- 2025-03-04 ms_boatnoise_shrimp_goby.Rmd
@@
 **SUMMARY**  
-Human activities are reshaping marine soundscapes globally, with persistent low-frequency noise from boat traffic recognised as a primary driver of marine noise pollution.
-Despite growing concern, empirical data for most marine life, in natural settings, remains sparse, particularly for fish and crustaceans whose auditory ranges overlap with the frequencies of boat noise.
-Accordingly, we conducted a field experiment to evaluate how boat noise from different engine types (2-stroke and 4-stroke) affects the mutualistic partnership between Steinitz’s goby (Amblyeleotris steinitzi) and snapping shrimp (Alpheus spp.).
-Across 123 mutualistic partnerships, we recorded behavioural responses before, during, and after noise exposure.
-Both species increased burrow use during noise exposure, indicating heightened risk perception, yet their tactile communication—critical for the functioning of the mutualism—remained unaltered.
-Notably, gobies responded more strongly to 4-stroke boat noise, reducing time outside their burrows by 22%, while shrimp were more sensitive to 2-stroke noise, reducing burrow use by 34%, reflecting species-specific sensitivities to different noise spectra.
-Behavioural changes were transient, rapidly reverting to baseline levels after the noise exposure stopped.
-These findings highlight divergent vulnerabilities tied to different engine acoustics and emphasise the need for targeted research to inform strategies for mitigating marine noise pollution.
+Persistent noise pollution produced by boat traffic is reshaping marine soundscapes globally.
+Despite growing ecological concern, most studies to date have focused on individual-level effects under laboratory conditions, leaving major gaps in our understanding of how boat noise shapes species interactions in the wild.
+Using field-based behavioural assays, we investigate how boat noise from different engine types (4-stroke and 2-stroke) affects the mutualistic partnership between Steinitz’s goby (Amblyeleotris steinitzi) and snapping shrimp (Alpheus spp.).
+Across 123 partnerships, we recorded behavioural responses before, during, and after noise exposure.
+Gobies increased burrow use during 4-stroke boat noise exposure, while shrimp responded stronger to 2-stroke noise—reflecting taxon-specific sensitivities to different noise spectra.
+Despite these shifts, tactile partner communication remained robust across treatments.
+These findings highlight divergent vulnerabilities between species tied to different engine acoustics, and emphasise the need for targeted research to inform strategies for mitigating marine noise pollution.
 
@@
 **CONTRIBUTOR ROLES**  
-*🚧 to be added 🚧*
+Here, we report a list of the author's roles using the Contributor Role Taxonomy (CRediT).
+Jack L.
+Manera: Data curation (lead), Formal analysis (lead), Investigation (contributor), Methodology (contributor), Visualization (lead), Writing – Original Draft Preparation (co-lead), and Writing – Review & Editing (co-lead).
+Jake M.
+Martin: Data curation, Formal analysis, Supervision, Methodology, Writing – Original Draft Preparation (co-lead), and Writing – Review & Editing (co-lead).
+Maria M.
+Palacios: Conceptualisation, Investigation, Methodology, Writing – Review & Editing.
+Rachel T.
+Mason: Data curation, Writing – Review & Editing.
+Mark I.
+McCormick: Conceptualisation, Investigation, Methodology, Writing – Review & Editing.
+Bob BM.
+Wong: Conceptualisation, Investigation, Methodology, Funding Acquisition, Writing – Review & Editing.
 
@@
 
-**Licenses/restrictions placed on the data:** CC-BY 4.0
+**Licenses/restrictions placed on the data:**
+CC BY-NC-SA 4.0 Attribution-NonCommercial-ShareAlike 4.0 International [https://creativecommons.org/licenses/by-nc-sa/4.0/]
 
 **Link to the associated publication:**     
-🚧 *To be added* 🚧
+(to be updated upon publication)
 
 **Recommended citation for this data:**      
-🚧 *To be added based on OSF DOI* 🚧
+Manera JL, Martin JM, Palacios MM, Mason RT, McCormick MI, Wong BBM.
+2025.
+Data from: Boat noise alters behaviour in a fish-shrimp mutualism.
+DOI: 10.17605/OSF.IO/3X5YF.
+(to be updated upon publication)
 
@@
 📧 **Email:** [jack.manera@monash.edu](mailto:jack.manera@monash.edu)
-
-🌐 **Web:** *🚧 to be added 🚧*
 
@@
   pivot_wider(
-    id_cols = c(burrow_species, burrow_species_stage, burrow, stage, species, boat_id, stroke, site, number_conspecifics, shrimp_species),
+    id_cols = c(burrow_species, burrow_species_stage, burrow, stage, species, boat_id, stroke, site, number_conspecifics, shrimp_species, cum_sum_boat_trials_per_site, date),
     names_from = behaviour,
@@
   mutate(shrimp_contact = ifelse(is.na(shrimp_contact), ifelse(goby_out == 1, 0, 1 - goby_out), shrimp_contact)) |> 
-  filter(site != "SITE O")
-
+  filter(site != "SITE O") |> 
+  mutate(parsed_date = mdy(paste(date, "2023")),
+         experiment_day = dense_rank(parsed_date))
+```
+
+#double check this
+```{r}
+final_df <- inner_join(goby_df, shrimp_df, by = "burrow_stage") %>% 
+  mutate(
+    shrimp_contact = ifelse(is.na(shrimp_contact),
+                            ifelse(goby_out == 1, 0, 1 - goby_out),
+                            shrimp_contact)) %>% 
+  filter(site != "SITE O") %>% 
+  mutate(
+    parsed_date    = mdy(paste(date, "2023")),
+    experiment_day = as.integer(parsed_date - min(parsed_date, na.rm = TRUE)) + 1
+  )
+
+head(final_df)
+```
+
+```{r}
 write_csv(final_df, "./1-data/final_df.csv")
@@
 ```{r}
-get_prior(
-  zoib_formula,
-  data = final_df
-) %>% 
-  gt()
+get_prior(zoib_formula, data = final_df)
 ```
@@
 
-#Now we run and save the model. **unhash** the code below if you haven't downloaded the saved model 'goby_out_model.rds' in the "3-models" folder.
-
-# prior_model <- brm(
-#   prior_formula,
-#   data = final_df,
-#   family = zero_one_inflated_beta(),
-#   prior = priors,
-#   control = list(adapt_delta = 0.99,
-#                  max_treedepth = 12),
-#   chains = 4, iter = 1000, warmup = 100,
-#   cores = 4, threads = threading(2),
-#   backend = "cmdstanr",
-#   seed = 1,
-#   sample_prior = "only",
-#   file = "./3-models/prior_check"
-# )
-
-prior_model <-  readRDS(file = "./3-models/goby_out_model.rds")
+prior_model <- brm(
+  prior_formula,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 1000, warmup = 100,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1,
+  sample_prior = "only",
+  file = "./3-models/prior_check"
+)
 
@@
 
-⏭️ **Skip this step** if you have downloaded the saved model 'goby_out_model.rds'. You will load the model in the next step.
-
-```{r}
-# goby_out_model <- brm(
-#   goby_out_formula_1,
-#   data = final_df,
-#   family = zero_one_inflated_beta(),
-#   prior = priors,
-#   control = list(adapt_delta = 0.99,
-#                  max_treedepth = 12),
-#   chains = 4, iter = 4000, warmup = 1000,
-#   cores = 4, threads = threading(2),
-#   backend = "cmdstanr",
-#   seed = 1,
-#   file = "./3-models/goby_out_model"
-# )
-```
-
-Here we reload the saved model.
-
-```{r}
-goby_out_model <-  readRDS(file = "./3-models/goby_out_model.rds")
+```{r}
+goby_out_model <- brm(
+  goby_out_formula_1,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 4000, warmup = 1000,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1,
+  file = "./3-models/goby_out_model"
+)
 ```
@@
 summary(predict(goby_out_model))
-```
-
-🚧 Interesting that a 16% of the observations are not being predicted very well by the model, do we think this is an issue 🚧
-
-Using leave one out (loo) measure of fit, the model appears to preform ok, 16% Pareto k estimates falls outside the good range (0.7, 1]
-
-```{r}
-loo(goby_out_model)
 ```
@@
 goby_out_plot3
-ggsave("./2-figures/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
-ggsave("./2-figures/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
+ggsave("./2-figures/goby_out_plot.png", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 
-⏭️ **Skip this step** if you have downloaded the saved model 'shrimp_out_model.rds'. You will load the model in the next step
-
-```{r}
-# shrimp_out_model <- brm(
-#   shrimp_out_formula,
-#   data = final_df,
-#   family = zero_one_inflated_beta(),
-#   prior = priors,
-#   control = list(adapt_delta = 0.99,
-#                  max_treedepth = 12),
-#   chains = 4, iter = 4000, warmup = 1000,
-#   cores = 4, threads = threading(2),
-#   backend = "cmdstanr",
-#   seed = 1,
-#   file = "./3-models/shrimp_out_model"
-# )
-```
-
-Here we reload the model.
-
-```{r}
-shrimp_out_model <-  readRDS(file = "./3-models/shrimp_out_model.rds")
+```{r}
+shrimp_out_model <- brm(
+  shrimp_out_formula,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 4000, warmup = 1000,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1,
+  file = "./3-models/shrimp_out_model"
+)
 ```
@@
 summary(predict(shrimp_out_model))
+```
+
+```{r}
+loo(shrimp_out_model)
 ```
@@
 shrimp_out_plot3
-ggsave("./2-figures/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
-ggsave("./2-figures/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
+ggsave("./2-figures/shrimp_out_plot.png", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 
-⏭️ **Skip this step** if you have downloaded the saved model 'shrimp_contact_model.rds'. You will load the model in the next step.
-
-```{r}
-# shrimp_contact_model <- brm(
-#   bf(shrimp_contact ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
-#      phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
-#      zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
-#      coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow)
-#      ),
-#   data = final_df,
-#   prior = priors,
-#   family = zero_one_inflated_beta(),
-#   control = list(adapt_delta = 0.99, max_treedepth = 12),
-#   chains = 4, iter = 6000, warmup = 1000, seed = 1, backend = "cmdstanr", cores = 4, threads = threading(2),
-#   file = "./3-models/shrimp_contact_model"
-# )
-```
-
-Here we reload the model.
-
-```{r}
-shrimp_contact_model <-  readRDS(file = "./3-models/shrimp_contact_model.rds")
+```{r}
+shrimp_contact_model <- brm(
+  bf(shrimp_contact ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
+     phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
+     zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
+     coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow)
+     ),
+  data = final_df,
+  prior = priors,
+  family = zero_one_inflated_beta(),
+  control = list(adapt_delta = 0.99, max_treedepth = 12),
+  chains = 4, iter = 6000, warmup = 1000, seed = 1, backend = "cmdstanr", cores = 4, threads = threading(2),
+  file = "./3-models/shrimp_contact_model"
+)
 ```
@@
   rename(.value = emmean)
-```
-#### Plotting model estimates and raw data
-
-```{r}
-shrimp_contact_model_draws <- shrimp_contact_model |> 
-  emmeans(~ stroke*stage,
-          epred = TRUE,
-          rg.limit = 14000,
-          re_formula = NA) |> 
-  gather_emmeans_draws()
-
-shrimp_contact_model_draws <- shrimp_contact_model_draws |> 
-  rename(emmean = .value)
-
-shrimp_contact_raw_data <- final_df |> 
-  rename(emmean = shrimp_contact)
-
-shrimp_contact_raw_data$stage <- factor(shrimp_contact_raw_data$stage, levels = c("Pre", "During", "Post"))
-shrimp_contact_raw_data$stroke <- factor(shrimp_contact_raw_data$stroke, levels = c("control", "4", "2"))
-
-shrimp_contact_model_estimates$stage <- factor(shrimp_contact_model_estimates$stage, levels = c("Pre", "During", "Post"))
-shrimp_contact_model_estimates$stroke <- factor(shrimp_contact_model_estimates$stroke, levels = c("control", "4", "2"))
-
-shrimp_contact_model_draws$stage <- factor(shrimp_contact_model_draws$stage, levels = c("Pre", "During", "Post"))
-shrimp_contact_model_draws$stroke <- factor(shrimp_contact_model_draws$stroke, levels = c("control", "4", "2"))
-
-shrimp_contact_means <- shrimp_contact_raw_data |> 
-  group_by(stage, stroke) |> 
-  summarise(emmean = mean(emmean))
-
-shrimp_contact_fig_together <- ggplot(data = shrimp_contact_raw_data, aes(x = stage, y = emmean, color = stroke, fill = stroke)) +
-  geom_point(data = shrimp_contact_means, alpha = 1, position = position_dodgenudge(width = 0.8, x = -0.09), size = 9, shape = "_") +
-  geom_half_point(alpha = 0.3, position = position_dodgenudge(width = 0.8, x = -0.03), side = "l", range_scale = 0.5) +
-  geom_half_violin(data = shrimp_contact_model_draws, aes(x = stage, y = emmean, color = stroke, fill = stroke), alpha = 0.6, position = position_dodge(width = 0.8), side = "r", size = 0) +
-  geom_point(data = shrimp_contact_model_estimates, aes(x = stage, y = emmean, color = stroke), position = position_dodge(width = 0.8), size = 3) +
-  geom_errorbar(data = shrimp_contact_model_estimates, aes(x = stage, y = emmean, ymin = lower.HPD, ymax = upper.HPD, color = stroke), position = position_dodge(width = 0.8), width = 0, size = 1.25) +
-  scale_fill_manual(values = c("control" = "#76A34A", "4" = "#F29E00", "2" = "#E25A00"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
-  scale_color_manual(values = c("control" = "#2A330E", "4" = "#805213", "2" = "#542709"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
-  scale_x_discrete(labels = c("Pre", "During", "Post")) +
-  labs(title = "The effects of boat noise on goby-shrimp contact",
-       y = "Proportion of time the in contact",
-       x = "Experimental phase relative to noise exposure") +
-  theme_classic() +
-  theme(
-    axis.text.x = element_text(size = 10, margin = margin(t = 5)),  
-    axis.text.y = element_text(size = 10, margin = margin(r = 5)),  
-    axis.title.x = element_text(size = 13, margin = margin(t = 10)),
-    axis.title.y = element_text(size = 13, margin = margin(r = 10)),
-    legend.text = element_text(size = 10),
-    legend.title = element_text(size = 10),
-    legend.position = "right",
-    legend.justification = "top",
-    plot.title = element_text(hjust = 0.5, size = 16),  
-    plot.margin = margin(10, 10, 10, 10)
-  )
-
-shrimp_contact_fig_together
-ggsave("./2-figures/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 shrimp_contact_plot3
-ggsave("./2-figures/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
-ggsave("./2-figures/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
+ggsave("./2-figures/shrimp_contact_plot.png", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
 ```
@@
 
-write_csv(model_estimates, "./1-data/model_estimates.csv")
+write_csv(model_estimates, "./2-figures/supplementary_tables/Table_S2.csv")
 ```
@@
 
-write_csv(goby_out_contrasts_table, "./1-data/goby_out_contrasts_table.csv")
+write_csv(goby_out_contrasts_table, "./2-figures/supplementary_tables/Table_S3.csv")
 
@@
 
-write_csv(shrimp_out_contrasts_table, "./1-data/shrimp_out_contrasts_table.csv")
+write_csv(shrimp_out_contrasts_table, "./2-figures/supplementary_tables/Table_S4.csv")
 
@@
 
-write_csv(shrimp_contact_contrasts_table, "./1-data/shrimp_contact_contrasts_table.csv")
+write_csv(shrimp_contact_contrasts_table, "./2-figures/supplementary_tables/Table_S5.csv")
 ```
@@
 ```
+
+# Supplementary analysis
+
+Although sites in the experimental design were spatially distinct, boats were tested multiple times at the same sites across the experiment.
+This raises the possibility that some burrows may have potentially experienced prior boat-noise exposure before their focal trial.
+Such cumulative exposure could influence the behavioural responses we observed.
+To assess this, we conducted a supplementary analysis.
+
+We quantified potential cumulative prior exposure at each site using the variable cum_sum_boat_trials_per_site, defined as the cumulative number of boat-noise treatments that had occurred at a site before the current trial.
+This variable was added as a predictor to the original models.
+We then compared models with and without the predictor using LOOIC, examined the estimated trend of each behavioural outcome in relation to cumulative exposure, and visually and quantitatively compared effect sizes.
+Finally, we assessed whether inclusion of the cumulative exposure variable altered the inference of the main effects.
+
+```{r}
+ggplot(data = final_df, aes(x = cum_sum_boat_trials_per_site, y = goby_out)) +
+  geom_smooth(method = "lm") +
+  geom_jitter()
+
+ggplot(data = final_df, aes(x = cum_sum_boat_trials_per_site, y = shrimp_out)) +
+  geom_smooth(method = "lm") +
+  geom_jitter()
+
+ggplot(data = final_df, aes(x = cum_sum_boat_trials_per_site, y = shrimp_contact)) +
+  geom_smooth(method = "lm") +
+  geom_jitter()
+```
+
+## Goby out model
+
+### Fit model
+
+Here we run the models with 'cum_sum_boat_trials_per_site' which is the cumulative sum of the number of boat trials at each site.
+This is to see if potential prior exposure to boat noise has a an effect on behavior
+
+```{r}
+cumulative_sum_goby_out_formula <- bf(
+  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + cum_sum_boat_trials_per_site + (1 | site/burrow),
+  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + cum_sum_boat_trials_per_site + (1 | site/burrow),
+  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  coi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  family = zero_one_inflated_beta()
+  )
+
+cumulative_sum_goby_out_model <- brm(
+  cumulative_sum_goby_out_formula,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 4000, warmup = 1000,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1,
+  file = "./3-models/cumulative_sum_goby_out_model"
+)
+```
+
+### Model Diagnostics
+
+```{r}
+summary(cumulative_sum_goby_out_model)
+
+plot(cumulative_sum_goby_out_model, ask = F)
+
+pp_check(cumulative_sum_goby_out_model)
+```
+
+### Model predictive performance
+
+```{r}
+goby_out_model <- add_criterion(goby_out_model, criterion = "loo")
+cumulative_sum_goby_out_model <- add_criterion(cumulative_sum_goby_out_model, criterion = "loo")
+
+loo_compare(goby_out_model, cumulative_sum_goby_out_model)
+```
+
+the addition of 'cum_sum_boat_trials_per_site' does not improve model predictive performance
+
+### Effects of previous boat trials
+
+```{r}
+emtrends(cumulative_sum_goby_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
+```
+
+'cum_sum_boat_trials_per_site' does not have a meaningful effect on the proportion of time gobies spent out of the burrow
+
+### Comparison of effect estimates
+
+```{r}
+cumulative_sum_goby_out_model_contrast_effect <- cumulative_sum_goby_out_model |>
+  emmeans(~ stroke*stage, 
+          epred = TRUE,
+          re_formla = NULL,
+          rg.limit =14000) |> 
+  contrast(method = "revpairwise")
+
+# Extract the relevant contrast information
+cumulative_sum_goby_out_results.table <- as.data.frame(cumulative_sum_goby_out_model_contrast_effect) |> 
+  dplyr::filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
+
+cumulative_sum_goby_out_results.table
+goby_out_results.table
+
+cumulative_sum_goby_out_results.table$dataset <- "Cumulative sum model"
+goby_out_results.table$dataset <- "Non-cumulative model"
+
+goby_contrast_plot_data <- bind_rows(
+  cumulative_sum_goby_out_results.table,
+  goby_out_results.table
+)
+
+# Plot contrasts with HPD intervals
+ggplot(goby_contrast_plot_data,
+       aes(x = estimate, y = contrast, color = dataset)) +
+  geom_point(position = position_dodge(width = 0.6), size = 2) +
+  geom_errorbarh(aes(xmin = lower.HPD, xmax = upper.HPD),
+                 position = position_dodge(width = 0.6), height = 0.2) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
+  theme_classic() +
+  labs(
+    x = "Posterior median (with 95% HPD interval)",
+    y = "Contrasts",
+    title = "Comparison of contrasts between cumulative-sum and original models"
+  )
+```
+
+## Shrimp out model
+
+### Fit model
+
+Here we run the models with 'cum_sum_boat_trials_per_site' which is the cumulative sum of the number of boat trials at each site.
+This is to see if potential prior exposure to boat noise has a an effect on behavior
+
+```{r}
+cumulative_sum_shrimp_out_formula <- bf(
+  shrimp_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + cum_sum_boat_trials_per_site + (1 | site/burrow),
+  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + cum_sum_boat_trials_per_site + (1 | site/burrow),
+  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  coi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  family = zero_one_inflated_beta()
+  )
+
+cumulative_sum_shrimp_out_model <- brm(
+  cumulative_sum_shrimp_out_formula,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 4000, warmup = 1000,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1,
+  file = "./3-models/cumulative_sum_shrimp_out_model"
+)
+```
+
+### Model Diagnostics
+
+```{r}
+summary(cumulative_sum_shrimp_out_model)
+
+plot(cumulative_sum_shrimp_out_model, ask = F)
+
+pp_check(cumulative_sum_shrimp_out_model)
+```
+
+### Model predictive performance
+
+```{r}
+shrimp_out_model <- add_criterion(shrimp_out_model, criterion = "loo")
+cumulative_sum_shrimp_out_model <- add_criterion(cumulative_sum_shrimp_out_model, criterion = "loo")
+
+loo_compare(shrimp_out_model, cumulative_sum_shrimp_out_model)
+```
+
+the addition of 'cum_sum_boat_trials_per_site' does not improve model predictive performance
+
+### Effects of previous boat trials
+
+```{r}
+emtrends(cumulative_sum_shrimp_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
+```
+
+'cum_sum_boat_trials_per_site' does not have a meaningful effect on the proportion of time shrimp spent out of the burrow
+
+### Comparison of effect estimates
+
+```{r}
+cumulative_sum_shrimp_out_model_contrast_effect <- cumulative_sum_shrimp_out_model |>
+  emmeans(~ stroke*stage, 
+          epred = TRUE,
+          re_formla = NULL,
+          rg.limit =14000) |> 
+  contrast(method = "revpairwise")
+
+# Extract the relevant contrast information
+cumulative_sum_shrimp_out_results.table <- as.data.frame(cumulative_sum_shrimp_out_model_contrast_effect) |> 
+  dplyr::filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
+
+cumulative_sum_shrimp_out_results.table
+shrimp_out_contrasts
+
+cumulative_sum_shrimp_out_results.table$dataset <- "Cumulative sum model"
+shrimp_out_contrasts$dataset <- "Non-cumulative model"
+
+shrimp_contrast_plot_data <- bind_rows(
+  cumulative_sum_shrimp_out_results.table,
+  shrimp_out_contrasts
+)
+
+# Plot contrasts with HPD intervals
+ggplot(shrimp_contrast_plot_data,
+       aes(x = estimate, y = contrast, color = dataset)) +
+  geom_point(position = position_dodge(width = 0.6), size = 2) +
+  geom_errorbarh(aes(xmin = lower.HPD, xmax = upper.HPD),
+                 position = position_dodge(width = 0.6), height = 0.2) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
+  theme_classic() +
+  labs(
+    x = "Posterior median (with 95% HPD interval)",
+    y = "Contrasts",
+    title = "Comparison of contrasts between cumulative-sum and original models"
+  )
+```
+
+## Shrimp contact model
+
+### Fit model
+
+Here we run the models with 'cum_sum_boat_trials_per_site' which is the cumulative sum of the number of boat trials at each site.
+This is to see if potential prior exposure to boat noise has a an effect on behavior
+
+```{r}
+cumulative_sum_shrimp_contact_formula <- bf(
+  shrimp_contact ~ stroke*stage + goby_number + shrimp_number + shrimp_species + cum_sum_boat_trials_per_site + (1 | site/burrow),
+  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + cum_sum_boat_trials_per_site + (1 | site/burrow),
+  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  coi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
+  family = zero_one_inflated_beta()
+  )
+
+cumulative_sum_shrimp_contact_model <- brm(
+  cumulative_sum_shrimp_contact_formula,
+  data = final_df,
+  family = zero_one_inflated_beta(),
+  prior = priors,
+  control = list(adapt_delta = 0.99,
+                 max_treedepth = 12),
+  chains = 4, iter = 4000, warmup = 1000,
+  cores = 4, threads = threading(2),
+  backend = "cmdstanr",
+  seed = 1,
+  file = "./3-models/cumulative_sum_shrimp_contact_model"
+)
+```
+
+### Model Diagnostics
+
+```{r}
+summary(cumulative_sum_shrimp_contact_model)
+
+plot(cumulative_sum_shrimp_contact_model, ask = F)
+
+pp_check(cumulative_sum_shrimp_contact_model)
+```
+
+### Model predictive performance
+
+```{r}
+shrimp_contact_model <- add_criterion(shrimp_contact_model, criterion = "loo")
+cumulative_sum_shrimp_contact_model <- add_criterion(cumulative_sum_shrimp_contact_model, criterion = "loo")
+
+loo_compare(shrimp_contact_model, cumulative_sum_shrimp_contact_model)
+```
+
+the addition of 'cum_sum_boat_trials_per_site' does not improve model predictive performance
+
+### Effects of previous boat trials
+
+```{r}
+emtrends(cumulative_sum_shrimp_contact_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
+```
+
+'cum_sum_boat_trials_per_site' does not have a meaningful effect on the proportion of time shrimp spent in contact with a goby
+
+### Comparison of effect estimates
+
+```{r}
+cumulative_sum_shrimp_contact_model_contrast_effect <- cumulative_sum_shrimp_contact_model |>
+  emmeans(~ stroke*stage, 
+          epred = TRUE,
+          re_formla = NULL,
+          rg.limit =14000) |> 
+  contrast(method = "revpairwise")
+
+# Extract the relevant contrast information
+cumulative_sum_shrimp_contact_results.table <- as.data.frame(cumulative_sum_shrimp_contact_model_contrast_effect) |> 
+  dplyr::filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))
+
+cumulative_sum_shrimp_contact_results.table
+shrimp_contact_contrasts
+
+cumulative_sum_shrimp_contact_results.table$dataset <- "Cumulative sum model"
+shrimp_contact_contrasts$dataset <- "Non-cumulative model"
+
+shrimp_contact_contrast_plot_data <- bind_rows(
+  cumulative_sum_shrimp_contact_results.table,
+  shrimp_contact_contrasts
+)
+
+# Plot contrasts with HPD intervals
+ggplot(shrimp_contact_contrast_plot_data,
+       aes(x = estimate, y = contrast, color = dataset)) +
+  geom_point(position = position_dodge(width = 0.6), size = 2) +
+  geom_errorbarh(aes(xmin = lower.HPD, xmax = upper.HPD),
+                 position = position_dodge(width = 0.6), height = 0.2) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
+  theme_classic() +
+  labs(
+    x = "Posterior median (with 95% HPD interval)",
+    y = "Contrasts",
+    title = "Comparison of contrasts between cumulative-sum and original models"
+  )
+```

### 2025-08-22 ms_boatnoise_shrimp_goby.Rmd
unifying style

@@
 ```{r}
-final_df <- inner_join(goby_df, shrimp_df, by = "burrow_stage") %>% 
+final_df <- inner_join(goby_df, shrimp_df, by = "burrow_stage") |> 
   mutate(
@@
                             ifelse(goby_out == 1, 0, 1 - goby_out),
-                            shrimp_contact)) %>% 
-  filter(site != "SITE O") %>% 
+                            shrimp_contact)) |> 
+  filter(site != "SITE O") |> 
   mutate(
@@
 
-goby_out_results.table %>% 
+goby_out_results.table |> 
   gt()
@@
 #assigning a value for the baseline mean
-goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control %>%
-  dplyr::filter(stage == "Pre") %>%
+goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control |>
+  dplyr::filter(stage == "Pre") |>
   pull(.value)
@@
 #assigning a value for the baseline mean
-shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control %>%
-  dplyr::filter(stage == "Pre") %>%
+shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control |>
+  dplyr::filter(stage == "Pre") |>
   pull(.value)
@@
 #assigning a value for the baseline mean
-shrimp_contact_model_estimates_control_intercept <- shrimp_contact_model_estimates_control %>%
-  dplyr::filter(stage == "Pre") %>%
+shrimp_contact_model_estimates_control_intercept <- shrimp_contact_model_estimates_control |>
+  dplyr::filter(stage == "Pre") |>
   pull(.value)
@@
 
-write_csv(model_estimates, "./2-figures/supplementary_tables/Table_S2.csv")
+write_csv(model_estimates, "./2-figures/supplementary_tables/Table_S4.csv")
 ```
@@
 
-write_csv(goby_out_contrasts_table, "./2-figures/supplementary_tables/Table_S3.csv")
+write_csv(goby_out_contrasts_table, "./2-figures/supplementary_tables/Table_S5.csv")
 
@@
 
-write_csv(shrimp_out_contrasts_table, "./2-figures/supplementary_tables/Table_S4.csv")
+write_csv(shrimp_out_contrasts_table, "./2-figures/supplementary_tables/Table_S6.csv")
 
@@
 
-write_csv(shrimp_contact_contrasts_table, "./2-figures/supplementary_tables/Table_S5.csv")
-```
-
-```{r}
-table_S1 <- final_df %>%
+write_csv(shrimp_contact_contrasts_table, "./2-figures/supplementary_tables/Table_S7.csv")
+```
+
+```{r}
+table_S1 <- final_df |>
   select(c("burrow", "stroke", "site")) |> 
   unique() |> 
-  group_by(site, stroke) %>%
-  summarise(n = n(), .groups = "drop") %>%
-  pivot_wider(names_from = stroke, values_from = n, values_fill = 0) %>%
-  mutate(Total = `control` + `4` + `2`) %>%
-  arrange(site) %>%
+  group_by(site, stroke) |>
+  summarise(n = n(), .groups = "drop") |>
+  pivot_wider(names_from = stroke, values_from = n, values_fill = 0) |>
+  mutate(Total = `control` + `4` + `2`) |>
+  arrange(site) |>
   rename(`4-stroke` = `4`, 
@@
          Control = control)
+table_S1
+
+write_csv(table_S1, "./2-figures/supplementary_tables/Table_S1.csv")
 ```
@@
 
-loo_compare(goby_out_model, cumulative_sum_goby_out_model)
+goby_out_cumulative_loo_compare <- as.data.frame(loo_compare(goby_out_model, cumulative_sum_goby_out_model))
+goby_out_cumulative_loo_compare
 ```
@@
 ```{r}
-emtrends(cumulative_sum_goby_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
+cum_sum_boat_trials_per_site_effect_goby_out <- emtrends(cumulative_sum_goby_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
+cum_sum_boat_trials_per_site_effect_goby_out
 ```
@@
 
-loo_compare(shrimp_out_model, cumulative_sum_shrimp_out_model)
+shrimp_out_cumulative_loo_compare <- as.data.frame(loo_compare(shrimp_out_model, cumulative_sum_shrimp_out_model))
+shrimp_out_cumulative_loo_compare
 ```
@@
 ```{r}
-emtrends(cumulative_sum_shrimp_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
+cum_sum_boat_trials_per_site_effect_shrimp_out <- emtrends(cumulative_sum_shrimp_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
+cum_sum_boat_trials_per_site_effect_shrimp_out
 ```
@@
 
-loo_compare(shrimp_contact_model, cumulative_sum_shrimp_contact_model)
+shrimp_contact_cumulative_loo_compare <- as.data.frame(loo_compare(shrimp_contact_model, cumulative_sum_shrimp_contact_model))
+shrimp_contact_cumulative_loo_compare
 ```
@@
 ```{r}
-emtrends(cumulative_sum_shrimp_contact_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
+cum_sum_boat_trials_per_site_effect_shrimp_contact <- emtrends(cumulative_sum_shrimp_contact_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
+cum_sum_boat_trials_per_site_effect_shrimp_contact
 ```
@@
 ```
+
+## Additional supplementary tables
+
+```{r}
+short_label <- function(x) dplyr::recode(
+  x,
+  "Proportion of time gobies spent outside of the burrow"  = "Goby: time outside burrow",
+  "Proportion of time shrimp spent outside of the burrow"  = "Shrimp: time outside burrow",
+  "Proportion of time shrimp spent in contact with a goby" = "Shrimp–goby contact",
+  .default = x
+)
+
+cumulative_loo_compare_clean <-
+  bind_rows(
+    goby_out_cumulative_loo_compare  |> rownames_to_column("Model") |>
+      mutate(Behavioural_measure = "Proportion of time gobies spent outside of the burrow"),
+    shrimp_out_cumulative_loo_compare |> rownames_to_column("Model") |>
+      mutate(Behavioural_measure = "Proportion of time shrimp spent outside of the burrow"),
+    shrimp_contact_cumulative_loo_compare |> rownames_to_column("Model") |>
+      mutate(Behavioural_measure = "Proportion of time shrimp spent in contact with a goby")
+  ) |>
+  mutate(
+    Behavioural_measure = short_label(Behavioural_measure),
+    Model = if_else(str_detect(Model, "^cumulative_sum"), "Cumulative-sum model", "Non-cumulative model")
+  ) |>
+  select(
+    Behavioural_measure, Model,
+    elpd_loo, se_elpd_loo, looic, elpd_diff, se_diff
+  ) |>
+  rename(
+    `Behavioural measure` = Behavioural_measure,
+    `SE (elpd_loo)` = se_elpd_loo,
+    `SE (elpd_diff)` = se_diff
+  )
+
+write_csv(cumulative_loo_compare_clean, "./2-figures/supplementary_tables/Table_S2.csv")
+
+cumulative_effects_clean <-
+  bind_rows(
+    as.data.frame(cum_sum_boat_trials_per_site_effect_goby_out) |>
+      mutate(Behavioural_measure = "Proportion of time gobies spent outside of the burrow"),
+    as.data.frame(cum_sum_boat_trials_per_site_effect_shrimp_out) |>
+      mutate(Behavioural_measure = "Proportion of time shrimp spent outside of the burrow"),
+    as.data.frame(cum_sum_boat_trials_per_site_effect_shrimp_contact) |>
+      mutate(Behavioural_measure = "Proportion of time shrimp spent in contact with a goby")
+  ) |>
+  mutate(Behavioural_measure = short_label(Behavioural_measure)) |>
+  select(any_of(c("Behavioural_measure", "cum_sum_boat_trials_per_site.trend", "lower.HPD", "upper.HPD"))) |>
+  rename(
+    `Behavioural measure` = Behavioural_measure,
+    `Trend per additional prior boat trial` = cum_sum_boat_trials_per_site.trend,
+    `Lower 95% CrI` = lower.HPD,
+    `Upper 95% CrI` = upper.HPD
+  )
+cumulative_effects_clean
+write_csv(cumulative_effects_clean, "./2-figures/supplementary_tables/Table_S3.csv")
+```

### 2025-08-22 ms_boatnoise_shrimp_goby.Rmd
ensuring all formatting is unifrom

@@
 ```{r}
-# Generate data points
-x <- seq(-20, 20, length.out = 1000)  # Adjusted range for better visualization
-
-# Define parameters for the distributions
+x <- seq(-20, 20, length.out = 1000)
+
 loc_logistic <- 0
@@
 
-# Calculate PDFs
 pdf_logistic <- dlogis(x, location = loc_logistic, scale = scale_logistic)
@@
 
-# Plot the PDFs
 df <- data.frame(x = x, Logistic = pdf_logistic, Student_t = pdf_student_t, Normal = pdf_normal)
 ggplot(df, aes(x)) +
-  geom_line(aes(y = Logistic, color = "Logistic(0, 3)")) + # Default priors of Logistic(0,1) have been broadened as these priors seemed too restrictive
+  geom_line(aes(y = Logistic, color = "Logistic(0, 3)")) + 
   geom_line(aes(y = Student_t, color = "Student_t(3, 0, 2.5)")) +
-  geom_line(aes(y = Normal, color = "Normal(0, 3)")) + #For the beta coefficient prior, we will set it to be normally distributed around 0 with an sd of 5, here is the plotted prior distribution 
+  geom_line(aes(y = Normal, color = "Normal(0, 3)")) +
   labs(title = "Probability Density Functions",
@@
 ```{r}
-#convergence diagnostics (R-hat)
 extract_rhats <- function(model) {
   model_summary <- summary(model)
-  #extract R-hat values for fixed effects
   fixed_rhats <- model_summary$fixed[, "Rhat", drop = FALSE]
-  #check for random effects and extract R-hat values if present
   if (!is.null(model_summary$random)) {
     random_rhats <- do.call(rbind, lapply(model_summary$random, function(x) x[, "Rhat", drop = FALSE]))
-    #combine fixed and random effects R-hat values
     rhats <- rbind(fixed_rhats, random_rhats)
@@
 
-# Extract the relevant contrast information
 goby_out_results.table <- as.data.frame(goby_out_contrast_effect) |> 
@@
 
-#assigning a value for the baseline mean
 goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control |>
@@
 ```{r}
-#posterior predictive checks
 pp_check(shrimp_out_model)
@@
 
-# Extract the relevant contrast information
 shrimp_out_contrasts <- as.data.frame(shrimp_out_contrasts) |> 
@@
 
-#assigning a value for the baseline mean
 shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control |>
@@
 shrimp_contact_plot
-# Distribution is a zero-one inflated beta distribution, because the value for shrimp_contact is bounded by 0-1 as it is a proportion of the total time and there is values of 0 and 1.
 ```
@@
 ```{r}
-#posterior predictive checks
 pp_check(shrimp_contact_model)
@@
 overall_mean <- shrimp_contact_model |>
-  emmeans(~ 1,             # 1 means "no factors," i.e. the grand mean
-          epred = TRUE,    # estimate on the response scale
-          re_formla = NULL,
-          rg.limit = 14000)
-
-# View the summary with posterior mean and credible intervals
+  emmeans(~ 1, epred = TRUE, re_formla = NULL, rg.limit = 14000)
+
 overall_mean
 
-# Extract the relevant contrast information
 shrimp_contact_contrasts <- as.data.frame(shrimp_contact_contrasts) |> 
@@
 
-#Storing the model estimate means for each group to plot later on
 shrimp_contact_model_estimates_control <- shrimp_contact_model_estimates |> 
@@
 
-#assigning a value for the baseline mean
 shrimp_contact_model_estimates_control_intercept <- shrimp_contact_model_estimates_control |>
@@
 ```{r}
-#goby out
 goby_out_contrasts <- goby_out_results.table |> 
@@
 
-#shrimp out
 shrimp_out_contrasts1 <- shrimp_out_contrasts |> 
@@
 
-#shrimp contact
 shrimp_contact_contrasts1 <- shrimp_contact_contrasts |> 
@@
 
-# Extract the relevant contrast information
 cumulative_sum_goby_out_results.table <- as.data.frame(cumulative_sum_goby_out_model_contrast_effect) |> 
@@
 
-# Plot contrasts with HPD intervals
 ggplot(goby_contrast_plot_data,
@@
 
-# Extract the relevant contrast information
 cumulative_sum_shrimp_out_results.table <- as.data.frame(cumulative_sum_shrimp_out_model_contrast_effect) |> 
@@
 
-# Plot contrasts with HPD intervals
 ggplot(shrimp_contrast_plot_data,
@@
 
-# Extract the relevant contrast information
 cumulative_sum_shrimp_contact_results.table <- as.data.frame(cumulative_sum_shrimp_contact_model_contrast_effect) |> 
@@
 
-# Plot contrasts with HPD intervals
 ggplot(shrimp_contact_contrast_plot_data,
